\documentclass[a4paper, 10pt, oneside, DIV=9, chapterprefix=true, numbers=enddot,bibliography=totoc]{scrbook}
\usepackage{StyleK}
\usepackage{ShortcutsK}
\usepackage[normalem]{ulem}


\newcommand{\embrace}[1]{\textup{(}#1\textup{)}}
\newlength{\LETTERheight}
\AtBeginDocument{\settoheight{\LETTERheight}{I}}
\newcommand*{\longrightsquigarrow}[1]{\ \raisebox{0.24\LETTERheight}{\tikz \draw [-to,
		line join=round, line cap=round,
		decorate, decoration={
			zigzag,
			segment length=4,
			amplitude=.9,
			post=lineto,
			post length=0.42ex
		}] (0,0) -- (#1,0);}\ }


\subject{Lecture Notes for}
\title{Algebraic and Hermitian $K$-Theory}
\author{{\normalsize Lecturer}\\
	Fabian Hebestreit}
\date{{\normalsize Notes typed by}\\
	Ferdinand Wagner}
\publishers{Winter Term 2020/21\\
	University of Bonn}

%\includeonly{nothingtoseehere}
%\includeonly{./Chapters/KTheory1.tex}
\begin{document}
	\frontmatter
	\KOMAoption{chapterprefix}{false}
	\renewcommand{\thedummy}{\arabic{dummy}}
	\maketitle
	\noindent This text consists of unofficial notes on the lecture \emph{Advanced Topics in Algebra -- Algebraic and Hermitian $K$-Theory}, taught at the University of
	Bonn by Fabian Hebestreit in the winter term (Wintersemester) 2020/21.
	
	Some additions have been made by the author. To distinguish them from the lecture's actual contents, they are labelled with an asterisk. So any \emph{Proof}* or \emph{Lemma}* etc.\ that the reader might encounter are wholly the author's responsibility.
	\\[\thmsep]Please report errors, typos etc.\ through the \href{https://github.com/FlorianAdler/AlgebraBonn/issues/new}{\emph{Issues}} feature of GitHub, or just tell me before or after the lecture.
	
	
	\tableofcontents
	\listoftoc{lol}
	\setcounter{llecture}{-1}
	\mainmatter\KOMAoption{chapterprefix}{true}
	\renewcommand{\thedummy}{\thechapter.\arabic{dummy}}
	\setcounter{chapter}{-1}
	\renewcommand{\thechapter}{\arabic{chapter}}
	\include{./Chapters/KTheory1}
	\renewcommand{\thechapter}{\Roman{chapter}}

\chapter{Symmetric Monoidal and Stable \texorpdfstring{$\infty$}{infty}-Categories}\label{chap:Monoidal}\setcounter{dummy}{-1}
\section{\texorpdfstring{$\IE_1$}{E1}-Monoids and \texorpdfstring{$\IE_1$}{E1}-Groups}
We start things off slowly by only considering (not necessarily symmetric) monoidal $\infty$-categories and $\IE_1$-spaces.
\numpar{Stasheff's Definition of Coherently Associative Monoids}
The naive way to define a monoid in $\An$ would be to have an object $M\in \An$ together with a multiplication map
\begin{equation*}
	\mu\colon M\times M\morphism M\,.
\end{equation*}
Now $\mu$ induces two different maps $M^3\morphism M$ (\enquote{two ways of bracketing}), so there ought to be a homotopy $H\colon \mu\circ (\mu\times \id_M)\simeq \mu\circ(\id_M\times \mu)$ between them. But then there are five maps $M^4\morphism M$ (\enquote{five ways of bracketing}), and we see that $H$ induces a loop in $\Hom_\An(M^4,M)$. Since $M$ should be associative up to \emph{coherent homotopy}, this loop has to be filled. The story goes on: There are a number of maps $M^5\morphism M$ (too lazy to count them) and now there are some $3$-simplices to be filled and so on.

Although this looks horrible, it is possible to turn these considerations into a precise definition, and one obtains Stasheff's \emph{$\IA_\infty$-spaces}. But we can take a simpler route! Indeed, thanks to our efforts so far, we now have the luxury of saying: \enquote{Well, a coherently associative monoid is just an $\infty$ category with only one object.} This leads to the following definition.
\begin{defi}\label{def:CartesianMonoids}
	Let $\Cc$ be an $\infty$-category with finite products (in particular, $\Cc$ has a final object $*\in \Cc$). A \emph{cartesian monoid in $\Cc$} is a functor $X\colon \IDelta^\op\morphism \Cc$ such that:
	\begin{alphanumerate}
		\item $X_0\simeq *$.
		\item It satisfies the Segal condition, i.e., the Segal maps $e_i\colon [1]\morphism {[n]}$ define an equivalence
		\begin{equation*}
			X_n\isomorphism \prod_{i=1}^nX_1
		\end{equation*}
	\end{alphanumerate}
	Let $\cat{Mon}(\Cc)\subseteq\cat{s}\Cc$ be the full sub-$\infty$-category spanned by cartesian monoids. If $\Cc=\An$, these are also called \emph{$\IE_1$-spaces}, \emph{$\IA_\infty$-spaces}, \emph{coherent monoids}, \emph{special $\Delta$-spaces}, \dotso. For $\Cc=\Cat_\infty$ we simply call them \emph{monoidal $\infty$-categories} (note that these can also be encoded as cocartesian fibrations over $\IDelta^\op$).
\end{defi}
To make sense of the condition from \cref{def:CartesianMonoids}\itememph{b}, note that since $X_0\simeq *$ is terminal, we have $X_1\times_{X_0}\times\dotsb\times_{X_0}X_1\simeq \prod_{i=1}^nX_1$, so this condition really \emph{is} the Segal condition. Somewhat weird though is that we don't impose any completeness conditions, and in fact, cartesian monoids in $\An$ are usually \emph{not} complete Segal spaces! This is in some sense fixed by the following proposition.
\begin{prop}\label{prop:CompletionOfMonoidsFullyFaithful}
	The completion functor $\comp\colon\cat{sAn}\morphism\cat{CSAn}$ from Lemma/Defi-nition~\textup{\labelcref{lemdef:Completion}} restricts to a fully faithful functor
	\begin{equation*}
		\comp\colon\cat{Mon}(\An)\morphism */\cat{CSAn}
	\end{equation*}
	with essential image those pointed complete segal spaces $(X,x)$ with $\pi_0X_0=*$.
\end{prop}
In other words, monoids really are categories with one object (up to equivalence, but not up to contractible choice, as Bastiaan pointed out in the lecture), since the target is also pointed categories with connected base.
\begin{proof}[Proof of \cref{prop:CompletionOfMonoidsFullyFaithful}]
	\emph{Step~1.} Let's construct a candidate for an inverse functor. Recall that if $X$ is Segal, then the completion functor does not affect the pullback spaces
	\begin{equation*}
		\begin{tikzcd}
			P_{x,y}\rar\dar\drar[pullback] & X_1\dar["{(d_1,d_0)}"]\\
			*\rar["{(x,y)}"] & X_0\times X_0
		\end{tikzcd}
	\end{equation*}
	(this follows essentially from \cref{eq:asscat2}). This motivates the following definition of an inverse (\enquote{decompletion}) functor $\decomp\colon {*/\cat{CSAn}}\morphism \cat{Mon}(\An)$: Let $(X,x)$ be a pointed complete Segal space. We send it to $Y\in \cat{Mon}(\An)$, where $Y\colon \IDelta^\op\morphism \An$ is defined by the pullback
	\begin{equation*}
		\begin{tikzcd}[column sep=large]
			Y_n\dar\rar\drar[pullback]& X_n\dar\\
			*\rar["{(x,\dotsc,x)}"] & X_0^{n+1}
		\end{tikzcd}
	\end{equation*}
	for all $[n]\in \IDelta^\op$. Let's first address the elephant in the room, i.e.\ how to make the pointwise-defined $Y_n$ into a functor $\IDelta^\op\morphism \An$, which in turn should be functorial in $X$. We'll have solved both problems at once if we show that the diagram
	$*\morphism X_0^{n+1}\lmorphism X_n$ is functorial in $(X,x)$ and in $[n]$. To this end consider $X$ as a functor $\IDelta\morphism \An^\op$ and colimit-extend it to a functor
	\begin{equation*}
		|\blank|_X\colon \cat{sAn}\morphism \An^\op\,.
	\end{equation*}
	This can be done functorially in $X$, as \cref{thm:ColimitPreservingRepresentable} shows. In more abstract terms, what we do here is to identify  $\cat{sAn}\simeq \Fun(\IDelta,\An^\op)^\op\simeq \Fun^L(\cat{sAn},\An^\op)^\op$. We define two functors $\Delta,\Delta_0\colon \IDelta\morphism\cat{sSet}\subseteq\cat{sAn}$ via $\Delta([n])=\Delta^n$ and $\Delta_0([n])=\coprod_{i=0}^n\Delta^0$. Since $\Delta$ and $\Delta_0$ are functors between $1$-categories (before we compose them with the inclusion $\cat{sSet}\subseteq \cat{sAn}$), we don't need to check any higher coherences and immediately obtain that $\Delta$ and $\Delta_0$ are indeed functors. Moreover, the canonical map $\coprod_{i=0}^n\Delta^0\morphism \Delta^n$ sending the $i\ordinalth$ component to the $i\ordinalth$ vertex of $\Delta^n$ is clearly functorial in $[n]\in \IDelta$, hence it induces a natural transformation $\Delta_0\Rightarrow\Delta$ (which exhibits $\Delta_0$ as the \enquote{$0$-skeleton} of $\Delta$, hence the notation).
	
	Now consider the two composites
	\begin{equation*}
		\cat{sAn}\simeq \Fun\left(\IDelta,\An^\op\right)^\op\simeq \Fun\left(\cat{sAn},\An^\op\right)^\op\doublemorphism[\Delta^*][\Delta_0^*]\Fun\left(\IDelta,\An^\op\right)^\op\simeq \cat{sAn}\,,
	\end{equation*}
	which we denote $|\Delta|_{(-)}$ and $|\Delta_0|_{(-)}$. The transformation $\Delta_0\Rightarrow \Delta$ induces a transformation $|\Delta|_{(-)}\Rightarrow |\Delta_0|_{(-)}$ (since there has been an $(-)^\op$ in between). Upon closer inspection, we find that $\Delta\colon \IDelta\morphism\cat{sAn}$ is actually nothing else but the Yoneda embedding, hence \cref{thm:ColimitPreservingRepresentable} shows that $|\Delta|_{(-)}\simeq \id$! Moreover, since $|\blank|_X$ preserves colimits, we easily obtain
	\begin{equation*}
		X_0^{n+1}\simeq \left|\coprod_{i=0}^n\Delta^0\right|_X\,,
	\end{equation*}
	hence the $X_0^{n+1}$ can be organized into a simplicial anima $|\Delta_0|_X$. The transformation $\id\simeq |\Delta|_{(-)}\Rightarrow |\Delta_0|_{(-)}$ gives a natural map $X\morphism |\Delta_0|_X$.
	
	This shows that the maps $X_0^{n+1}\lmorphism X_n$ can indeed be made functorial in $X$ and $[n]$. A similar argument applies shows that the maps $*\morphism X_0^{n+1}$, which assemble into a functorial map $\Delta^0\morphism |\Delta_0|_X$. We conclude that $Y\simeq X\times_{|\Delta_0|_X}\Delta^0$ as above is indeed a simplicial anima and functorial in $X$. We have $Y_0\simeq *$ by construction and also $Y_n\simeq Y_1\times_{Y_0}\dotsb\times_{Y_0}Y_1$ follows from the fact that $X$ itself satisfies the Segal conditions together with some abstract pullback nonsense (basically that \enquote{limits commute}, see the dual of \cref{prop:ColimitsCommute}). So $Y\in \cat{Mon}(\An)$ and we can finally write down the functor
	\begin{equation*}
		\decomp\colon {*/\cat{CSAn}}\morphism \cat{Mon}(\An)\,.
	\end{equation*}

	\emph{Step~2.} Next, let's check that $\comp\colon \cat{Mon}(\An)\morphism \cat{CSAn}$ from \cref{lemdef:Completion} indeed factors over $*/\cat{CSAn}\morphism \cat{CSAn}$ and that its essential image is contained in those pointed complete Segal spaces $(X,x)$ with $\pi_0X_0=*$. To get the factorization, observe that $\cat{Mon}(\An)$ has an initial object, namely $\Delta^0\in\sSet\subseteq\cat{sAn}$ (in the lecture we called it \enquote{$\const*$}, but it's really just $\Delta^0$). Indeed, if $T\in \cat{Mon}(\An)$, then
	\begin{equation*}
		\Hom_{\cat{Mon}(\An)}(\Delta^0,T)\simeq \Hom_{\cat{sAn}}(\Delta^0,T)\simeq T_0\simeq *
	\end{equation*}
	by \cref{def:CartesianMonoids}\itememph{a}. Also $\comp (\Delta^0)\simeq *$, so the completion functor really lifts to a functor $\cat{Mon}(\An)\simeq \Delta^0/\cat{Mon}(\An)\morphism */\cat{CSAn}$, as required.
	
	To check that $\pi_0(\comp T)_0=*$, recall that $(\comp T)_0\simeq \core \asscat T\simeq |T^\times|$ by \cref{eq:asscat1}. Now we have to use the following general fact:
	\begin{alphanumerate}
		\item[\itememph{*}] \itshape For all $X\in\cat{sAn}$ the map $\pi_0X_0\morphism \pi_0|X|$ is surjective.
	\end{alphanumerate}
	This shows what we want since $(T^\times)_0\simeq T_0\simeq *$ holds by assumption. To see where \itememph{*} comes from, observe that $\pi_0$, being a left adjoint (\cref{exm:MyFirstAdjoints}\itememph{a}), commutes with colimits. This shows $\pi_0|X|\simeq \pi_0\colimit_{\IDelta^\op}X\simeq \colimit_{\IDelta^\op}\pi_0X$, where the colimit on the right-hand side is a good old colimit taken in $\sSet$. Now $\{d_0,d_1\colon [1]\shortdoublemorphism [0]\}\subseteq \IDelta^\op$ is $1$-cofinal (but not $\infty$-cofinal!), hence
	\begin{equation*}
		\colimit_{\IDelta^\op}\pi_0X=\Coeq\left(\pi_0X_1\doublemorphism[d_1][d_0] \pi_0X_0\right)\,.
	\end{equation*}
	This immediately implies \itememph{*}.
	
	\emph{Step~3.} Finally, we check that $\decomp\colon (*/\cat{CSAn})_{\pi_0=*}\morphism \cat{Mon}(\An)$ is indeed an inverse, where $(*/\cat{CSAn})_{\pi_0=*}\subseteq */\cat{CSAn}$ is the full subcategory spanned by those $(X,x)$ with $\pi_0X_0=*$. The first step is to construct the required natural transformations. We didn't do this in the lecture (Fabian promised to give a full proof in the lecture notes soon), so here's what I would do. We claim:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}]\itshape The functors $\comp\colon \cat{Mon}(\An)\shortdoublelrmorphism */\cat{CSAn}\noloc \decomp$ form an adjunction.
	\end{alphanumerate}
	Once we proved \itememph{\boxtimes}, we get the required transformations for free. So let's do this! Consider $T\in \cat{Mon}(\An)$, which is naturally pointed via the unique (up to contractible choice) map $1_T\colon \Delta^0\morphism T$, and let $(X,x)$ be a pointed complete Segal space. Then
	\begin{align*}
		\Hom_{*/\cat{CSAn}}\big(\comp T,(X,x)\big)&\simeq \Hom_{*/\cat{sAn}}\big((T,1_T),(X,x)\big)\\
		&\simeq \Hom_{\cat{sAn}}(T,X)\times_{\Hom_{\cat{sAn}}(\const 1_T,X)}\{\const x\}\\
		&\simeq \Hom_{\cat{sAn}}(T,X)\times_{\Hom_\An(1_T,X_0)}\{x\}\,.
	\end{align*}
	The first equivalence follows from \cref{lemdef:Completion} (and the fact that adjunctions extend to slice categories), the second follows from \cite[Corollary~VIII.6]{HigherCatsII}. The last one follows by inspection. All of them are functorial in $(X,x)$. Moreover, we have
	\begin{align*}
		\Hom_{\cat{Mon}(\An)}\big(T,\decomp (X,x)\big)&\simeq \Hom_{\cat{sAn}}\left(T,X\times_{|\Delta_0|_X}\Delta^0\right)\\
		&\simeq \Hom_{\cat{sAn}}(T,X)\times_{\Hom_{\cat{sAn}}(T,|\Delta_0|_X)}\Hom_{\cat{sAn}}(T,\Delta^0)\,.
	\end{align*}
	Since $\id\Rightarrow |\Delta_0|_{(-)}$ is a natural transformation, one quickly checks that the morphism $\Hom_{\cat{sAn}}(T,X)\morphism \Hom_{\cat{sAn}}(T,|\Delta_0|_X)$ factors over $\Hom_{\cat{sAn}}(|\Delta_0|_T,|\Delta_0|_X)$. But $T_0\simeq *$, hence $|\Delta_0|_T\simeq \Delta^0$. Also $\Hom_{\cat{sAn}}(T,\Delta^0)\simeq *$. Putting everything together, we can rewrite
	\begin{equation*}
		\Hom_{\cat{Mon}(\An)}\big(T,\decomp (X,x)\big)\simeq \Hom_{\cat{sAn}}(T,X)\times_{\Hom_\An(T_0,X_0)}\{x\}\,,
	\end{equation*} 
	and after another inspection, this provides the required natural equivalence
	\begin{equation*}
		\Hom_{*/\cat{CSAn}}\big(\comp T,(X,x)\big)\simeq\Hom_{\cat{Mon}(\An)}\big(T,\decomp (X,x)\big)\,,
	\end{equation*}
	proving \itememph{\boxtimes}.
	
	Equipped with our newly-acquired unit and counit transformations $\id\Rightarrow \decomp\circ \comp$ and $\comp\circ\decomp\Rightarrow \id$, we now set out to prove that $\decomp\colon (*/\cat{CSAn})_{\pi_0=*}\morphism \cat{Mon}(\An)$ is indeed an inverse of $\comp$. Let's start with the second one, i.e.\ the counit. We must show $\comp(\decomp (X,x))\simeq (X,x)$ for all $(X,x)\in (*/\cat{CSAn})_{\pi_0=*}$ . Observe that $\comp X\simeq X$ because $X$ is already complete. Hence it suffices to show $\asscat(\decomp(X,x))\simeq \asscat X$ (and check that the chosen base points on both sides correspond, but that's easy) because $\N^r$ is fully faithful by \cref{thmdef:RezkNerve}. Using \cref{eq:asscat1} and the fact that $X^\times$ is a constant simplicial anima with value $X_0$ as $X$ is complete, we see that
	\begin{equation*}
		\pi_0\core(\asscat X)\simeq \pi_0|X^\times|\simeq \pi_0X_0\simeq *\,,
	\end{equation*}
	so $\asscat(\decomp(X,x))\morphism \asscat X$ is essentially surjective for trivial reasons. Moreover, we have $\decomp(X,x)_0\simeq \{x\}$ by construction, and \cref{eq:asscat2} (which is applicable here because $\decomp(X,x)$ is Segal by construction) easily shows
	\begin{equation*}
		\Hom_{\asscat(\decomp(X,x))}(x,x)\simeq P_{x,x}\simeq \Hom_{\asscat X}(x,x)\,,
	\end{equation*}
	so $\asscat(\decomp(X,x))\morphism \asscat(X)$ is fully faithful too. This shows that the counit is an equivalence, as claimed.
	
	The argument for the unit is similar: We have to show $T\simeq \decomp(\comp T)$ for all $T\in \cat{Mon}(\An)$. Since both sides are functors $\IDelta^\op\morphism \cat{An}$ and a natural transformation between them is already given, we can do this degree-wise by \cref{thm:JoyalEquivalence}\itememph{b}. Since both sides are cartesian monoids, is suffices to check that the map in degree $1$ is an equivalence, i.e.\ that $T_1\simeq \decomp(\comp T)_1$. Write $(X,x)\simeq \comp T$. By construction we have
	\begin{equation*}
		\decomp(X,x)_1\simeq P_{x,x}\quad\text{and}\quad T_1\simeq P_{1_T,1_T}\,,
	\end{equation*}
	where as usual $1_T\colon \Delta^0\morphism T$ is the natural pointing of $T$. As observed at the very beginning of this proof, the spaces $P_{y,z}$ aren't affected by completion, hence $P_{x,x}\simeq P_{1_T,1_T}$ and we're done. 
\end{proof}
\lecture[More on $\IE_1$-monoids and $\IE_1$-groups. Group completion.\newline --- \enquote{\emph{The fact that you can write down a group or a monoid in semester 2 is sort of an accident.}}]{2020-11-26}Under the equivalence $\Cat_\infty\simeq \cat{CSAn}$ from \cref{thmdef:RezkNerve}, the construction of $\decomp$ from the proof of \cref{prop:CompletionOfMonoidsFullyFaithful} corresponds to a functor $*/\Cat_\infty\morphism\cat{Mon}(\An)$ which becomes an equivalence when restricted to the full subcategory $(*/\Cat_\infty)_{\geq 1}\subseteq */\Cat_\infty$ spanned by those $\Cc$ with $\pi_0\core\Cc\simeq *$. In diagrams,
\begin{equation*}
	\begin{tikzcd}
		*/\Cat_\infty\rar & \cat{Mon}(\An)\\
		(*/\Cat_\infty)_{\geq 1}\uar[symbol=\subseteq]\urar[iso] & 
	\end{tikzcd}
\end{equation*}
Explicitly, this functor sends a pointed $\infty$-category $(\{x\}\morphism \Cc)$ to $\Hom_\Cc(x,x)$ in degree $1$ (and then all other degrees are determined by the conditions from \cref{def:CartesianMonoids}). We thus obtain:
\begin{cor}
	If $\Cc$ is an $\infty$-category and $x\in \Cc$, then $\Hom_\Cc(x,x)$ carries a canonical structure of an $\IE_1$-monoid.
\end{cor}
\begin{defi}\label{def:E1Group}
	Let $\Cc$ be an $\infty$-category with finite products. A cartesian monoid $X$ in $\Cc$ is called a \emph{cartesian group} (or \emph{$\IE_1$-group} in the case $\Cc=\An$) if the map
	\begin{align*}
		(\pr_1,\circ)\colon X_1\times X_1&\isomorphism X_1\times X_1\\
		(f,g)&\longmapsto (f,f\circ g)
	\end{align*}
	is an equivalence. Here \enquote{$\circ$} is the composition as defined in \cref{thmdef:RezkNerve}\itememph{c}. We denote by $\Grp(\Cc)\subseteq \cat{Mon}(\Cc)$ the full sub-$\infty$-category of cartesian groups.
\end{defi}
\begin{prop}\label{prop:Grp(An)=(*/An)Connected}
	The equivalences $\cat{Mon}(\An)\simeq (*/\Cat_\infty)\simeq (*/\cat{CSAn})_{\pi_0=*}$ restrict to equivalences
	\begin{equation*}
		\begin{tikzcd}[column sep=small]
			\cat{Mon}(\An)\dar[iso]\rar[symbol=\supseteq] & \Grp(\An)\dar[iso]\\
			(*/\Cat_\infty)_{\geq 1}\dar[iso] \rar[symbol=\supseteq] & (*/\An)_{\geq 1}\dar[iso]\\
			(*/\cat{CSAn})_{\pi_0=*}\rar[symbol=\supseteq] & (*/\mathrm{const.}\ \cat{sAn})_{\pi_0=*}
		\end{tikzcd}
	\end{equation*}
	In the lower right corner we use the notation from \cref{exm:MyFirstRezkNerves}\itememph{c}.
\end{prop}
\begin{proof}[Proof sketch]
	In the lecture we noted only that $X\in \cat{Mon}(\An)$ is an $\IE_1$-group iff the set $\pi_0X_1$ with its induced ordinary monoid structure is an ordinary group.
	
	To elaborate on this a bit more, first note that we may assume $X\simeq \Hom_\Cc(x,x)$ for some $\infty$-category $\Cc$ with $\pi_0\core \Cc\simeq *$, as was argued above. If $X$ is an $\IE_1$-group, then $\pi_0\Hom_\Cc(x,x)$ must be an ordinary group, which implies that all endomorphisms of $x$ are equivalences, hence all morphisms in $\Cc$ are equivalences as $\pi_0\core \Cc\simeq *$. This proves that $\Cc$ is an anima by \cref{thm:JoyalLifting}. Conversely, if $\Cc$ is an anima, either inclusion $[1]\monomorphism J$ into the free-living isomorphism induces a trivial fibration $\Fun(J,\Cc)\isomorphism \Ar(\Cc)$. Choosing a section and composing it with the the other map $\Fun(J,\Cc)\morphism \Ar(\Cc)$ (induced by the other inclusion $[1]\monomorphism J$) yields an \enquote{inversion} map $(-)^{-1}\colon \Hom_\Cc(x,x)\morphism \Hom_\Cc(x,x)$. From this we can construct an inverse of the map in \cref{def:E1Group}
\end{proof}
\numpar{}\label{par:Grp(An)=(*/An)Connected}
The equivalence $\Grp(\An)\simeq (*/\An)_{\geq 1}$ is explicitly given as follows:
\begin{equation*}
	|\blank|\colon \Grp(\An)\doublelrmorphism[\sim][\sim](*/\An)_{\geq 1}\noloc \Omega
\end{equation*}
(sometimes the functor $|\blank| = \colimit_{\IDelta^\op}$ is also denoted \enquote{$B$} for \enquote{Bar construction}, but Fabian doesn't like that). To make sense of this, recall that the composition
\begin{equation*}
	\cat{Mon}(\An)\xrightarrow{\comp}\cat{CSAn}\morphism[\ev_0]\An
\end{equation*}
sends $X\mapsto |X^\times|$, as follows from \cref{eq:asscat1} and some unravelling. If $X$ is an $\IE_1$-group, one easily verifies $X^\times=X$ and thus $X\in \Grp(\An)$ is sent to $|X|$, as claimed above. Conversely, the composition
\begin{equation*}
	(*/\An)_{\geq 1}\xrightarrow{\decomp}\Grp(\An)\morphism[\ev_1]\An
\end{equation*}
sends a pointed connected anima $(K,k)$ to $\Hom_K(k,k)$, as argued previously. So to justify why $(*/\An)_{\geq 1}\isomorphism \Grp(\An)$ should be thought of as a \enquote{loop space functor}, we must explain why $\Omega_kK\simeq \Hom_K(k,k)$. This can be done by several arguments and I will present a different one than in the lecture. The loop space is usually defined by the left of the following pullback diagrams in $\An$:
\begin{equation*}
	\begin{tikzcd}
		\Omega_kK\vphantom{\Hom_K^L}\dar\rar\drar[pullback]& *\vphantom{K_{k/}}\dar["k"]\\
		*\rar["k"] & K
	\end{tikzcd}\quad\isomorphism\quad
	\begin{tikzcd}
		\Hom_K^L(k,k)\dar\rar\drar[pullback]& K_{k/}\dar\\
		*\rar["k"]& K
	\end{tikzcd}
\end{equation*}
The map $*\morphism K$ can be factored into the left anodyne map $*\monomorphism K_{k/}$ followed by the left fibration $K_{k/}\morphism K$, which is even a Kan fibration since $K$ is an anima. Replacing one of the $*\morphism K$ accordingly, we obtain the pullback diagram on the right, which is already a pullback in $\sSet$ as one leg is a Kan fibration (see \cref{thm:HomotopyLimits}). Its pullback is thus $\Hom_K^L(k,k)\simeq \Hom_K(k,k)$ as left-$\Hom$ anima coincide with the regular $\Hom$ anima by \cite[Digression~I Corollary~D.2]{HigherCatsII}.

In particular, we have proved another result from algebraic topology (or rather deduced it from the much more general statement of \cref{thmdef:RezkNerve}, which we didn't prove, but never mind that).
\begin{cor}[Recognition Principle for Loop Spaces, Stasheff]
	The loop functor $\Omega\colon {*/\An}\morphism \An$ lifts to an equivalence
	\begin{equation*}
		\Omega\colon (*/\An)_{\geq 1}\isomorphism \Grp(\An)\,.
	\end{equation*}
\end{cor}
Note that $\ev_1\colon \cat{Mon}(\An)\morphism \An$ preserves limits since $\cat{Mon}(\An)$ is closed under limits in $\cat{sAn}$ (the Segal condition is given by a limit and limits commute by the dual of \cref{prop:ColimitsCommute}). Colimits however are bloody complicated, and even though one can show that $\cat{Mon}(\An)$ is cocomplete, colimits in it are \emph{by far not} just colimits of underlying simplicial anima, same as colimits of ordinary monoids are much more complicated than colimits in sets.
\begin{prop}\label{prop:InftyGrp}
	The inclusion $\Grp(\An)\subseteq\cat{Mon}(\An)$ has a left adjoint called \emph{group completion} and denoted
	\begin{equation*}
		(-)^\inftygrp\colon \cat{Mon}(\An)\morphism \Grp(\An)\,.
	\end{equation*}
	It is given by $X^\inftygrp\simeq \Omega_e|X|$ \embrace{often also denoted $\Omega BX$}.
\end{prop}
\begin{proof}
	We know that $\An\subseteq \Cat_\infty$ has a left-adjoint $|\blank|\colon \Cat_\infty\morphism \An$. The unit and counit are equivalences on $*\in \An$, hence the adjunction passes to slices under it. Moreover the $(-)_{\geq 1}$-parts on both sides are clearly preserved, thus $|\blank|$ descends to a left adjoint
	\begin{equation*}
		|\blank|\colon (*/\Cat_\infty)_{\geq 1}\morphism (*/\An)_{\geq 1}
	\end{equation*}
	of the obvious inclusion in the other direction. Now use \cref{prop:Grp(An)=(*/An)Connected} to get the desired left-adjoint $(-)^\inftygrp\colon \cat{Mon}(\An)\morphism\Grp(\An)$. The explicit description follows from our calculations in \cref{par:Grp(An)=(*/An)Connected}
\end{proof}
Next we will discuss some examples. We begin with free monoids and groups.
\begin{prop}\label{prop:FreeMonoids}
	The evaluation functor $\ev_1\colon \cat{Mon}(\An)\morphism \An$ has a left adjoint $\operatorname{Free}^{\Mon}\colon \An\morphism \cat{Mon}(\An)$. It is given explicitly by the \enquote{anima of words of arbitrary length}
	\begin{equation*}
		\operatorname{Free}^{\Mon}(K)_1\simeq \coprod_{n\geq 0}K^n\,.
	\end{equation*}
\end{prop}
We postpone the proof of \cref{prop:FreeMonoids}. By the explicit construction given there, the diagram
\begin{equation*}
	\begin{tikzcd}[column sep=large]
		\Set\dar\rar["\operatorname{Free}"]& \cat{Mon}(\Set)\dar\\
		\An\rar["\operatorname{Free}^{\Mon}"] & \cat{Mon}(\An)
	\end{tikzcd}
\end{equation*}
commutes. But be aware that this is not automatic, and in fact we'll see it very much breaks once we impose commutativity. As some first examples, one has $\operatorname{Free}^{\Mon}(*)\simeq\IN$ and $\operatorname{Free}^{\Mon}(\emptyset)\simeq *$, which is initial in $\cat{Mon}(\An)$.
\begin{prop}\label{prop:FreeGroups}
	The evaluation functor $\ev_1\colon \Grp(\An)\morphism \An$ has a left-adjoint $\Free^\Grp\colon \An\morphism\Grp(\An)$ too. Explicitly, it is given by the composite
	\begin{align*}
		\An&\morphism */\An\morphism[\Sigma]*/\An\morphism[\Omega]\Grp(\An)\\
		X&\longmapsto X\sqcup *\,.
	\end{align*}
	In other words, the free $\IE_1$-group on $X$ is $\Free^\Grp(X)\simeq\Omega\Sigma X_+$, where $X_+=X\sqcup *$. As usual, the suspension functor $\Sigma\colon \An\morphism \An$ is given by the pushout diagram
	\begin{equation*}
		\begin{tikzcd}
			X\dar\rar\drar[pushout] & *\dar\\
			* \rar& \Sigma X
		\end{tikzcd}
	\end{equation*}
\end{prop}
\begin{rem*}\label{rem*:CoLimitsIn(*/An)OrAn}
	For the proof, we'll need a functor $\Sigma\colon {*/\An}\morphism */\An$ instead. It is induced by its unpointed variant, of course, but we can also define it by taking the above pushout in $*/\An$. In fact, it doesn't matter whether the pushout is taken in $*/\An$ or $\An$ since $*/\An\morphism \An$ commutes with weakly contractible colimits (but not with arbitrary ones, as I claimed before; for example, it doesn't preserve the initial object). Indeed, if $\Ii$ is any diagram shape, then a quick calculation shows $\Fun(\Ii,*/\An)\simeq (\const *)/\Fun(\Ii,\An)$. For the adjunction 
	\begin{equation*}
		\colimit_\Ii\colon \Fun(\Ii,\An)\doublelrmorphism\An\noloc \const
	\end{equation*}
	to descend to slice categories below $\const*$ and $*$, we need that these objects are mapped to each other and that unit/counit are equivalences on them. If $\Ii$ is weakly contractible, then $\colimit_\Ii (\const *)\simeq |\Ii|\simeq *$ by \cref{prop:CoLimitsInCat} and the required conditions are easily checked. Therefore, the adjunction above descends to an adjunction 
	\begin{equation*}
		\colimit_\Ii\colon \Fun(\Ii,*/\An)\simeq (\const *)/\Fun(\Ii,\An)\doublelrmorphism */\An\noloc \const
	\end{equation*}
	in this case. If you think about this for a moment, this is exactly what we need to show that $*/\An\morphism \An$ commutes with colimits over $\Ii$.
	
	Similarly, once we have chosen a basepoint $x\in X$, it doesn't matter whether we take the defining pullback of $\Omega_xX$ in $*/\An$ or in $\An$ (and then equip it with its natural basepoint). This can be seen as above, or simply by the fact that $*/\An\morphism \An$ has a left adjoint, so we can apply \cref{obs:AdjointsPreserveLimits}. However, in contrast to $\Sigma$, we can't define $\Omega$ as a functor on $\An$, since there is no canonical choice of basepoint.
\end{rem*}
\begin{proof}[Proof sketch of \cref{prop:FreeGroups}]
	The existence of a left adjoint would be immediate from Propositions~\labelcref{prop:InftyGrp,prop:FreeMonoids}, but we can give a direct argument that also yields the explicit description. We have seen in \cref{par:Grp(An)=(*/An)Connected} that the diagram
	\begin{equation*}
		\begin{tikzcd}
			\Grp(\An)\dar["|\blank|"']\rar["\ev_1"]& \An\\
			(*/\An)_{\geq 1}\urar["\Omega"',""{name=A,sloped}] & \arrow[from=1-1,to=A,phantom,"\scriptscriptstyle/\!/\!/"]
		\end{tikzcd}
	\end{equation*}
	commutes. Observe that $(-)_+=-\sqcup*\colon \An\morphism */\An$ is a left adjoint of the forgetful functor $*/\An\morphism \An$ (this is basically trivial) and that $\Sigma\colon {*/\An}\shortdoublelrmorphism */\An\noloc \Omega$ are adjoints (this we leave as an exercise---just play around with the defining pushouts/pullbacks, which can be taken in $*/\An$ by \cref{rem*:CoLimitsIn(*/An)OrAn}). Finally, $\Omega\colon (*/\An)_{\geq 1}\shortdoublelrmorphism \Grp(\An)\noloc |\blank|$ is an adjunction (even an equivalence) by \cref{par:Grp(An)=(*/An)Connected}. The assertion now follows from the fact that left adjoints compose.
\end{proof}
\begin{exm}\label{exm:MyFirstMonoidals}
	\begin{alphanumerate}
		\item The evaluation functor $\ev_1\colon \cat{Mon}(\An)\morphism \An$ factors canonically over $*/\An\morphism \An$, and the resulting functor $\ev_1\colon \cat{Mon}(\An)\morphism */\An$ has a left adjoint too. For a pointed anima $(X,x)$, we denote the corresponding left adjoint object (\enquote{free $\IE_1$-monoid with unit $x$}) by $\operatorname{Free}^{\Mon}(X,x)$. Similarly, $\ev_1\colon \Grp(\An)\morphism */\An$ has a left adjoint given on objects by $\operatorname{Free}^{\Grp}(X,x)\simeq \Free^\Mon(X,x)^\inftygrp\simeq \Omega\Sigma X$ (this equality can be seen along the lines of the proof of \cref{prop:FreeGroups}).
		
		If $(X,x)$ is connected, one actually has $\operatorname{Free}^{\Mon}(X,x)\simeq \operatorname{Free}^{\Grp}(X,x)$. Indeed, as we've seen in the proof of \cref{prop:Grp(An)=(*/An)Connected}, we only need to check that the ordinary monoid $\pi_0\operatorname{Free}^{\Mon}(X,x)_1$ is already an ordinary group. Playing around with universal properties, we see that $\pi_0\operatorname{Free}^{\Mon}(X,x)_1$ is the free ordinary monoid on the set $\pi_0 X$ with unit $[x]$, hence just $\{[x]\}$ itself since $X$ is connected, hence it already is a group.
		\item By \cref{prop:FreeMonoids}, $\operatorname{Free}^{\Mon}(\IS^1)\simeq \coprod_{n\geq 0}\IT^n$ is an infinite union of tori $\IT^n=\prod_{i=1}^n\IS^1$ and thus a reasonable geometric object. However, \cref{prop:FreeGroups} implies
		\begin{equation*}
			\operatorname{Free}^{\Grp}(\IS^1)\simeq \Omega\Sigma(\IS^1_+)\simeq \Omega(\IS^2\vee\IS^1)\,,
		\end{equation*}
		and the homotopy groups of the right-hand side are not fully known to this day. Similarly, using the pointed variant from \itememph{a} above, we get
		\begin{equation*}
			\operatorname{Free}^{\Mon}(\IS^1,*)\simeq\operatorname{Free}^{\Grp}(\IS^1,*)\simeq \Omega\Sigma(\IS^1,*)\simeq\Omega\IS^2
		\end{equation*}
		\item \lecture[A pushout computation. Monoidal $1$-categories give monoidal $\infty$-categories. Definition of algebraic and hermitian $K$-theory.]{2020-12-01}\hspace{-1ex}It is completely formal to see that $\ev_1\colon \cat{Mon}(\An)\morphism \An$ and $\ev_1\colon \Grp(\An)\morphism \An$ are represented by $\operatorname{Free}^{\Mon}(*)$ and $\operatorname{Free}^{\Grp}(*)\simeq \Free^\Mon(*)^\inftygrp$ respectively. What's not formal, however, is that $\operatorname{Free}^{\Mon}(*)\simeq \IN$ and $\operatorname{Free}^{\Grp}(*)\simeq \Omega \IS^1\simeq\IZ$, regarded as discrete simplicial anima. This really needs Propositions~\labelcref{prop:FreeMonoids,prop:FreeGroups}.
		
		Moreover, we'll see that the analogous functors are no longer represented by $\IN$ and $\IZ$ once we impose commutativity, even though they are the free $\IE_1$-monoid/group on a point and happen to be commutative. In fact they are \enquote{too commutative to be free commutative monoids} (*\emph{sphere spectrum intensifies}*).
		\item Let's for some reason compute the pushout
		\begin{equation*}
			\begin{tikzcd}
				\IN \rar["\cdot2"]\dar\drar[pushout] & \IN\dar\\
				* \rar & \IN /\!\!/ 2
			\end{tikzcd}
		\end{equation*}
		in $\cat{Mon}(\An)$. The answer is $\IN/\!\!/ 2\simeq \Omega \IR\IP^2$. To see this, first observe that the functor $\pi_0\colon \cat{Mon}(\An)
		\morphism\cat{Mon}(\Set)$ commutes with colimits, so $\pi_0(\IN/\!\!/2)=\IZ/2$ since we know how to compute pushouts in $\cat{Mon}(\Set)$. But $\IZ/2$ is a group, so $\IN/\!\!/2\in \Grp(\An)$ by \cref{prop:Grp(An)=(*/An)Connected}. In particular, since the group completion functor $(-)^\inftygrp$ commutes with colimits, we get $\IN/\!\!/2\simeq \IZ/\!\!/2$, i.e., the diagram
		\begin{equation*}
			\begin{tikzcd}
				\IZ \rar["\cdot2"]\dar\drar[pushout] & \IZ\dar\\
				* \rar & \IN /\!\!/ 2
			\end{tikzcd}
		\end{equation*}
		is a pushout in $\Grp(\An)$. Translating to $*/\An$ via \cref{prop:Grp(An)=(*/An)Connected} gives a diagram
		\begin{equation*}
			\begin{tikzcd}
				\IS^1\rar["\cdot 2"]\dar\drar[pushout] & \IS^1\dar\\
				\ID^2\rar & \IR\IP^2
			\end{tikzcd}
		\end{equation*}
		(we have replaced $*$ by the disk $\ID^2$ to make one leg of the pushout into a cofibration so that it can be computed by an ordinary pushout of CW complexes by \cref{thm:HomotopyLimits}) and translating back using \cref{par:Grp(An)=(*/An)Connected} shows $\IN/\!\!/2\simeq \Omega\IR\IP^2$, as claimed.
		\item Every monoidal $1$-category $(\Cc,\otimes)$ gives rise to a monoidal $\infty$-category, i.e.\ an object in $\cat{Mon}(\Cat_1^{(2)})\subseteq \cat{Mon}(\Cat_\infty)$. We will produce this by straightening a suitable cocartesian fibration $p^{\otimes}\colon \Cc^\otimes\morphism \IDelta^\op$ of $1$-categories. Define $\Cc^\otimes\in \Cat_1^{(2)}$ as follows: Its objects are
		\begin{equation*}
			\operatorname{obj}(\Cc^\otimes)=\coprod_{n\geq 0}\operatorname{obj}(\Cc)^n\,,
		\end{equation*}
		i.e.\ given by tuples $(n, x_1,\dotsc,x_n)$ with $[n]\in \IDelta$ and $x_i\in \Cc$. We'll usually abbreviate $x=(x_1,\dotsc,x_n)$ and simply write $(n,x)$. Morphisms are defined as
		\begin{equation*}
			\Hom_{\Cc^\otimes}\big((n,x),(m,y)\big)=\left\{(\alpha,f)\st \begin{tabular}{c}
				$\alpha\colon [m]\rightarrow [n]$ in $\IDelta$ and $f=(f_1,\dotsc,f_m)$\\
				where $f_j\colon x_{\alpha(j-1)+1}\otimes\dotsb\otimes x_{\alpha(j)}\rightarrow y_j$\\
				are morphisms in $\Cc$ for all $j=1\dotsc,m$
			\end{tabular}\right\}\,.
		\end{equation*}
		If $\alpha(j-1)+1>\alpha(j)$ for some $j$, then $x_{\alpha(j-1)+1}\otimes\dotsb\otimes x_{\alpha(j)}$ is the empty tensor product, which is the tensor unit $1_\Cc\in\Cc$ by definition.
		
		The composition of $(\alpha,f)\colon(n,x)\morphism (m,y)$ and $(\beta,g)\colon (m,y)\morphism (k,z)$ is given as follows: Its first component is $\alpha\circ\beta\colon [k]\morphism{[n]}$. For the second component, observe that we can write
		\begin{equation*}
			x_{\alpha\beta(j-1)+1}\otimes \dotsb \otimes x_{\alpha\beta(j)}=\bigotimes_{i=1}^{\beta(j)-\beta(j-1)}\left(x_{\alpha(\beta(j-1)+i-1)+1}\otimes\dotsb\otimes x_{\alpha(\beta(j-1)+i)}\right)\,.
		\end{equation*}
		The $i\ordinalth$ tensor factor on the right maps to $y_{\beta(j-1)+i}$ via $f_{\beta(j-1)+i}$. Tensoring them together and postcomposing with $g_j\colon y_{\beta(j-1)+1}\otimes\dotsb\otimes z_j$ provides the desired composition of $f$ and $g$. This finishes the construction of $\Cc^\otimes$.
		
		The functor $p^\otimes\colon \Cc^\otimes\morphism\IDelta^\op$ just extracts $[n]$ from $(n,x)$ and $\alpha$ from $(\alpha,f)$. The fibres $\Cc_n^\otimes$ of $p^\otimes$ are then obviously given by $\Cc^n$. To show that $p$ is a cocartesian fibration of $1$-categories, we must provide cocartesian lifts of morphisms in $\IDelta^\op$. Given $\alpha\colon [m]\morphism {}[n]$ in $\IDelta$ and $(n,x)\in \Cc^\otimes$, we claim that the identities can be regarded as a morphism
		\begin{equation*}
			\alpha_*\colon (n,x)\morphism \left(m,x_{\alpha(0)+1}\otimes\dotsb\otimes x_{\alpha(1)},\dotsc,x_{\alpha(m-1)+1}\otimes\dotsb\otimes x_{\alpha(m)}\right)\,.
		\end{equation*}
		It's straightforward to check that $\alpha_*$ is a cocartesian lift of $\alpha$ (note that the daunting homotopy pullbacks in \cref{def:WeirdCocartesianDefinition} become just good old pullbacks of sets/discrete anima, since we are dealing with $1$-categories).
		
		It remains to check that $\St (p^\otimes)$ satisfies the conditions from \cref{def:CartesianMonoids}. As seen above, $\St (p^\otimes)_0\simeq \Cc_0^\otimes \simeq \Cc^0\simeq *$ is a point, as desired. To verify the Segal condition, let's organize the world a little bit. Call a map in $\IDelta$ \emph{inert} if it is the inclusion of an interval and \emph{active} if it preserves the largest and the smallest element. The Segal maps $e_i\colon [1]\morphism {}[n]$ are precisely the inert maps with source $[1]$. We claim that for a general inert map $\alpha\colon [m]\morphism{[n]}$, the induced functor (given by taking cocartesian lifts) 
		\begin{equation*}
			\alpha_*\colon \Cc^m\simeq \Cc_m^\otimes \morphism \Cc_n^\otimes \simeq \Cc^n
		\end{equation*}
		simply sends $(x_1,\dotsc,x_m)\in \Cc^m$ to $(x_{\alpha(1)},\dotsc,x_{\alpha(m)})\in \Cc^n$ with no tensor products occuring. Thus the Segal condition follows immediately.
		
		As a slogan, \enquote{inerts induce forgetful functors on fibres}, whereas \enquote{actives don't forget, they just tensor}. Generally, any map in $\IDelta$ can be uniquely factored into an inert followed by an active.
		\item The construction from \itememph{e} also works if $\Cc$ is Kan enriched. In this case one can again constructed a cocartesian fibration $p^\otimes\colon \Cc^\otimes \morphism \IDelta^\op$, but of Kan-enriched categories this time (where $\IDelta^\op$ receives its discrete enrichment). Then $\N^c(\Cc^\otimes)\morphism \N^c(\IDelta^\op)\simeq \IDelta^\op$ straightens to a monoidal $\infty$-category as well. Fabian wouldn't tell us what a cocartesian fibration of Kan-enriched categories is though, since this would take---not a lot, but too much---time.
	\end{alphanumerate}
\end{exm}
%We're now very close to defining $K$-theory as $K_i(R)\coloneqq \pi_i\Omega (\Proj^\fg(R))^\inftygrp$ (or, if you prefer the Bar notation that Fabian hates, $\pi_i\Omega B(\Proj^\fg(R))$). What's left to do is to investigate $\Proj^\fg(R)$ and to turn it into an $\IE_1$-monoid.
\cref{exm:MyFirstMonoidals}\itememph{e} allows us to construct many interesting examples. All examples will turn out to be commutative (see after \cref{cor:CommutativeHorizontalAdjoints}), but that doesn't matter for now.

\numpar*{Algebraic $K$-Theory}
Let $R$ be a ring and consider $\cat{Mod}(R)$ as a monoidal category under $\oplus$. Moreover, let $\Proj(R)$ denote the sub-groupoid of spanned by finite projective $R$-modules (\enquote{vector bundles on $\Spec R$}) and their isomorphisms. This inherits a (symmetric) monoidal structure by \cref{exm:MyFirstMonoidals}\itememph{e}, so we obtain
	\begin{equation*}
		\Proj(R)\in \cat{Mon}\big(\Grpd_1^{(2)}\big)\subseteq \cat{Mon}(\An)\,.
	\end{equation*}
\begin{defi}[Quillen]
	The \emph{projective class anima} (or \emph{algebraic $K$-theory space}) of $R$ is defined as 
	\begin{equation*}
		k(R)\coloneqq \Proj(R)^\inftygrp\in \Grp(\An)\,,
	\end{equation*}
	and the \emph{higher projective class groups} (or \emph{higher $K$-groups}) of $R$ are given by
	\begin{equation*}
		K_i(R)=\pi_i\big(k(R)_1,*\big)\,.
	\end{equation*}
\end{defi}
The reason we write $k(R)$ is that the notation $K(R)$ is reserved for the $K$-theory \emph{spectrum} which we will eventually define. Note immediately that
\begin{equation*}
	K_0(R)=\pi_0\big(\Proj(R)^\inftygrp\big)=\big(\pi_0\Proj(R)\big)^\grp=\left\{\begin{tabular}{c}
		iso.\ classes of finite\\
		projective $R$-modules
	\end{tabular}\right\}^\grp\,,
\end{equation*}
where $(-)^\grp\colon \cat{Mon}(\Set)\morphism \Grp(\Set)$ denotes the ordinary group completion. This shows that $K_0(R)$ is precisely what we wanted it to be way back in the introduction, \cref{def:K0R}. We will soon see that also $K_1(R)$ can be described as in \cref{def:K1R}.


\numpar*{Hermitian $K$-Theory/Grothendieck--Witt Theory} Let $R$ be a ring, $M$ an $R\otimes R$-module and $\sigma\colon M\morphism M$ an involution that is flip-linear, i.e.\ $\sigma((a\otimes b)m)=(b\otimes a)\sigma(m)$. Moreover, assume that $M$ is finite projective when considered as an $R$-module via the map $R\simeq \IZ\otimes R\morphism R\otimes R$ (one can check that it doesn't matter if we choose this map or $R\simeq R\otimes \IZ\morphism R\otimes R$) and that the map
\begin{align*}
	R&\isomorphism \Hom_R(M,M)\\
	r&\longmapsto \big(m \mapsto (r\otimes 1)m\big)
\end{align*}
is an isomorphism. A pair $(M,\sigma)$ subject to these conditions is called an \emph{invertible module with involution} over $R$ (beware that this is non-standard terminology).

For a finite projective $R$-module $P\in \Proj (R)$ consider the group $\Hom_{R\otimes R}(P\otimes P,M)$ of $M$-valued $R$-bilinear forms on $P$. This is acted upon by $\IZ/2$ via conjugation with the flip of $P\otimes P$ and $\sigma$ on $M$. Define the groups of \emph{symmetric} and \emph{quadratic forms} on $P$ as
\begin{align*}
	\Sym_R(P,M)&\coloneqq \Hom_{R\otimes R}(P\otimes P,M)^{\IZ/2}\\
	\Quad_R(P,M)&\coloneqq \Hom_{R\otimes R}(P\otimes P,M)_{\IZ/2}\,,
\end{align*}
where $(-)^{\IZ/2}$ denotes the invariants of the $\IZ/2$-action and $(-)_{\IZ/2}$ denotes the coinvariants (i.e.\ take the coequalizer rather than the equalizer). Finally, let the group of \emph{even forms} on $P$ be
\begin{equation*}
	\Even_R(P,M)\coloneqq \im\left(\Nm\colon \Quad_R(P,M)\rightarrow \Sym_R(P,M)\right)\,,
\end{equation*}
where $\Nm$ denotes the \emph{norm map} which can be defined on general abelian groups with a $\IZ/2$-action: If $X\in \IZ/2\mhyph\Ab$ is an abelian group with $\IZ/2$ acting via an involution $\tau\colon X\morphism X$,
\begin{align*}
	\Nm\colon X_{\IZ/2}&\morphism X^{\IZ/2}\\
	[x]&\longmapsto x+\tau(x)\,.
\end{align*}
A symmetric form $q\in \Sym_R(P,M)$ is called \emph{unimodular} if the induced map
\begin{equation*}
	q_*\colon P\isomorphism \Hom_R(P,M)\eqqcolon D_M(P)
\end{equation*}
is an isomorphism. The right-hand side should be thought of the \enquote{$M$-valued dual} of $P$. This is reasonable because the assumptions on $M$ are chosen precisely to ensure that $D_M\colon \Proj(R)^\op\isomorphism \Proj(R)$ is an equivalence with inverse $D_M^\op$.

Similarly, an even or quadratic form is called \emph{unimodular} if their image in $\Sym_R(P,M)$ (via the inclusion or via $\Nm$) is unimodular. For $r\in\{\text{sym},\text{quad}, \text{even}\}$ we denote
\begin{equation*}
	\Unimod^r(P,M)=\left\{\begin{tabular}{c}
		groupoid of unimodular $r$-forms, i.e. pairs\\
		$(P,q)$, where $q$ is a unimodular $r$-form on $P$,\\
		and isomorphisms between them
	\end{tabular}\right\}
\end{equation*}
This is a symmetric monoidal $1$-groupoid via $\oplus$, hence induces a symmetric monoidal anima by \cref{exm:MyFirstMonoidals}\itememph{e}.
\begin{defi}[Karoubi]
	For $r\in\{\text{sym},\text{quad}, \text{even}\}$, the \emph{Grothendieck--Witt anima} of $(R,M)$ is given by
	\begin{equation*}
		\gw^r(R,M)\coloneqq \Unimod^r(R,M)^\inftygrp\,.
	\end{equation*}
\end{defi}
\lecture[Topological $K$-theory and its connection to deep theorems in geometric topology. Cartesian commutative monoids and groups.]{2020-12-03}To make the rather technical definitions of symmetric, quadratic, and even forms a bit clearer, we discussed some examples. Choose $R$ a commutative ring, let $M=R$ and make it an $R\otimes R$-module via the multiplication map $\mu\colon R\otimes R\morphism R$. Choosing either $\sigma=\id_R$ or $\sigma=-\id_R$, we we see that $\Sym_R(P,M)$ returns the usual notion of symmetric or skew-symmetric $R$-bilinear forms on $P$.

If $R=\IC$, we can also equip $M=\IC$ with a $\IC\otimes\IC$-module structure via
\begin{equation*}
	\IC\otimes\IC\xrightarrow{\id\otimes \overline{(-)}}\IC\otimes \IC\morphism[\mu]\IC\,,
\end{equation*}
where $\overline{(-)}\colon \IC\morphism\IC$ denotes complex conjugation, as usual. In this case, $\Sym_\IC(P,\IC)$ amounts to hermitian or skew-hermitian forms on $P$, depending on whether $\sigma=\id_\IC$ or $\sigma=-\id_\IC$.

\begin{exc}\label{exc:WhatQuad?}
	Show that $\Quad_R(P,M)$ is in bijection with the set of all pairs $(b,q)\in \Sym_R(P,M)\times \Hom_\Set(P,M_{\IZ/2})$ satisfying
	\begin{equation*}
		b(p,p)=\Nm\big(q(p)\big)\quad\text{and}\quad q(rp)=(r\otimes r)q(p) 
	\end{equation*}
	for all $p\in P$ and $r\in R$. Under this bijection, the map $\Nm\colon \Quad_R(P,M)\morphism\Sym_R(P,M)$ simply forgets $q$.
\end{exc}
What \cref{exc:WhatQuad?} means depends a little on $R$. We always assume that $R$ is commutative.
\begin{alphanumerate}
	\item If $\sigma=\id_M$, then $M_{\IZ/2}=M=M^{\IZ/2}$ and $\Nm$ is simply multiplication by $2$. So if $M$ has no $2$-torsion, then $q$ is already defined by $b$ and the equation $b(p,p)=\Nm(q(p))$. Hence the norm map $\Nm\colon \Quad_R(P,M)\morphism \Sym_R(P,M)$ is an isomorphism onto its image, which means that quadratic forms and even forms are in bijection in this case.
	\item If $\sigma=-\id_M$, then $M_{\IZ/2}=M/2$ and $M^{\IZ/2}=M[2]=2\text{-torsion of }M$. Hence $\Nm\colon M_{\IZ/2}\morphism M^{\IZ/2}$ is the zero map. If $M[2]=0$, then $b(p,p)=0$ for all $b\in \Sym_R(P,M)$ and all $p\in P$, hence $\Nm\colon \Quad_R(P,M)\morphism \Sym_R(P,M)$ is surjective, because under the identification from \cref{exc:WhatQuad?}, $(b,0)$ is always a preimage of $b$. Thus all symmetric forms are even, but in general an even form may have lots of quadratic forms that map to it.
	\item If $2\in R^\times$ is a unit and $\sigma=\id_M$, then $\Nm\colon \Quad_R(P,M)\morphism\Sym_R(P,M)$ is an isomorphism and the notions of symmetric, quadratic, and even forms all agree.
\end{alphanumerate} 

\numpar*{Topological $K$-Theory}
Consider the three categories
\begin{equation*}
	\cat{Vect}_\IR\,,\quad\cat{Eucl}_\IR\,,\quad\text{and}\quad\cat{Sph}_\IR\,. 
\end{equation*}
In all three cases, the objects are the finite-dimensional $\IR$-vector spaces equipped with their usual topology. Morphisms in $\cat{Vect}_\IR$ are linear homeomorphisms, morphisms in $\cat{Eucl}_\IR$ are arbitrary homeomorphisms, and morphisms in $\cat{Sph}_\IR$ are proper homotopy equivalences. These categories can be Kan-enriched and are (symmetric) monoidal under $\times$ (the usual product). Applying the construction from \cref{exm:MyFirstMonoidals}\itememph{f}, we obtain monoidal anima
\begin{equation*}
	\cat{\Vv ect}_\IR\,,\quad\cat{\Ee ucl}_\IR\,,\quad\text{and}\quad\cat{\Ss ph}_\IR
\end{equation*}
Observe that while $\cat{Vect}_\IR$ and $\cat{Eucl}_\IR$ are already groupoids, $\cat{Sph}_\IR$ is not, so it only becomes an anima after taking the coherent nerve, since homotopy equivalences have homotopy inverses. Also observe that the one-point compactification $(-)^+$ of topological spaces induces equivalences
\begin{equation*}
	\Hom_{\cat{\Ss ph}_\IR}(T,U)\simeq \Hom_{\core(*/\An)}(T^+,U^+)\,.
\end{equation*}
Writing $T\cong \IR^n$, $U\cong \IR^m$ (recall that the objects of $\cat{\Ss ph}_\IR$ are finite-dimensional vector spaces) we get that $T^+\cong \IS^n$ and $U^+\cong \IS^m$ are actually spheres, hence the name $\cat{\Ss ph}_\IR$.
\begin{defi}\label{def:koEtAl}
	Define $\IE_1$-groups in anima
	\begin{equation*}
		k\cat{o}=\cat{\Vv ect}_\IR^\inftygrp\,,\quad k\cat{top}=\cat{\Ee ucl}_\IR^\inftygrp\,,\quad\text{and}\quad k\cat{sph}=\cat{\Ss ph}_\IR^\inftygrp\,.
	\end{equation*}
\end{defi}
\cref{def:koEtAl} admits many variations. For example, if $X$ is a topological space, then we can consider anima
\begin{equation*}
	\cat{\Vv ect}_\IR(X)\,,\quad \cat{\Ee ucl}_\IR(X)\,,\quad\cat{\Ss ph}_\IR(X)
\end{equation*}
of vector bundles, $\IR^n$-fibre bundles, and spherical fibrations over $X$ respectively. In case $X$ is a CW complex (or more generally if some numerability conditions are satisfied), these can also be described as
\begin{equation*}
	\Hom_\An\left(X,\cat{\Vv ect}_\IR\right)\,,\quad \Hom_\An\left(X,\cat{\Ee ucl}_\IR\right)\,,\quad\text{and}\quad\Hom_\An\left(X,\cat{\Ss ph}_\IR\right)
\end{equation*}
If we believe that $\Hom_\An(X,-)\colon \An\morphism \An$ preserves $\IE_1$-groups, the universal property of group completion results in comparison maps
\begin{align*}
	\cat{\Vv ect}_\IR(X)^\inftygrp&\morphism \Hom_\An(X,k\cat{o})\\
	\cat{\Ee ucl}_\IR(X)^\inftygrp&\morphism \Hom_\An(X,k\cat{top})\\
	\cat{\Ss ph}_\IR(X)^\inftygrp&\morphism \Hom_\An(X,k\cat{sph})\,.
\end{align*}
Be aware that these are only equivalences when $X$ is a finite CW complex (or a retract of such), as we will see later. The homotopy groups of the right-hand sides are usually denoted $k\cat{o}^*(X)$, $k\cat{top}^*(X)$, and $k\cat{sph}^*(X)$ respectively, and are pretty important invariants in geometric topology.

Fabian also mentioned that although $k\cat{o}$, $k\cat{top}$, and $k\cat{sph}$ are pretty complicated objects, we can actually compute the homotopy groups of their \enquote{differences}. More precisely, for $n\neq 4$ we have that
\begin{equation*}
	 \pi_n\big(\fib(k\cat{o}\rightarrow k\cat{top})\big)\simeq \Theta^n
\end{equation*}
is the group of exotic spheres in dimension $n$, i.e.\ exotic smooth structures on $\IS^n$. Moreover,
\begin{equation*}
	\pi_n\big(\fib(k\cat{top}\rightarrow k\cat{sph})\big)\simeq L_n^\mathrm{q}\IZ\simeq \begin{cases*}
		\IZ & if $n\equiv 0\mod 4$\\
		0 & if $n\equiv 1\mod 4$\\
		\IZ/2 & if $n\equiv 2\mod 4$\\
		0 & if $n\equiv 3\mod 4$
	\end{cases*}\,.
\end{equation*}
is Wall's quadratic $L$-group of the integers. Moreover, $\pi_n(k\cat{sph})\simeq \pi_n^s$ is the $n\ordinalth$ stable homotopy group of spheres, and by the famous Bott periodicity theorem one has
\begin{equation*}
	\pi_n(k\cat{o})\simeq \begin{cases*}
		\IZ & if $n\equiv 0\mod 8$\\
		\IZ/2 & if $n\equiv 1\mod 8$\\
		\IZ/2 & if $n\equiv 2\mod 8$\\
		0 & if $n\equiv 3\mod 8$\\
		\IZ & if $n\equiv 4\mod 8$\\
		0 & if $n\equiv 5\mod 8$\\
		0 & if $n\equiv 6\mod 8$\\
		0 & if $n\equiv 7\mod 8$
	\end{cases*}\,.
\end{equation*}
\section{\texorpdfstring{$\IE_\infty$}{Einfty}-Monoids and \texorpdfstring{$\IE_\infty$}{Einfty}-Groups}
The \enquote{idea} how to impose commutativity is to replace $\IDelta^\op$ by some other category $\IGamma^\op$ (Lurie uses $\cat{Fin}_*^\op$, but Fabian decided to honour Segal's original notation) which has \enquote{flips} in it.
\begin{defi}\label{def:CartesianCommutativeMonoids}
	We denote by $\IGamma^\op$ the $1$-category whose objects are finite sets and whose morphisms are partially defined maps. Write $\langle n\rangle=\{1,\dotsc,n\}$. There is a functor
	\begin{equation*}
		\Cut\colon\IDelta^\op\morphism\IGamma^\op
	\end{equation*}
	defined on objects via $\Cut([n])=\langle n\rangle$. On a morphism $\alpha\colon [m]\morphism {[n]}$ in $\Delta$ (which then points in the other direction in $\IDelta^\op$), $\Cut(\alpha)\colon \langle n\rangle\morphism\langle m\rangle $ is defined via
	\begin{equation*}
		\Cut(\alpha)(i)=\begin{cases*}
			\text{undefined} & if $i\leq\alpha(0)$\\
			j & if $\alpha(j-1)<i\leq \alpha(j)$\\
			\text{undefined} & if $\alpha(n)<i$
		\end{cases*}\,.
	\end{equation*}
	In more invariant words, $\Cut$ sends a finite non-empty totally ordered set $I\in \IDelta^\op$ to its set of \emph{Dedekind cuts} (i.e.\ partitions into two non-empty intervals), and a map $\alpha\colon I\morphism J$ in $\IDelta$ is sent to $\alpha^*\colon \Cut(J)\morphism \Cut(I)$ which is given by taking preimages (whenever these are non-empty, otherwise it's undefined).
	
	If now $\Cc$ is an $\infty$-category with finite products, then a \emph{cartesian commutative monoid} in $\Cc$ is a functor $X\colon \IGamma^\op\morphism \Cc$ such that $X\circ \Cut\colon \IDelta^\op\morphism \Cc$ is a cartesian monoid in the sense of \cref{def:CartesianMonoids}. If it is even a cartesian group, then $X$ is called a \emph{cartesian commutative group}  in $\Cc$. We let $\CMon(\Cc),\CGrp(\Cc)\subseteq \Fun(\IGamma^\op,\Cc)$ denote the full sub-$\infty$-categories spanned by cartesian commutative monoids/groups.
\end{defi}
Time to unwind! The functor $\Cut\colon \IDelta^\op\morphism\IGamma^\op$ takes the Segal maps $e_i\colon [1]\morphism {[n]}$ in $\IDelta$ to the maps $\rho_i\colon \langle n\rangle \morphism\langle 1\rangle$ defined by
\begin{equation*}
	\rho_i(j)=\begin{cases*}
		1 & if $i=j$\\
		\text{undefined} & else
	\end{cases*}\,.
\end{equation*}
Moreover, the face maps $d_0,d_1,d_2\colon [1]\morphism{[2]}$ in $\IDelta$ are sent to $l,m,r\colon \langle 2\rangle \morphism\langle 1\rangle$, the unique maps defined on $\{1\}$, $\{1,2\}$, and $\{2\}$ respectively. So composition in a cartesian commutative monoid becomes
\begin{equation*}
	\begin{tikzcd}[column sep=2em]
		\mu\colon X_1\times X_1& X_2\morphism[m]X_1\lar["\sim", "{(l,r)}"']
	\end{tikzcd}\,.
\end{equation*}
But consider the flip map $\operatorname{flip}\colon \langle 2\rangle \morphism\langle 2\rangle$ that swaps $1$ and $2$. Then $m\circ \operatorname{flip}=m$, $r\circ\operatorname{flip}=l$, and $l\circ \operatorname{flip}=r$ hold in $\IGamma^\op$, so the diagram
\begin{equation*}
	\begin{tikzcd}[row sep=small]
		X_1\times X_1\ar[dd,"\text{flip factors}"']\drar[bend left=20,"\mu"] & \\
		\phantom{X}\rar[phantom, pos=0.4, "\scriptscriptstyle/\!/\!/"] & X_1\\
		X_1\times X_1\urar[bend right=20, "\mu"'] &
	\end{tikzcd}
\end{equation*}
commutes. So it really makes sense to think of $X$ as commutative!
\begin{exc}
	If $\Cc$ is a $1$-category, show that $\Cut^*\colon \Fun(\IGamma^\op,\Cc)\morphism\Fun(\IDelta^\op,\Cc)$ restricts to a fully faithful functor $\CMon(\Cc)\morphism\Mon(\Cc)$. Note that this is false for general $\infty$-categories, even for $\Cc=\Cat_1^{(2)}$!
\end{exc}
Similar to \cref{exm:MyFirstMonoidals}\itememph{e}, any symmetric monoidal $1$-category $(\Cc,\otimes)$ gives rise to an object in $\CMon(\Cat_1^{(2)})\subseteq \CMon(\Cat_\infty)$. Similar to the monoidal case, this is constructed from a cocartesian fibration $p^\otimes\colon \Cc^\otimes\morphism \IGamma^\op$.

Let's briefly sketch the construction. Objects of $\Cc^\otimes$ are pairs $(n,x_1,\dotsc,x_n)$, where $\langle n\rangle \in \IGamma^\op$ and $x_1,\dotsc,x_n\in \Cc$. Morphisms $(n,x)\morphism (m,y)$ comprise the data of a map $\alpha\colon \langle n\rangle \morphism\langle m\rangle $ in $\IGamma^\op$ together with maps $f_j\colon \bigotimes_{i\in\alpha^{-1}(j)}x_i\morphism y_j$ for all $j=1,\dotsc,m$. Composition is defined in the \enquote{obvious} way, using the braiding $\sigma$, and to see that composition is associative one has to use $\sigma^2=\id$. If you are confused by this braiding stuff: In a nutshell, a \emph{braiding} of a monoidal category is a choice of isomorphisms $\sigma_{x,y}\colon x\otimes y\isomorphism y\otimes x$ subject to some naturality conditions. In this terminology, a symmetric monoidal category is a braided monoidal category for which $\sigma_{x,y}\circ \sigma_{y,x}=\id$.

One can check that the cocartesian fibration $p_\mathrm{mon}^\otimes\colon\Cc_\mathrm{mon}^\otimes\morphism\IDelta^\op$ from \cref{exm:MyFirstMonoidals}\itememph{e} fits into a pullback diagram
\begin{equation*}
	\begin{tikzcd}
		\Cc_\mathrm{mon}^\otimes\dar["p_\mathrm{mon}^\otimes"']\rar\drar[pullback] & \Cc^\otimes\dar["p^\otimes"]\\
		\IDelta^\op\rar & \IGamma^\op
	\end{tikzcd}
\end{equation*}
It turns out that the diagram
\begin{equation*}
	\begin{tikzcd}
			\CMon\big(\Cat_1^{(2)}\big)\rar["\Cut^*"]\dar[iso] & \Mon\big(\Cat_1^{(2)}\big)\dar[iso]\\
		\cat{SymMonCat}_1^{(2)}\rar["\text{forget}"]& \cat{MonCat}_1^{(2)}
	\end{tikzcd}
\end{equation*}
commutes (we never defined the bottom categories, but if you sit down for a while you will surely come up with suitable a definition of the $2$-category of symmetric/arbitrary monoidal $1$-categories). However, a monoidal category can have many symmetries, so the horizontal functors are not at all fully faithful! For example, let $(\Cc,\otimes)$ be the category of $\IZ$-graded $R$-modules equipped with the graded tensor product. Any unit $u\in R^\times$ defines a braiding $\tau_u$ on $\Cc$ via $\tau_u\colon X\otimes Y\isomorphism Y\otimes X$ given by $\tau_u(x\otimes y)=u^{|x||y|}y\otimes x$ on elementary tensors. If $u^2=1$, then this braiding defines a symmetric monoidal structure. In particular, there can be many of these! So commutativity is a \emph{structure}, not a \emph{property}.

\numpar*{Semi-Additive and Additive $\infty$-Categories}
\lecture[Semi-additive and additive $\infty$-categories, monoids and groups in these.]{2020-12-08} An $\infty$-category is called \emph{semi-additive} if it admits finite products and finite coproducts, its initial and terminal object agree, and for any $x,y\in \Cc$ the natural map
\begin{equation*}
	\begin{pmatrix}
		\id_x & 0\\
		0 & \id_y
	\end{pmatrix}\colon x\sqcup y\isomorphism x\times y
\end{equation*}
is an equivalence. Here $0\colon x\morphism 0\morphism y$ denotes the unique (up to contractible choice) map in $\Hom_\Cc(x,y)$ factoring through an initial/terminal object which we also denote $0\in \Cc$. If $\Cc$ is semi-additive, then we'll usually denote its unified product and coproduct by $\oplus$.

We call $\Cc$ \emph{additive} if also the shear map
\begin{equation*}
	\begin{pmatrix}
		\id_x & \id_x\\
		0 & \id_x
	\end{pmatrix}\colon x\oplus x\isomorphism x\oplus x
\end{equation*}
is an equivalence for all $x\in \Cc$. The typical source of examples is everything that has to do with abelian groups, so for example $\Kk(\IZ)$ and the derived category $\Dd(\IZ)$ are additive.
\begin{prop}\label{prop:CMonOfSemiAdditive}
	If $\Cc$ is a semi-additive $\infty$-category, then the forgetful maps
	\begin{equation*}
		\CMon(\Cc)\isomorphism\Mon(\Cc)\isomorphism \Cc
	\end{equation*}
	are equivalences. If $\Cc$ is additive, then the same holds true for
	\begin{equation*}
		\CGrp(\Cc)\isomorphism\Grp(\Cc)\isomorphism \Cc\,.
	\end{equation*}
\end{prop}
\begin{cor}\label{cor:HomSemiAdditveFactorsThroughCGrpAn}
	If $\Cc$ is an additive $\infty$-category, then there is a canonical lift
	\begin{equation*}
		\Hom_\Cc\colon \Cc^\op\times \Cc\morphism \CGrp(\An)\,.
	\end{equation*}
	If $\Cc$ is only semi-additive, one still gets a lift to $\CMon(\An)$.
\end{cor}
\begin{proof*}
	In general, if $F\colon \Cc\morphism\Dd$ is a finite product-preserving functor, then the induced functor $F_*\colon \Fun(\IGamma^\op,\Cc)\morphism \Fun(\IGamma^\op,\Dd)$ preserves the Segal condition and also the condition from \cref{def:E1Group}, hence it restricts to functors $F_*\colon \CMon(\Cc)\morphism\CMon(\Dd)$ and $F_*\colon \CGrp(\Cc)\morphism\CGrp(\Dd)$.
	
	We can't apply this directly to our situation, since $\Hom_\Cc\colon \Cc^\op\times\Cc\morphism\An$ doesn't preserve finite products---or rather it is too good at respecting products, as
	\begin{equation*}
		\Hom_\Cc\left(\bigoplus_{i=1}^nx_i,\bigoplus_{i=1}^ny_i\right)\simeq \prod_{i,j=1}^n\Hom_\Cc(x_i,y_j)\,,
	\end{equation*}
	of which the diagonal $\prod_{i=1}^n\Hom_\Cc(x_i,y_i)$ is only a factor.
	
	At least $\Hom_\Cc(x,-)\colon \Cc\morphism\An$ preserves products for all $x\in \Cc$, whence it induces a functor $\Hom_\Cc(x,-)_*\colon \CGrp(\Cc)\morphism\CGrp(\An)$. But if $\Cc$ is additive, then $\CGrp(\Cc)\simeq \Cc$ by \cref{prop:CMonOfSemiAdditive}, which provides the desired lift $\Hom_\Cc(x,-)\colon \Cc\morphism\CGrp(\An)$. To paste these lifts together into a lift $\Hom_\Cc\colon\Cc^\op\times \Cc\morphism \CGrp(\An)$ as well, consider the composite
	\begin{equation*}
		\Fun(\Cc,\An)\morphism\Fun\big(\Fun(\IGamma^\op,\Cc),\Fun(\IGamma^\op,\An)\big)\morphism \Fun\big(\CGrp(\Cc),\Fun(\IGamma^\op,\An)\big)\,.
	\end{equation*}
	If we restrict to the full subcategory $\Fun^\times(\Cc,\An)\subseteq \Fun(\Cc,\An)$ of finite product-preserving functors, it lands in $\Fun(\CGrp(\Cc),\CGrp(\An))$, as argued above. Moreover, if $\Cc$ is additive, then $\CGrp(\Cc)\simeq \Cc$ by \cref{prop:CMonOfSemiAdditive}. Now $\Hom_\Cc\colon \Cc^\op\morphism\Fun(\Cc,\An)$ has image in $\Fun^\times(\Cc,\An)$, hence we may compose it with the above to obtain a functor
	\begin{equation*}
		\Hom_\Cc\colon \Cc^\op\morphism\Fun\big(\Cc,\CGrp(\An)\big)\,,
	\end{equation*}
	as desired.
	
	If $\Cc$ is only semi-additive, then the argument still works with $\CMon(-)$ instead of $\CGrp(-)$ everywhere. Moreover, one can check (but we won't do that here) that if we we use the (semi-)additive structure on $\Cc^\op$ instead to do the constructions above, we still end up with the same functor $\Hom_\Cc\colon \Cc^\op\times \Cc\morphism\CGrp(\An)$.
\end{proof*}
\begin{proof}[Proof sketch of \cref{prop:CMonOfSemiAdditive}]
	The key to the proof is the following claim:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}] \itshape Let $\Ii\in\{\IDelta^\op,\IGamma^\op\}$. Given a functor $X\colon \Ii\morphism\Cc$ satisfying $X_0\simeq 0$, then $X$ satisfies the Segal condition iff it is left-Kan extended from $X_{|\Ii_{\leq 1}}$ along $p\colon \Ii_{\leq 1}\morphism\Ii$.
	\end{alphanumerate}
	To conclude the statement of the proposition from \itememph{\boxtimes}, write $\Fun(\Ii_{\leq 1},\Cc)_0\subseteq \Fun(\Ii_{\leq 1},\Cc)$ for the full subcategory of functors $F$ satisfying $F(0)\simeq 0$. Since $0\in \Cc$ is initial and terminal, one easily checks that $\Cc\isomorphism\Fun(\Ii_{\leq 1},\Cc)_0$, sending $x\in \Cc$ to the unique (up to contractible choice) functor $F_x$ satisfying $F_x(0)\simeq 0$ and $F_x(1)\simeq x$, is an equivalence. Moreover,
	\begin{equation*}
		\Fun(\Ii_{\leq 1},\Cc)_0\subseteq \Fun(\Ii_{\leq 1},\Cc)\xrightarrow{\Lan_p}\Fun(\Ii,\Cc)
	\end{equation*}
	is fully faithful by \cref{cor:FullyFaithfulKanExtension}, and \itememph{\boxtimes} precisely says that its essential image is $\Mon(\Cc)$ for $\Ii=\IDelta^\op$ or $\CMon(\Cc)$ for $\Ii=\IGamma^\op$. This shows $\Mon(\Cc)\simeq \Cc\simeq \CMon(\Cc)$, as required. If $\Cc$ is additive, then the image of $x\in \Cc$ under the above composite is automatically a cartesian group: Indeed, after an easy unravelling, the condition from \cref{def:E1Group} translates into the condition that the shear map on $x$ be an equivalence, which is guaranteed by $\Cc$ being additive.
	
	To prove \itememph{\boxtimes}, first note that we get a natural counit transformation $\Lan_p X_{|\Ii_{\leq 1}}\Rightarrow X$ for free, so whether this is an equivalence can be checked on objects. Recall from \cref{thm:KanExtension} that
	\begin{equation*}
		\Lan_p X_{|\Ii_{\leq 1}}(n)\simeq \colimit_{i\in \Ii_{\leq 1}/n}X_i
	\end{equation*}
	(it will follow from the discussion below that these colimits exist in $\Cc$, so the theorem is indeed applicable). Therefore we have to understand the slice categories $\IGamma_{\leq 1}^\op/\langle n\rangle$ and $\IDelta_{\leq 1}^\op/[n]\simeq ([n]/\IDelta_{\leq 1})^\op$. So let's describe $[n]/\IDelta_{\leq 1}$, first in words and then in a picture. Its vertices are given by maps $[n]\morphism {[1]}$ and $[n]\morphism {[0]}$ in $\IDelta$. There's only one of the latter kind and it is denoted $0$ (depicted on the right). There are $n+2$ maps $[n]\morphism {[1]}$: One that is constantly $0$, one that is constantly $1$ (depicted on the top and on the bottom), and $n$ surjective maps (depicted on the left). Moreover, there's a bunch of non-degenerate edges. The pink ones are those induced by $0\colon [0]\morphism {[1]}$ and $0\colon [1]\morphism {[1]}$, the purple ones are those induced by $1\colon [0]\morphism{[1]}$ and $1\colon [1]\morphism{[1]}$, and finally the black ones are induced by the unique morphism $[1]\morphism {[0]}$.
	\begin{center}
	\begin{tikzpicture}[x=0.6cm,y=0.6cm, line cap=round]
		\fill (0,0) circle (0.5ex) coordinate (A);
		\fill (0,-1) circle (0.5ex) coordinate (B);
		\fill (0,-3) circle (0.5ex) coordinate (C);
		\fill (3,-4) circle (0.5ex) coordinate (D);
		\fill (3,1) circle (0.5ex) coordinate (E);
		\node[rotate=-90] at (0,-2) {$\dotso$};
		\fill (6,-1.5) circle (0.5ex) coordinate (F);
		\node[left=1ex]  at (A) {$0\dotso01$};
		\node[left=1ex] (001) at (B) {$0\dotso11$};
		\node[left=1ex] (011) at (C) {$01\dotso1$};
		\node[below=0.5ex] (111) at (D) {$1\dotso1$};
		\node[above=0.5ex] (000) at (E) {$0\dotso0$};
		\node[right=1ex] at (F) {$0$};
		\path (001.south) -- (011.north) node[pos=0.5,sloped] {$\dotso$};
		\draw[dotted, rounded corners=2] (1ex,1ex) to[out=0,in=150] (3.6cm+1ex,-0.9cm+1ex) to ++ (0,-2ex) to[out=210,in=0] (1ex,-1.8cm-1ex) to (-1ex,-1.8cm-1ex) to (-1ex,1ex) to (1ex,1ex);
		%\draw[dotted, rounded corners=2, shift={(F)}] (1ex,1ex) -- (1ex,-1ex) -- (-1ex,-1ex) -- (-1ex,1ex) -- cycle;
		% pink
		\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=20] (A) to (E);
		\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=10] (B) to (E);
		\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=5] (C) to (E);
		\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=10] (D) to (E);
		\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend right=45] (F) to (E);
		\draw[FabiansPink,-to,looseness=4] (000.115) to[out=115,in=65] (000.65);
		%purple
		\draw[FabiansPurple!67!FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=5] (A) to (D);
		\draw[FabiansPurple!67!FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend right=15] (B) to (D);
		\draw[FabiansPurple!67!FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend right=20] (C) to (D);
		\draw[FabiansPurple!67!FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=15] (E) to (D);
		\draw[FabiansPurple!67!FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend left=45] (F) to (D);
		\draw[FabiansPurple!67!FabiansPink,-to,looseness=4] (111.-115) to[out=-115,in=-65] (111.-65);
		% black
		\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend left=15] (A) to (F);
		\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend right=5] (B) to (F);
		\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend right=15] (C) to (F);
		\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend right=20] (D) to (F);
		\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend left=20] (E) to (F);
	\end{tikzpicture}
	\end{center}

	However, the punchline is that all of this doesn't really matter, since the dotted part turns out to be consisting of the vertices on the left and $0$ on the right turns out to be final (in the lecture we claimed that already the vertices on the left are final, but I think that's not true). To prove this, verify the criterion from \cref{thm:JoyalQuillenThmA}\itememph{b} and use that the slice category in question contain the respective arrow starting at $0$ as a terminal object. After passing to $\IDelta_{\leq 1}^\op/[n]$ instead of $[n]/\IDelta$, the dotted part becomes cofinal, hence the colimit in question can be taken over the dotted part only. But the $0$-vertex on the right is mapped to $X_0\simeq 0$ and there are no edges between the vertices on the left, hence it's easy to see that the colimit over the dotted part is just $X_1^{\oplus n}$. This is precisely what we wanted to show!
	
	For $\IGamma^\op/\langle n\rangle$, we can draw a similar picture:
	\begin{center}
		
		\begin{tikzpicture}[x=0.6cm,y=0.6cm, line cap=round]
			\fill (0,0) circle (0.5ex) coordinate (A);
			\fill (0,-1) circle (0.5ex) coordinate (B);
			\fill (0,-3) circle (0.5ex) coordinate (C);
			\fill (3,-1.5) circle (0.5ex) coordinate (D);
			\node[rotate=-90] at (0,-2.065) {$\dotso$};
			\fill (6,-1.5) circle (0.5ex) coordinate (F);
			\node[left=1ex]  at (A) {$1$};
			\node[left=1ex] (001) at (B) {$2$};
			\node[left=1ex] (011) at (C) {$n$};
			\node[right=0.5ex] (111) at (D) {$\emptyset$};
			\node[right=1ex] at (F) {$\emptyset$};
			\path (001.north) -- (011.south) node[pos=0.5,sloped] {$\dotso$};
			\draw[dotted, rounded corners=2] (-1ex,-1.8cm-1ex) to (-1ex,1ex) to[bend left] (3.6cm+1ex,-0.9cm+1ex) to ++ (0,-2ex) to[bend left]  cycle;
			\draw[dotted, rounded corners=2] (1.5,-1.65) to[out=90,in=90] (5,-1.65) to[out=-90,in=-90] cycle;
			% pink
			\draw[FabiansPink,-to,looseness=4] (111.-115) to[out=-115,in=-65] (111.-65);
			\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex] (D) -- (A);
			\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex] (D) -- (B);
			\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex] (D) -- (C);
			\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend right=20] (111.east) to (F);
			\draw[FabiansPink,-to,shorten <=1.25ex,shorten >=1.25ex,bend right=20] (F) to (111.east);
			%purple
			% black
			\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend right] (F) to (A);
			\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend right] (F) to (B);
			\draw[-to,shorten <=1.25ex,shorten >=1.25ex,bend left] (F) to (C);
		\end{tikzpicture}
	\end{center}
	The vertices of $\IGamma^\op/\langle n\rangle$ consist of partially defined maps $\langle 0\rangle \morphism\langle n\rangle$ and $\langle 0\rangle \morphism\langle n\rangle$. As $\langle 0\rangle=\emptyset$, there is only one such map of the first kind, depicted by the vertex on the right. The vertex in the middle represents the unique nowhere-defined map $\langle 1\rangle\morphism \langle n\rangle$, and the vertices on the right correspond to the maps $\langle 1\rangle\morphism \langle n\rangle$ which are actually defined on $1$. Again, the dotted part (i.e.\ everything except the vertex in the middle) is cofinal and the colimit over it evaluates to $X_1^{\oplus n}$ since the vertex on the right is sent to $X_0\simeq 0$.
\end{proof}


Since $\Dd_{\geq 0}(\IZ)$ is additive, a simple consequence of \cref{prop:CMonOfSemiAdditive} is that the Eilenberg--MacLane functor from Very Long Example~\cref{exm:EilenberMacLane} lifts to a functor
\begin{equation*}
	K\colon \Dd_{\geq 0}(\IZ)\morphism\CGrp(\An)\,.
\end{equation*}
Indeed, $K$ is a right-adjoint by construction, hence it preserves products, so we can use the argument from the proof of \cref{cor:HomSemiAdditveFactorsThroughCGrpAn} to produce the desired lift. We will soon extend this further (in \cref{exm:MyFirstSpectra}\itememph{c})!

So Eilenberg--MacLane anima give rise to $\IE_\infty$-groups. Another source of examples for $\IE_\infty$-monoids/groups is
\begin{equation*}
	\CMon(\Kan)\morphism \CMon(\An)\quad\text{and}\quad \CGrp(\Kan)\morphism \CGrp(\An)\,,
\end{equation*}
(again note that $\Kan\morphism \An$ preserves products), but these are essentially the same examples: It is a theorem of Dold--Thom, that a connected commutative monoid in Kan complexes has underlying anima a \emph{gem} (\enquote{generalized Eilenberg--MacLane space}; we defined these things in Very Long Example~\cref{exm:EilenberMacLane}). The same then holds for not necessarily connected commutative groups in Kan complexes, since all connected components are equivalent.
\begin{prop}\label{prop:RealizationCommutesWithFiniteProducts}
	The realization functor $|\blank|\colon \cat{sAn}\morphism\An$ preserves finite products.
\end{prop}
\begin{proof}
	We compute
	\begin{align*}
		|M\times N|\simeq\colimit_{[n]\in\IDelta^\op}\left(M_n\times N_n\right)&\simeq \colimit_{([n],[m])\in \IDelta^\op\times \IDelta^\op}\left(M_n\times N_m\right)\\
		&\simeq \colimit_{[n]\in\IDelta^\op}\left(M_n\times \colimit_{[m]\in\IDelta^\op}N_m\right)\\
		&\simeq \left(\colimit_{[n]\in\IDelta^\op}M_n\right)\times \left(\colimit_{[m]\in\IDelta^\op}N_m\right)\\
		&\simeq |M|\times |N|\,.
	\end{align*}
	For the second equivalence see \cref{exc:IDeltaOpSifted} below. The third equivalence follows from \cref{prop:ColimitsCommute} together with the fact that $M_n\times -$ commutes with arbitrary colimits. Indeed, for any $X\in\An$ the functor $X\times-\colon \An\morphism\An$ is a left adjoint of $\Hom_\An(X,-)$. Applying the same argument to $-\times \colimit_{\IDelta^\op}N_m$ gives the fourth equivalence.
\end{proof}
\begin{exc}\label{exc:IDeltaOpSifted}
	Show that the diagonal $\Delta\colon \IDelta^\op\morphism\IDelta^\op\times \IDelta^\op$ is cofinal as a map of $\infty$-categories. In other words, $\IDelta^\op$ is \emph{sifted}.
\end{exc}
\begin{proof*}
	By \cref{thm:JoyalQuillenThmA}\itememph{b} we need to check that $\IDelta^\op\times_{\IDelta^\op\times \IDelta^\op}([m],[n])/(\IDelta^\op\times \IDelta^\op)$ is weakly contractible for all $[m],[n]\in \IDelta^\op$. Note that we may form the slice category as a $1$-category, since the nerve functor commutes with limits. Also note that we may replace the slice category by its opposite $\Ss_{m,n}\coloneqq\IDelta\times_{\IDelta\times \IDelta}(\IDelta\times \IDelta)/([m],[n])$ for convenience.
	
	Unravelling definitions, we find that objects in $\Ss_{m,n}$ can be thought of as maps of posets $\alpha\colon [i]\morphism {}[m]\times [n]$. Any such map factors uniquely into a composition $[i]\epimorphism{} [j]\monomorphism{} [m]\times [n]$ of a surjective and an injective map. This defines a functor $r\colon \Ss_{m,n}\morphism\Cc_{m,n}$ into the category $\Cc_{m,n}$ of non-empty linearly ordered subposets of $[m]\times [n]$ ($\Cc_{m,n}$ is partially ordered by inclusion). But conversely, any such subposet is given by an injective map $[j]\monomorphism {}[m]\times [n]$ for some $j\leq m+n+1$, hence we get an inclusion $s\colon \Cc_{m,n}\morphism \Ss_{m,n}$ in the reverse direction. Clearly $r\circ s=\id_{\Cc_{m,n}}$, whereas the surjections $[i]\epimorphism{} [j]$ define a natural transformation $\id_{\Ss_{m,n}}\Rightarrow s\circ r$.
	
	This shows that $\Ss_{m,n}$ and $\Cc_{m,n}$ are weakly (and even strongly) homotopy equivalent after taking nerves. Now if we recall \cite[Definition~V.4.7]{HigherCatsI}, we recognize $\Cc_{m,n}$ as the barycentric subdivision $\operatorname{sd}(\Delta^m\times \Delta^n)$, which is weakly contractible because $\Delta^m\times \Delta^n$ is.
\end{proof*}
\begin{rem*}\label{rem*:RealizationOmega}
	Recall that we have an adjunction
	\begin{equation*}
		|\blank|\colon \Mon(\An)\doublelrmorphism */\An\colon \Omega\,.
	\end{equation*}
	Although this follows from stuff we did before, I got quite a bit confused since for example \cref{par:Grp(An)=(*/An)Connected} says something slightly different. So it's perhaps worth to spell out where this adjunction actually comes from.
	
	For a pointed anima $(X,x)$, let $X_x$ denote the connected component containing $x$. Then $\Omega_xX\simeq \Omega_xX_x$, so the equivalence $\Omega\colon (*/\An)_{\geq 1}\isomorphism\Grp(\An)$ from \cref{par:Grp(An)=(*/An)Connected} extends to a functor $\Omega\colon {*/\An}\morphism \Grp(\An)$. Now if $M\in \Mon(\An)$ is an $\IE_1$-monoid, we can compute
	\begin{align*}
		\Hom_{\Mon(\An)}(M,\Omega_xX)&\simeq \Hom_{\Grp(\An)}(M^\inftygrp,\Omega_xX_x)\\
		&\simeq \Hom_{\Grp(\An)}\big(\Omega_e|M|,\Omega_xX_x\big)\\
		&\simeq \Hom_{(*/\An)_{\geq 1}}\big(|M|,X_x\big)\\
		&\simeq \Hom_{*/\An}\big(|M|,X\big)\,,
	\end{align*}
	which establishes the desired adjunction. The second equivalence follows from \cref{prop:InftyGrp}, the third equivalence uses that $\Omega\colon (*/\An)_{\geq 1}\isomorphism\Grp(\An)$ is an equivalence, and the fourth equivalence follows from the fact that $|M|$ is connected, hence any pointed map $|M|\morphism X$ only hits the connected component $X_x$. Also recall \cref{rem:Realization}, which ensures that the different meanings of $|\blank|$ ($\colimit_{\IDelta^\op}$ or localization of an $\infty$-category at all its morphisms) are actually compatible.
\end{rem*}
Now $|\blank|$ and $\Omega$ both preserve finite products---the former by \cref{prop:RealizationCommutesWithFiniteProducts}, the latter since it is a right-adjoint. So both functors preserve the Segal condition. Therefore the adjunction obtained from \cref{rem*:RealizationOmega} after applying $\Fun(\IGamma^\op,-)$ on both sides restricts to an adjunction
\begin{equation}\label{eq:BOmegaAdjunction}
	B\colon \CMon\big(\Mon(\An)\big)\doublelrmorphism \CMon(*/\An)\noloc \Omega
\end{equation}
(even though Fabian doesn't like to use $B$ instead of $|\blank|$, he does it here since we will soon have both $B$ and $|\blank|$ in one diagram). Now it is easy to see that the forgetful map $\CMon(*/\Cc)\morphism\CMon(\Cc)$ is an equivalence for any $\infty$-category $\Cc$ with finite products (and thus a terminal object $*\in \Cc$). We claim that also%\setcounter{smallerdummy}{0}
\begin{equation}\label{eq:EckmannHilton}
	\begin{tikzcd}[row sep=small]
		\CMon\big(\Mon(\Cc)\big)\ar[dd,iso]\drar[bend left=20,"\mathrm{forget}_*","\sim"{swap,sloped}]& \\
		\phantom{X}\rar[phantom, pos=0.4, "\scriptscriptstyle/\!/\!/"]&\CMon(\Cc)\\
		\Mon\big(\CMon(\Cc)\big)\urar[bend right=20,iso,"\mathrm{forget}"'] &
	\end{tikzcd}
\end{equation}
commutes (the forgetful functors are given by evaluation in degree $1$ of course). Once we have this, we will obtain the following statement (which is from the future, as its number suggests).
\addtocounter{dummy}{2}
\begin{cor}\label{cor:CommutativeHorizontalAdjoints}
	There is a commutative diagram of horizontal adjunctionts
	\begin{equation*}
		\begin{tikzcd}
			\CMon(\An)\rar[shift left=0.45ex, "B"]\dar["\Cut^*"'] & \CMon(\An)\lar[shift left=0.45ex,"\Omega"]\dar["\ev_1"]\\
			\Mon(\An)\rar[shift left=0.45ex, "|\blank|"] & */\An\lar[shift left=0.45ex,"\Omega"]
		\end{tikzcd}
	\end{equation*}
	Restricting $B$ to the full subcategory $\CGrp(\An)\subseteq\CMon(\An)$ gives a fully faithful functor $B\colon \CGrp(\An)\morphism\CMon(\An)$. Moreover, $\Omega$ from the top row takes values in $\CGrp(\An)$ and the composite $\Omega B\colon \CMon(\An)\morphism\CGrp(\An)$ is a left adjoint to $\CGrp(\An)\subseteq \CMon(\An)$.
\end{cor}
\begin{proof*}
	We construct the diagram and prove commutativity first. The bottom row is already known. After identifying $\CMon(*/\An)\simeq \CMon(\An)$ and $\CMon(\An)\simeq \CMon(\Mon(\An))$, the upper row becomes \cref{eq:BOmegaAdjunction}. To see that the diagram commutes, we first check that the these identifications transform the forgetful functor $\CMon(\Mon(\An))\morphism\Mon(\An)$ into $\Cut^*\colon \CMon(\An)\morphism \Mon(\An)$. Indeed, this follows easily from \cref{eq:EckmannHilton}. Now both vertical arrows are of the form $\mathrm{forget}\colon \CMon(-)\morphism (-)$, from which commutativity of the diagram is clear.
	
	Next we check that $\Omega$ takes values in $\CGrp(\An)$. It suffices to check that ${\Cut^*}\circ\Omega$ lands in $\Grp(\An)$ (that's just how $\IE_\infty$-groups are defined). But ${\Cut^*}\circ \Omega\simeq \Omega\circ\ev_1$ and the right-hand side takes values in $\Grp(\An)$ by \cref{par:Grp(An)=(*/An)Connected}. 
	
	In particular, the top row adjunction restricts to an adjunction
	\begin{equation*}
		B\colon \CGrp(\An)\shortdoublelrmorphism \CMon(\An)\noloc \Omega\,.
	\end{equation*}
	To show that $B$ is fully faithful on $\CGrp(\An)$, it suffices therefore to check that the unit $\id\Rightarrow \Omega B$ is an equivalence. Equivalences of $\IE_\infty$-groups can be detected on underlying $\IE_1$-groups (in fact, even on underlying anima, i.e.\ after applying $\ev_1$). So it suffices that $\Cut^*\Rightarrow \Cut^*\Omega B$ is an equivalence. But $\Cut^*\Omega B\simeq \Omega\ev_1 B\simeq \Omega|\Cut^*|$, and if $G$ is an $\IE_\infty$-group, then $\Omega|\Cut^*G|\simeq (\Cut^*G)^\inftygrp\simeq G$ by \cref{prop:InftyGrp}. This finishes the proof that $B_{|\CGrp(\An)}$ is fully faithful.
	
	Let $\Cc\subseteq \CMon(\An)$ denote the essential image of $B_{|\CGrp(\An)}$. Then $B\colon \CGrp(\An)\isomorphism\Cc$ is an equivalence, hence its right adjoint $\Omega\colon \Cc\morphism\CGrp(\An)$ is an equivalence too. For $M\in \CMon(\An)$ and $G\in \CGrp(\An)$ we may thus compute
	\begin{align*}
		\Hom_{\CGrp(\An)}(\Omega BM,G)&\simeq \Hom_{\CGrp(\An)}(\Omega BM,\Omega BG)\\
		&\simeq \Hom_\Cc(BM,BG)\\
		&\simeq \Hom_{\CMon(\An)}(M,\Omega BG)\\
		&\simeq \Hom_{\CMon(\An)}(M,G)\,,
	\end{align*}
	where we also used $G\simeq \Omega BG$ twice. This shows that $\Omega B\colon \CMon(\An)\morphism\CGrp(\An)$ is a left adjoint of the inclusion $\CGrp(\An)\subseteq \CMon(\An)$.
\end{proof*}
In particular, all examples from the end of the previous section, i.e.\ $k(R)$, $\gw^r(R)$, $k\mathrm{o}$, $k\mathrm{top}$, and $k\mathrm{sph}$, are canonically $\IE_\infty$-groups, since they arise as group completions of $\IE_\infty$-monoids.

Also note that $B\colon \CMon(\An)\morphism\CMon(\An)$ actually takes values in $\CGrp(\An)$ (just like $\Omega$ does). Indeed, as argued in the proof of \cref{prop:Grp(An)=(*/An)Connected}, it suffices to check that the ordinary monoids $\pi_0(BM)_1$ are groups for all $M\in \CMon(\An)$. But in fact $\pi_0(BM)_1\simeq *$ is always a trivial group!

Moreover, we get a commutative solid diagram
\begin{equation*}
	\begin{tikzcd}[column sep=large]
		\Dd_{\geq 0}(\IZ)\dar[shift right=0.45ex,"{[1]=\Sigma}"']\rar["K"]\drar[phantom,"\scriptscriptstyle/\!/\!/"] & \CGrp(\An)\dar[shift right=0.45ex,"B"']\\
		\Dd_{\geq 0}(\IZ)\uar[dotted,shift right=0.45ex,"{\Omega}"']\rar["K"] & \CGrp(\An)\uar[dotted,shift right=0.45ex,"\Omega"']
	\end{tikzcd}
\end{equation*}
in $\Cat_\infty$. In a nutshell, this says that \enquote{$B$ preserves Eilenberg--MacLane anima and only shifts the homotopy groups up by $1$}. To see commutativity, first note that the diagram with the dotted vertical arrows commutes (where $\Omega=(\tau_{\geq 1}-)[-1]\colon \Dd_{\geq 0}(\IZ)\morphism \Dd_{\geq 0}(\IZ)$ is defined as in Philosophical Nonsense~\cref{rem:PhilosophicalNonsenseII}). Indeed, $\Omega$ is given by a pullback which is preserved by the right-adjoint functor $K$ (being a right adjoint is still true for the lift $K\colon \Dd_{\geq 0}(\IZ)\morphism \CGrp(\An)$, simply by construction and our \cref{obs:AdjunctionOfFunctorCats} that adjunctions extend to functor categories). By abstract nonsense, commutativity of the dotted diagram induces a natural transformation $BK\Rightarrow K\Sigma$. Whether this is an equivalence can be checked on objects $C\in \Dd_{\geq 0}(\IZ)$. But whether $BKC\morphism K\Sigma C$ is an equivalence can be checked on homotopy groups of underlying anima, i.e.\ it suffices to check that $\pi_*((BKC)_1,e)\isomorphism \pi_*((K\Sigma C)_1,e)$ is an isomorphism. But for general $X\in \CGrp(\An)$ we have
\begin{equation*}
	\pi_i\big((BX)_1,e\big)\simeq \begin{cases*}
		\pi_{i-1}(X_1,e)& if $i>0$\\
		* & if $i=0$ 
	\end{cases*}
\end{equation*}
(indeed, its well-known that $\Omega$ shifts homotopy groups down, so $B$ has to shift them up since $\Omega B\simeq \id$ by \cref{cor:CommutativeHorizontalAdjoints}).

Now towards the proof of \cref{eq:EckmannHilton}. Let's denote by $\Cat_\infty^\times\subseteq \Cat_\infty$ the (non-full) sub-$\infty$-category spanned by $\infty$-categories with finite products and functors preserving these. Let furthermore $\Cat_\infty^\mathrm{add}\subseteq \Cat_\infty^{\mathrm{semi\mhyph add}}\subseteq \Cat_\infty^\times$ denote the full sub-$\infty$-categories spanned by the additive and semi-additive $\infty$-categories respectively.\addtocounter{dummy}{-3}
\begin{thm}\label{thm:CMonCGrpAdjunctions}
	If an $\infty$-category $\Cc$ has products, then $\CMon(\Cc)$ and $\CGrp(\Cc)$ are semi-additive and additive, respectively. Furthermore, the functors
	\begin{align*}
		\CMon\colon \Cat_\infty^\times&\morphism \Cat_\infty^\mathrm{semi\mhyph add}\\
		\CGrp\colon \Cat_\infty^\times &\morphism \Cat_\infty^\mathrm{add}
	\end{align*}
	are right-adjoint to the inclusions $ \Cat_\infty^{\mathrm{semi\mhyph add}}\subseteq \Cat_\infty^\times$ and $\Cat_\infty^\mathrm{add}\subseteq\Cat_\infty^\times$ respectively.
\end{thm}
Using \cref{thm:CMonCGrpAdjunctions} we get an easy proof of \cref{eq:EckmannHilton}. First note that the two maps
\begin{equation*}
	\begin{tikzcd}
		\CMon\big(\CMon(\Cc)\big)\rar[bend left,start anchor=north east, end anchor=north west, "\sim"', "\mathrm{forget}_*"]\rar[bend right,start anchor=south east, end anchor=south west, "\sim", "\mathrm{forget}"'] & \CMon(\Cc)
	\end{tikzcd}	
\end{equation*}
agree and are equivalences. Indeed, $\CMon(-)\morphism (-)$ is the counit of the adjunction from \cref{thm:CMonCGrpAdjunctions}, hence an equivalence since the left adjoint $\Cat_\infty^\mathrm{semi\mhyph add}\subseteq \Cat_\infty^\times$ is fully faithful. This shows that both functors are equivalences. Moreover, by writing down the triangle identities we find that both maps are inverses (once from the right, once from the left) to the unit $\CMon(\Cc)\morphism \CMon(\CMon(\Cc))$, hence they must agree. This almost shows \cref{eq:EckmannHilton}, except that we want to replace one $\CMon$ by a $\Mon$. To do this, note that \cref{prop:CMonOfSemiAdditive} implies $\CMon(\CMon(\Cc))\simeq \Mon(\CMon(\Cc))$. Moreover $\CMon(\Mon(\Cc))\simeq \Mon(\CMon(\Cc))$ follows by straightforward inspection, as both sides can be interpreted as full subcategories of $\Fun(\IDelta^\op\times \IGamma^\op,\Cc)$. Hence we are done.

Note that our argument can not be extended to show that the two forgetful functors $\Mon(\Mon(\Cc))\shortdoublemorphism\Mon(\Cc)$ agree. This is still true, but much harder to show. Moreover, if $\Cc$ is a $1$-category, then $\Mon(\Mon(\Cc))\simeq \CMon(\Cc)$, a fact that is usually called the \emph{Eckmann--Hilton trick}. This is false for $\infty$-categories! What is true instead is
\begin{equation*}
	\CMon(\Cc)\simeq \limit_{n\in \IN^\op}\Mon^{(n)}(\Cc)\,,
\end{equation*}
where $\Mon^{(n)}(-)=\Mon(\Mon(\dotso(\Mon(-))\dotso))$ is the $n$-fold iteration of $\Mon(-)$. The transition morphisms $\Mon^{(n)}(\Cc)\morphism \Mon^{(n-1)}(\Cc)$ are given by forgetting one $\Mon$. There are $n$ choices to do so, but it turns out that they all agree, generalizing our claim about $\Mon(\Mon(\Cc))\shortdoublemorphism\Mon(\Cc)$.



For the proof of \cref{thm:CMonCGrpAdjunctions}, we need a criterion for semi-additivity.
\begin{lem}[compare {\cite[Proposition~\HAthm{2.4.3.19}]{HA}}, which is stronger]\label{lem:SemiAddCriterion}
	Let $\Cc$ be a category with finite products. Then $\Cc$ is semi-additive if the following conditions hold:
	\begin{alphanumerate}
		\item The terminal object $*\in \Cc$ also is initial.
		\item We have a natural transformation $\mu\colon (\Delta\colon x\mapsto x\times x)\Rightarrow\id_\Cc$ such that both compositions
		\begin{align*}
			x&\simeq x\times *\xrightarrow{{\id_x}\times 0} x\times x\morphism[\mu_x]x\\
			 x&\simeq *\times x\xrightarrow{0\times{\id_x}} x\times x\morphism[\mu_x]x
		\end{align*}
		are homotopic to $\id_x$ for all $x\in \Cc$, and the diagram
		\begin{equation*}
			\begin{tikzcd}[column sep=small]
				(x\times x)\times (y\times y)\drar["\mu_x\times \mu_y"']\ar[rr,"\id_x\times\mathrm{flip}\times \id_y"] & & (x\times y)\times (x\times y)\dlar["\mu_{x\times y}"]\\
				& x\times y & 
			\end{tikzcd}
		\end{equation*}
		commutes up to homotopy for all $x,y\in \Cc$.
	\end{alphanumerate}
\end{lem}
\begin{rem*}
	Lurie only requires that the first of the two compositions in \cref{lem:SemiAddCriterion}\itememph{b} is homotopic to $\id_x$, and Fabian may or may not have done the same in the lecture. However, the second one doesn't follow from the first, and we'll really need both to be homotopic to $\id_x$ in the proof. In fact, if only the first composition were to be homotopic to $\id_x$, we could take $\mu_x$ to be $\pr_1\colon x\times x\morphism x$ for all $x\in \Cc$ (it's clear that this also makes the diagram above commute), and then we could show that every $\infty$-categories with finite products and a zero object is semi-additive. This can't be true!
\end{rem*}
\begin{proof}[Proof of \cref{lem:SemiAddCriterion}]
	Let $c,d\in \Cc$. We want to show that the maps
	\begin{equation*}
		c\simeq c\times *\xrightarrow{\id_c\times 0}c\times d\quad\text{and}\quad d\simeq *\times d\xrightarrow{0\times\id_d}c\times d
	\end{equation*}
	exhibit $c\times d$ as a coproduct of $c$ and $d$. That is, we need to show that the natural transformation
	\begin{equation*}
		\phi\colon \Hom_\Cc(c\times d,-)\overset{\sim}{\Longrightarrow}\Hom_\Cc(c,-)\times \Hom_\Cc(d,-)
	\end{equation*}
	induced by these maps is an equivalence. This can be checked on objects. Given $a\in \Cc$, we construct an inverse $\psi_a$ to $\phi_a$ as follows:
	\begin{equation*}
		\psi_a\colon \Hom_\Cc(c,a)\times \Hom_\Cc(d,a)\morphism[\times]\Hom_\Cc(c\times d,a\times a)\morphism[\mu_a]\Hom_\Cc(c\times d,a)
	\end{equation*}
	Note that we do not claim that the $\psi_a$ combine into a natural transformation $\psi$ which is inverse to $\phi$, only that $\psi_a$ is inverse to $\phi_a$, since it suffices to have $\phi$ a pointwise equivalence. Let's prove $\phi_a\circ \psi_a\simeq \id$ first. This follows essentially from the first condition in \itememph{b}, but since this sparked some confusion in the lecture, I'll try to give a much more detailed proof than in the lecture and be as precise as possible (hopefully this doesn't make things worse). We begin by drawing a tiny diagram:
	\begin{equation*}
		\begin{tikzcd}[column sep=1.765ex]
			& \Hom_\Cc(c,a)\times \Hom_\Cc(d,a)\dar[iso]\ar[ldd,bend right,start anchor=west,"\times"']\ar[rddd,bend left,start anchor=east,"\id","\sim"{swap,sloped}] &[-3ex] \\
			\phantom{X}\drar[phantom, start anchor=center, end anchor=center, "\mathrm{(I)}"]& \Hom_\Cc(c\times *,a\times *)\times \Hom_\Cc(*\times d,*\times a)\dar\drar[phantom, start anchor=center, end anchor=center, "\mathrm{(III)}"] &[-3ex] \\
			\Hom_\Cc(c\times d,a\times a)\dar["\mu_a"']\rar\drar[phantom, start anchor=center, end anchor=center,"\mathrm{(II)}"] & \Hom_\Cc(c\times *,a\times a)\times \Hom_\Cc(*\times d,a\times a)\dar["\mu_a\times \mu_a"] &[-3ex] \phantom{X} \\
			\Hom_\Cc(c\times d,a)\rar & \Hom_\Cc(c\times*,a)\times \Hom_\Cc(*\times d,a)\rar[iso] &[-3ex] \Hom_\Cc(c,a)\times \Hom_\Cc(d,a)
		\end{tikzcd}
	\end{equation*}
	If we can show that this diagram commutes up to homotopy, then walking around its perimeter will show $\phi_a\circ \psi_a\simeq \id$. The cell labelled (III) commutes up to homotopy because the composition of the three downward pointing arrows and the rightward pointing arrow is induced by $\mu_a\circ (\id_a\times 0)\colon a\simeq a\times *\morphism a\times a\morphism a$ in the first factor and by $\mu_a\circ (0\times\id_a)\colon a\simeq *\times a\morphism a\times a\morphism a$ in the second factor, both of which are homotopic to $\id_a$ by assumption.
	
	To see that the cell labelled (II) commutes up to homotopy, it suffices to check this after composition with $\pr_1\colon \Hom_\Cc(c\times *,a)\times \Hom_\Cc(*\times d,a)\morphism \Hom_\Cc(c\times *,a)$ and after composition with $\pr_2\colon \Hom_\Cc(c\times *,a)\times \Hom_\Cc(*\times d,a)\morphism \Hom_\Cc(*\times d,a)$. We only give the argument for $\pr_1$, since the argument for $\pr_2$ will be analogous. After composition with $\pr_1$, we end up with two maps $\Hom_\Cc(c\times d,a\times a)\morphism \Hom_\Cc(c\times *,a)$. Both are given by precomposition with $c\times *\morphism c\times d$ and postcomposition with $\mu_a\colon a\times a\morphism a$, but in different orders. However, it doesn't matter (up to homotopy) in which order we postcompose and precompose, which proves commutativity of (II).
	
	Finally, to see that (I) commutes, we look at the diagram (and its obvious analogue where $c\times *$ is replaced by $*\times d$)
	\begin{equation*}
		\begin{tikzcd}
			\Hom_\Cc(c,a)\times \Hom_\Cc(d,a)\dar\rar["\times"] & \Hom_\Cc(c\times d,a\times a)\dar\\
			\Hom_\Cc(c,a)\times \Hom_\Cc(*,a)\rar["\times"] & \Hom_\Cc(c\times *,a\times a)\\
			\Hom_\Cc(c,a)\times \Hom_\Cc(*,*)\uar[iso]\rar["\times"] & \Hom_\Cc(c\times *,a\times *)\uar
		\end{tikzcd}
	\end{equation*}
	This commutes \enquote{by naturality of the $\times$-construction on morphism anima}. The bottom left vertical arrow is an equivalence since $*$ is initial, so $\Hom_\Cc(*,-)\simeq *$. In particular, this shows $\Hom_\Cc(c,a)\times \Hom_\Cc(*,*)\simeq \Hom_\Cc(c,a)$. Under this identification, the bottom row becomes the morphism $\Hom_\Cc(c,a)\morphism \Hom_\Cc(c\times *,a\times *)$ from (I) and the two left vertical arrows compose to the projection $\pr_1\colon \Hom_\Cc(c,a)\times \Hom_\Cc(d,a)\morphism \Hom_\Cc(c,a)$. This shows that (I) commutes indeed and therefore that $\phi_a\circ \psi_a\simeq \id$.
	
	Now we prove $\psi_a\circ \phi_a\simeq \id$. First we check that $\psi_a\circ\phi_a$ is homotopic to the map induced by precomposition with
	\begin{equation*}
		c\times d\simeq (c\times *)\times (*\times d)\morphism (c\times d)\times (c\times d)\xrightarrow{\mu_{c\times d}} c\times d\,.
	\end{equation*}
	To show this, we draw another moderately large diagram:
	\begin{equation*}
		\begin{tikzcd}[column sep=0.5em]
			\Hom_\Cc(c,a)\times \Hom_\Cc(d,a)\dar\drar[phantom, start anchor=center, end anchor=center, "\mathrm{(IV)}"]&[-0.4em] \Hom_\Cc(c\times d,a)\dar["\Delta"]\lar\ar[ddr,bend left,start anchor=east, end anchor=north,"\mu_{c\times d}"]\ar[ddr,phantom, start anchor=center, end anchor=center, "\mathrm{(V)}",pos=0.25] & \\
			\Hom_\Cc(c\times d,a\times a)\dar["\mu_a"']\ar[drr,phantom, start anchor=center, end anchor=center, "\mathrm{(VI)}"] & \Hom_\Cc\big((c\times d)\times (c\times d),a\times a)\big)\lar[dotted]\drar[bend left=20, start anchor=east,"\mu_a"'] &  \\
			\Hom_\Cc(c\times d,a) & \Hom_\Cc\big((c\times *)\times (*\times d),a\big)\lar & \Hom_\Cc\big((c\times d)\times (c\times d),a\big)\lar
		\end{tikzcd}
	\end{equation*}
	The cell labelled (V) commutes up to homotopy because $\mu\colon \Delta\Rightarrow \id$ is a natural transformation (and I believe Fabian is right that we really need this here---if we were to use Lurie's weaker condition, it would only commute on $\pi_0$). If we choose the dotted arrow to be induced by $c\times d\simeq(c\times *)\times (*\times d)\morphism (c\times d)\times (c\times d)$, then also (VI) commutes up to homotopy because it doesn't matter in which order precomposition with said morphism and postcomposition with $\mu_a$ are applied. Finally, (IV) commutes by inspection. Walking around the perimeter of this diagram now proves that $\psi_a\circ \phi_a$ is really induced by precomposition with the map from above.
	
	Now we finally use the second condition from \itememph{b} to obtain a homotopy-commutative diagram
	\begin{equation*}
		\begin{tikzcd}
			c\times d\rar[iso]\drar[iso] & (c\times *)\times (*\times c)\eqar[d]\rar & (c\times d)\times (c\times d)\rar["\mu_{c\times d}"] & c\times d\\
			& (c\times *)\times (*\times d)\rar & (c\times c)\times (d\times d)\uar["\id_c\times\mathrm{flip}\times \id_c","\sim"{swap,sloped}]\urar["\mu_c\times \mu_d"']
		\end{tikzcd}
	\end{equation*}
	in $\Cc$. Using the first condition from \itememph{b} we see that the composition of the lower three arrows is homotopic to $\id_c\times \id_d$. Hence the morphism we precompose with is homotopic to the identity on $c\times d$, which shows $\psi_a\times \phi_a\simeq \id$, as required.
\end{proof}
\begin{proof}[Proof of \cref{thm:CMonCGrpAdjunctions}]
	We first prove that $\CMon(\Cc)$ is semi-additive. Of course we would like to apply \cref{lem:SemiAddCriterion}, so we must produce the corresponding data on $\CMon(\Cc)$. First of all, note that $\const_*\colon \IGamma^\op\morphism \Cc$ is both terminal and initial. It is even terminal in $\Fun(\IGamma^\op,\Cc)$ because $*\in \Cc$ is terminal and limits in functor categories are computed pointwise (\cref{lem:f^*preservesColimits}). To see that it is initial, let $X\in \CMon(\Cc)$ and compute
	\begin{equation*}
		\Nat(\const_*,X)\simeq \Hom_\Cc\left(*,\limit_{\langle n\rangle\in \IGamma^\op}X_n\right)\simeq \Hom_\Cc(*,X_0)\simeq \Hom_\Cc(*,*)\simeq *\,,
	\end{equation*}
	where we used that $\langle 0\rangle\in \IGamma^\op$ is a terminal object and thus spans a final subset.
	
	Next we need to construct functorial maps $\mu_M\colon M\times M\morphism M$ for all $M\in \CMon(\Cc)$. Consider the map $\times \colon \IGamma^\op\times \IGamma^\op\morphism \IGamma^\op$ given by crossing the sets and crossing the morphisms (note that this wouldn't work with $\IDelta^\op$). It induces a functor $\Fun(\IGamma^\op,\Cc)\morphism \Fun(\IGamma^\op,\Fun(\IGamma^\op,\Cc))$, and one easily checks that the Segal condition is preserved, i.e.\ we get a functor
	\begin{equation*}
		\operatorname{Double}\colon \CMon(\Cc)\morphism\CMon\big(\CMon(\Cc)\big)\,.
	\end{equation*}
	Unravelling definitions, we find that $\operatorname{Double}(-)_1\colon \CMon(\Cc)\morphism\CMon(\Cc)$ is naturally equivalent to the identity and $\operatorname{Double}(-)_2\colon \CMon(\Cc)\morphism\CMon(\Cc)$ is naturally equivalent to the diagonal $\Delta\colon M\mapsto M\times M$. Hence we can take $\mu_M\colon M\times M\morphism M$ to be the multiplication $m\colon \operatorname{Double}(M)_2\morphism \operatorname{Double}(M)_1$, i.e.\ the map induced by $m\colon \langle 2\rangle \morphism\langle 1\rangle$ in $\IGamma^\op$ (see \cref{def:CartesianCommutativeMonoids}). Since the $\mu_M$ are induced by a map in $\IGamma^\op$, it's clear that they assemble into a natural transformation $\mu$. Also the required conditions for $\mu$ are straightforward to check.
	
	This shows that $\CMon(\Cc)$ is semi-additive by \cref{lem:SemiAddCriterion}. Hence the same holds for its full subcategory $\CGrp(\Cc)\subseteq \CMon(\Cc)$ since this is closed under finite products. To show that $\CGrp(\Cc)$ is additive, we need to check that the shear map is an equivalence for all objects $G\in \CGrp(\Cc)$. But in view of the fact that the codiagonal $G\times G\morphism G$ is induced by $\mu_G$ (this follows by unravelling the explicit inverse in the proof of \cref{lem:SemiAddCriterion}), hence by multiplication on $\operatorname{Double}(G)$, this gets translated into the fact that $\operatorname{Double}(G)$ is a cartesian commutative group itself, which is again easy to check.
	
	Finally, we need to show that $\CMon\colon \Cat_\infty^\times\morphism \Cat_\infty^\mathrm{semi\mhyph add}$ and $\CGrp\colon \Cat_\infty^\times \morphism \Cat_\infty^\mathrm{add}$ are right adjoints. If we denote $R=\CMon$ and $\eta\colon R\Rightarrow \id$ the forgetful natural transformation (given by evaluation in degree $1$), then \cref{prop:CMonOfSemiAdditive} and the fact that $\CMon(\Cc)$ is semi-additive show that $\eta R\colon R\circ R\overset{\sim}{\Longrightarrow} R$ and $R\eta\colon R\circ R\overset{\sim}{\Longrightarrow} R$ are natural equivalences. Thus we may apply the dual of Proposition~\labelcref{prop:LLaddendum} to see that $R$ is a right adjoint to the inclusion $\im(R)\subseteq \Cat_\infty^\times$ of its essential image. But $\im(R)=\Cat_\infty^\mathrm{semi\mhyph add}$: Indeed, \enquote{$\subseteq$} was checked above, whereas \enquote{$\supseteq$} follows from \cref{prop:CMonOfSemiAdditive} again. The argument for $\CGrp$ is completely analogous.
\end{proof}
\numpar*{A Few Comments/Examples}\lecture[Spectra! The recognition principle for infinite loop spaces. Stable $\infty$-categories.\newline --- \enquote{\emph{Peter May hates this proof. I love it.}}]{2020-12-10}\label{par:FreeCMon}
The forgetful functor $\CMon(\An)\morphism\An$ as a left adjoint $\Free^\CMon\colon \An\morphism \CMon(\An)$. On objects $X\in\An$ it is given by
\begin{equation*}
	\Free^\CMon(X)_1\simeq \coprod_{n\geq 0}X_{h\SS_n}^n\,,
\end{equation*}
i.e.\ we take free words in $X$, but we need to homotopy-quotient out the action of the symmetric group $\SS_n$, which the notation $(-)_{h\SS_n}$ is supposed to do. In general, given a functor $F\colon BG\morphism\Cc$, where $\Cc$ is an $\infty$-category with colimits and $G$ is a discrete group, we put
\begin{equation*}
	F_{hG}\simeq \colimit_{BG}F\,.
\end{equation*}
On $X^n$, the $\SS_n$-action is given by \enquote{permuting factors}, so the corresponding map $B\SS_n\morphism\An$ sends the unique $0$-simplex to $X^n$, the edges to the corresponding automorphisms of $X^n$ and so on. As an example,
\begin{equation*}
	\Free^\CMon(*)_1\simeq \coprod_{n\geq 0}B\SS_n\simeq \big(\{\text{finite sets, bijections}\},\sqcup\big),
\end{equation*}
where the right-hand side is the symmetric monoidal $1$-groupoid of finite sets and bjections between them, whose tensor product is given by disjoint union.


Also, if $G$ is a topological group, then $BG$ agrees with the classifying space for principal $G$-bundles.

\section{Spectra and Stable \texorpdfstring{$\infty$}{infinity}-Categories}
Let $\CGrp(\An)_{\geq i}\subseteq \CGrp(\An)$ be the full sub-$\infty$-category spanned by those $X$ with $\pi_jX_1=0$ for $j<i$. We have seen in \cref{cor:CommutativeHorizontalAdjoints} that $B\colon \CGrp(\An)\morphism\CMon(\An)$ is fully faithful with right adjoint $\Omega$. Moreover, after its proof we checked that $B$ actually has essential image in $\CGrp(\An)_{\geq 1}$. In fact, its essential image \emph{is} $\CGrp(\An)_{\geq 1}$! To see this, it suffices to check that the counit $c\colon B\Omega X\isomorphism X$ is an equivalence for all $X\in \CGrp(\An)_{\geq 1}$. This can be checked on underlying anima, i.e.\ after $\ev_1$, and then again on homotopy groups. Since $\Omega$ shifts homotopy groups down and $B$ shifts them up, we get that $c_*\colon \pi_i(B\Omega X)_1\isomorphism \pi_i X_1$ is an isomorphism for $i>0$. For $i=0$ it is one as well as both sides are connected.

Iterating this argument, we find that the $i$-fold application $B^{(i)}=B\circ\dotsb\circ B$ is an equivalence
\begin{equation*}
	B^{(i)}\colon \CGrp(\An)\isomorphism\CGrp(\An)_{\geq i}\,.
\end{equation*}
Moreover, since $\Omega B\simeq \id$ by \cref{cor:CommutativeHorizontalAdjoints}, we get $\Omega B^{(i+1)}\simeq B^{(i)}$. This yields a fully faithful functor
\begin{equation*}
	B^\infty\colon \CGrp(\An)\morphism \limit_{\IN^\op}\left(\dotso\morphism[\Omega]\CGrp(\An)\morphism[\Omega]\CGrp(\An)\right)
\end{equation*}
(the limit being taken in $\Cat_\infty$ of course) with essential image
\begin{equation*}
	\limit_{\IN^\op}\left(\dotso\morphism[\Omega]\CGrp(\An)_{\geq 2}\morphism[\Omega]\CGrp(\An)_{\geq 1}\right)\,.
\end{equation*}\stepcounter{dummy}
\begin{defi}\label{def:spectra}
	We say that an $\infty$-category $\Cc$ has \emph{finite limits} if it has finite products and pullbacks (one can check that this is equivalent to having limits over all finite simplicial sets). If this is the case, then a suspension functor $\Omega\colon {*/\Cc}\morphism */\Cc$ can be defined and we put
	\begin{equation*}
		\Sp(\Cc)\coloneqq \limit_{\IN^\op}\left(\dotso\morphism[\Omega]*/\Cc\morphism[\Omega]*/\Cc\right)\,
	\end{equation*}
	called the $\infty$-category of \emph{spectrum objects} in $\Cc$. If $\Cc=\An$, we obtain $\Sp=\Sp(\An)$, the $\infty$-category of \emph{spectra}.
\end{defi}
\begin{prop}\label{prop:SpCGrpIsSpAgain}
	Suppose $\Cc$ has finite limits. Then the forgetful functor
	\begin{equation*}
		\Sp\big(\CGrp(\Cc)\big)\isomorphism\Sp(\Cc)
	\end{equation*}
	is an equivalence.
\end{prop}
\begin{proof}[Proof sketch]
	Topologists hate this proof. First observe that $\Sp(\CGrp(\Cc))\simeq \CGrp(\Sp(\Cc))$. This is because
	\begin{equation*}
		\limit_{\IN^\op}\left(\dotso\morphism[\Omega]\Fun(\IGamma^\op,*/\Cc)\morphism[\Omega]\Fun(\IGamma^\op,*/\Cc)\right)\simeq \Fun\left(\IGamma^\op,\limit_{\IN^\op}\left(\dotso\morphism[\Omega]*/\Cc\morphism[\Omega]*/\Cc\right)\right)
	\end{equation*}
	(here we use that $\Fun(\Dd,-)\colon \Cat_\infty\morphism\Cat_\infty$ commutes with limits since it is right-adjoint to $\Dd\times -$ and also that $\Omega$ in functor categories can be computed pointwise by \cref{lem:f^*preservesColimits}) and one checks that the Segal condition and the group condition are preserved.
	
	Therefore, we will be done by \cref{prop:CMonOfSemiAdditive} once we show that $\Sp(\Cc)$ is an additive category. Of course we will employ \cref{lem:SemiAddCriterion} again. Clearly $(*,*,\dotsc)\in \Sp(\Cc)$ is both initial and terminal. Also $\Sp(\Cc)$ again has finite limits, inherited from $*/\Cc$ because limits in limits can be computed degree-wise (combine the fact that $\Hom$ anima in limits are limits of $\Hom$ anima with \cref{cor:HomPreservesColimits} and \cref{prop:ColimitsCommute}). Moreover, we know that $\Omega\colon \Sp(\Cc)\isomorphism \Sp(\Cc)$ is an equivalence by construction and factors as
	\begin{equation*}
		\Omega\colon \Sp(\Cc)\morphism \Grp\big(\Sp(\Cc)\big)\morphism[\ev_1]\Sp(\Cc)
	\end{equation*}
	(I didn't find this quite obvious, so I decided to sketch a proof in \cref{rem*:OmegaFactorsOverGrp} below). Finally, to apply \cref{lem:SemiAddCriterion}, we must produce functorial morphisms $\mu_X\colon X\times X\morphism X$ with the properties stated there. For this, we use $X\simeq \Omega(\Omega^{-1}X)_1$ and take $\mu_X$ to be induced by the multiplication on $\Omega(\Omega^{-1}X)\in \Grp(\Sp(\Cc))$.
	
	Up to checking the various conditions, this shows that $\Sp(\Cc)$ is semi-additive. For additivity we must check that the shear map is an equivalence on every $X\in \Sp(\Cc)$. Similar to the proof of \cref{thm:CMonCGrpAdjunctions} this follows from the fact that $\Omega(\Omega^{-1}X)$ is a cartesian group rather than just a monoid.
\end{proof}
\begin{rem*}\label{rem*:OmegaFactorsOverGrp}
	For any $\infty$-category $\Dd$ with finite limits and a zero object $*\in \Dd$ (i.e.\ an object that is both initial and terminal) the functor $\Omega\colon \Dd\morphism\Dd$ factors as
	\begin{equation*}
		\Omega\colon \Dd\morphism\Grp(\Dd)\morphism[\ev_1]\Dd
	\end{equation*}
	This can be bootstrapped from the case $\Dd=*/\An$ which we already know from \cref{par:Grp(An)=(*/An)Connected}. The first step is to enhance the Yoneda embedding to a fully faithful functor $\Dd\morphism \Fun(\Dd^\op,*/\An)$. To this end we consider $\Fun(\Dd^\op,\An)\morphism\Fun(\Ar(\Dd^\op),\Ar(\An))\morphism\Fun(*/\Dd^\op,\Ar(\An))$ and check that its image lands in the \enquote{correct fibre}, i.e.\ in $\Fun(*/\Dd^\op,*/\An)$ if we restrict the source to finite limits-preserving functors (where the Yoneda embedding lands).
	
	On $\Fun(\Dd^\op,*/\An)$ we have loop functor $\Omega\colon \Fun(\Dd^\op,*/\An)\morphism \Fun(\Dd^\op,*/\An)$ as well, and it is simply given by postcomposition with $\Omega\colon {*/\An}\morphism*/\An$. Hence it factors as 
	\begin{equation*}
		\begin{tikzcd}
			& \Fun\big(\Dd^\op,\Grp(*/\An)\big)\dar["\ev_1"]\rar[iso] & \Grp\big(\Fun(\Dd^\op,*/\An)\big)\\
			\Fun(\Dd^\op,*/\An)\rar["\Omega"]\urar[dashed,"\Omega"]&\Fun(\Dd^\op,*/\An)
		\end{tikzcd}
	\end{equation*}
	Since the Yoneda embedding preserves limits, we get a lift $\Omega\colon \Dd\morphism \Grp(\Fun(\Dd^\op,*/\An))$ and one checks that it lands in the full sub-$\infty$-category $\Grp(\Dd)$, as required.
\end{rem*}
\numpar*{Homotopy Groups of Spectra}
Because  $\IN^\op\subseteq \IZ^\op$ is final in the sense of \cref{def:cofinal}, we can also write $\smash{\Sp(\Cc)\simeq\limit_{\IZ^\op}(\ActsOn{*/\Cc}{\Omega})}$. This gives evaluation functors
\begin{equation*}
	\Omega^{\infty-i}\colon \Sp(\Cc)\morphism\Cc\,.
\end{equation*}
for all $i\in \IZ$. Note $\Omega\Omega^{\infty-i}X\simeq \Omega^{\infty-(i-1)}X\simeq\Omega^{\infty-i}\Omega X$, so this somewhat weird notation actually makes sense. For $X\in \Sp$ we can now define homotopy groups as
\begin{equation*}
	\pi_iX=\pi_0\Omega^{\infty-i}X\,.
\end{equation*}
If we think of a spectrum $X$ as a sequence $X=(X_0,X_1,X_2,\dotsc)$, where $X_i=\Omega^{\infty-i}X$, together with equivalences $X_i\simeq \Omega X_{i+1}$, then we see that $\pi_iX\simeq \pi_0X_i\simeq \pi_jX_{i+j}$ for all $j\geq 0$ because $\Omega\colon {*/\An}\morphism */\An$ shifts homotopy groups down.

\numpar*{Summary of What We Know So Far}
Let's explicitly record the following facts we already learned in the proof of \cref{prop:SpCGrpIsSpAgain} and afterwards:
\begin{alphanumerate}
	\item $\Sp(\Cc)$ has finite limits (because $*/\Cc$ has) and limits in $\Sp(\Cc)$ are computed degree-wise, i.e.\ $\Omega^{\infty-i}\colon \Sp(\Cc)\morphism\Cc$ preserves limits. %The only reason this doesn't work for colimits as well is that the degree-wise colimits might not be compatible with the $\Omega$-maps any more, so they don't necessarily define an element of $\Sp(\Cc)$.
	\item $\Omega\colon \Sp(\Cc)\isomorphism\Sp(\Cc)$ is an equivalence.
	\item $\Sp(\Cc)$ is additive.
\end{alphanumerate}
\begin{cor}[Recognition principle for infinite loop spaces, Boardman--Vogt, May, Segal]\label{cor:RecognitionForInfiniteLoopSpaces}
	The functor
	\begin{equation*}
		B^\infty\colon\CGrp(\An)\morphism\Sp
	\end{equation*}
	is fully faithful with essential image those $X\in \Sp$ with $\pi_iX=0$ for $i<0$ \embrace{as a slogan, $\IE_\infty$-groups are spectra with no negative homotopy groups}. Also $\pi_i(B^\infty X)=\pi_i(X_1,*)$ for all $i\geq 0$.
\end{cor}
\begin{proof*}
	The target of $B^\infty$ is $\Sp(\CGrp(\An))\simeq \Sp$ by \cref{prop:SpCGrpIsSpAgain}. We have seen that $B^\infty$ is fully faithful and identified its image before \cref{def:spectra}, and it's easy to see that the two descriptions of the essential image of $B^\infty$ are the same (for this we need the convention $0\notin\IN^\op$, otherwise everything gets shifted by one).
\end{proof*}
\begin{exm}\label{exm:MyFirstSpectra}
	Let $\Cc$ always have finite limits. Here are \enquote{my first spectra}:
	\begin{alphanumerate}
		\item If $\Omega\colon {*/\Cc}\isomorphism */\Cc$ is an equivalence, then $\Sp(\Cc)\simeq \Cc$ (because $|\IN^\op|\simeq *$). For example, $\Sp(\Dd(\IZ))\simeq \Dd(\IZ)$ or, even more silly, $\Sp(\Sp)\simeq \Sp$.
		\item Let's compute $\Sp(\Dd_{\geq 0}(R))$ for a ring $R$. Recall that the loop functor on $\Dd_{\geq 0}(\IZ)$ is defined as $\Omega C\simeq \tau_{\geq 0}(C[-1])\in \Dd_{\geq 0}(R)$. Then the functor
		\begin{align*}
			\Dd(R)&\isomorphism \Sp\big(\Dd_{\geq 0}(R)\big)\\
			C&\longmapsto \big(\tau_{\geq 0}C,(\tau_{\geq -1}C)[1],(\tau_{\geq -2}C)[2],\dotsc\big)
		\end{align*}
		is an equivalence. The inverse functor sends a sequence $(C_0,C_1,\dotsc)$ with equivalences $\sigma_i\colon C_i\simeq (\tau_{\geq 1}C_{i+1})[-1]$ to $\colimit_\IN C_i[-i]$. The structure maps $C_i[-i]\morphism C_{i+1}[-(i+1)]$ in this colimit are constructed from the $\sigma_i$ in the obvious way.
		\item Consider the Eilenberg--MacLane functor $K\colon \Dd_{\geq 0}(\IZ)\morphism \An$. Being a right adjoint, it preserves finite limits, and in particular loop spaces. Hence it upgrades to a functor
		\begin{equation*}
			\begin{tikzcd}
				\Sp\big(\Dd_{\geq 0}(\IZ)\big)\eqar[d]\rar["\Sp(K)"]& \Sp(\An)\eqar[d]\\
				\Dd(\IZ)\rar["H"] & \Sp
			\end{tikzcd}
		\end{equation*}
		the \emph{Eilenberg--MacLane spectrum functor}. By construction, the diagram
		\begin{equation*}
			\begin{tikzcd}[column sep=small]
				\Dd(\IZ)\drar["{K(\tau_{\geq -i}-)[i]}"']\ar[rr,"H"] & & \Sp\dlar["\Omega^{\infty-i}"]\\
				& \CGrp(\An)
			\end{tikzcd}
		\end{equation*}
		commutes. If $C\in \Dd_{\geq 0}(\IZ)$, then $HC=(K(C),K(C[1]),K(C[2]),\dotsc)$ and we have $\pi_i HC=H_iC$. If $C$ is an abelian group $A$ concentrated in degree $0$, we obtain the \emph{Eilenberg--MacLane spectrum} $HA=(K(A,0),K(A,1),K(A,2),\dotsc)$.
		\item We have $\Sp(\An^\op)\simeq *$, because it is a sequential limit over $(\emptyset/\An^\op)\simeq (\An/\emptyset)^\op\simeq *$ (since there is no map $X\morphism\emptyset$ in $\An$ except $\id_\emptyset\colon \emptyset\morphism \emptyset$). Also
		\begin{align*}
			\Sp\big((*/\An)^\op\big)&\simeq \limit_{\IN^\op}\left(\dotso\morphism[\Omega](*/\An)^\op\morphism[\Omega](*/\An)^\op\right)\\
			&\simeq \limit_{\IN^\op}\left(\dotso\morphism[\Sigma]*/\An\morphism[\Sigma]*/\An\right)^\op\simeq *\,,
		\end{align*}
		since only contractible spaces can be an infinite suspension (as all homotopy groups must be vanish).
	\end{alphanumerate}
\end{exm}
\numpar{Homology of Spectra}\label{par:HomologyOfSpectra}
The Eilenberg--MacLane spectrum functor $H$, the adjunction $\snake{C}_\bullet\colon {*/\An}\shortdoublelrmorphism \Dd_{\geq0}(\IZ)\noloc K$ from Very Long Example~\cref{exm:EilenberMacLane} can be upgraded to another adjunction
\begin{equation*}
	C_\bullet\colon \Sp\doublelrmorphism \Dd(\IZ)\noloc H\,.
\end{equation*}
The new $C_\bullet$ is defined by the formula $C_\bullet(X)\simeq \colimit_{i\in \IN}\snake{C}_\bullet(\Omega^{\infty-i}X)[-i]$ on objects. To see where the transition maps in this colimit come from, recall that $\Omega=[-1]$ is the loop functor in $\Dd(\IZ)$. Together with $\snake{C}(*)\simeq 0$, this provides a natural transformation $\snake{C}_\bullet(\mathop{\Omega}-)\Rightarrow \snake{C}_\bullet(-)[-1]$, which provide the required transition maps.

To check that $C_\bullet$ is a left adjoint, it suffices to do so on objects by \cref{cor:AdjointsPointwise} (in particular, this will show that $C_\bullet$ is a functor at all), where we can compute
\begin{align*}
	\Hom_{\Dd(\IZ)}\big(C_\bullet(X),D\big)&\simeq \limit_{i\in \IN^\op}\Hom_{\Dd(\IZ)}\big(\snake{C}_\bullet(\Omega^{\infty-i}X),D[i]\big)\\
	&\simeq \limit_{i\in \IN^\op}\Hom_{*/\An}\big(\Omega^{\infty-i}X,K(D[i])\big)\\
	&\simeq \limit_{i\in \IN^\op}\Hom_{*/\An}(\Omega^{\infty-i}X,\Omega^{\infty-i}HD)\\
	&\simeq \Hom_\Sp(X,HD)\,,
\end{align*}
where we used that $\Hom$ anima in $\Sp$ (in fact, in arbitrary limits of $\infty$-categories) can be computed as a limit over the $\Hom$ anima in each degree. Also all equivalences are clearly functorial in $D\in \Dd(\IZ)$.

Now define the \emph{homology of $X$ with coefficients in $A\in \Ab$} to be
\begin{equation*}
	H_*(X,A)\coloneqq H_*\big(C_\bullet X\otimes_\IZ^LA\big)=\colimit_{i\in \IN}H_*(\Omega^{\infty-i}X,A)\,.
\end{equation*}
Note however that neither $H_*(HC,A)$ nor $H_*(B^\infty X,A)$ are easy to compute! We will eventually find out that $H_*(HC,\IZ)=\Tor_*^\IS(C,C)$ is given by \enquote{$\Tor$ over the sphere spectrum}.

\begin{propdef}\label{propdef:StableInftyCategory}
	If $\Cc$ is an $\infty$-category with a zero object \embrace{i.e.\ a simultaneously initial and terminal object $0\in \Cc$}, then the following are equivalent:
	\begin{alphanumerate}
		\item $\Cc$ has finite limits and $\Omega\colon \Cc\isomorphism\Cc$ is an equivalence.
		\item $\Cc$ has finite colimits and $\Sigma\colon \Cc\isomorphism \Cc$ is an equivalence.
		\item $\Cc$ has finite limits and finite colimits and a square
		\begin{equation*}
			\begin{tikzcd}
				a \rar\dar& b\dar\\
				c\rar & d
			\end{tikzcd}
		\end{equation*}
		is a pushout in $\Cc$ iff it is a pullback.
	\end{alphanumerate}
	Such $\infty$-categories are called \emph{stable $\infty$-categories}.
\end{propdef}
\begin{proof}
	The implications \itememph{c} $\Rightarrow $ \itememph{a}, \itememph{b} are clear: Applying the pushout-pullback condition to the pushout square defining $\Sigma$ and the pullback square defining $\Omega$ shows that the unit $\id\overset{\sim}{\Longrightarrow}\Omega\Sigma$ and the counit $\Sigma\Omega\overset{\sim}{\Longrightarrow}\id$ are natural equivalences, so $\Sigma$ and $\Omega$ must be equivalences of $\infty$-categories.
	
	 For \itememph{a} $\Rightarrow$ \itememph{c}, the same argument as in the proof of \cref{prop:SpCGrpIsSpAgain} shows that $\Cc$ is additive  (write $X$ as $\Omega Y$ in $\Grp(\Cc)$ and apply \cref{lem:SemiAddCriterion}). So we only need to check that pushouts exist and coincide with pullbacks. Let $P\subseteq \Fun(\Delta^1\times\Delta^1,\Cc)$ be the full subcategory spanned by pullback squares. We claim:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}] \itshape The restriction $P\isomorphism \Fun(\Lambda_0^2,\Cc)$ is an equivalence.
	\end{alphanumerate}
	To prove \itememph{\boxtimes}, we construct an inverse functor. Given a diagram $F\colon \Lambda_0\morphism \Cc$, which we can view as a span $c\lmorphism a\morphism b$ in $\Cc$, we construct the following moderately large diagram:
	\begin{equation*}
		\begin{tikzcd}
			\Omega a\rar\dar\drar[pullback] & \Omega c\rar\dar\drar[pullback] & 0\dar & \\
			\Omega b\rar\dar\drar[pullback] & x \rar\dar\drar[pullback] & g \rar\dar\drar[pullback] & 0\dar\\
			0\rar & f\rar\dar\drar[pullback] & a\dar\rar & b\\
			& 0\rar & c & 
		\end{tikzcd}
	\end{equation*}
	All squares are pullbacks as indicated. The fact that $\Omega a$, $\Omega b$, and $\Omega c$ appear in the top left corner follows by combining suitable pullback squares into larger pullback rectangles. The inverse functor now sends 
	\begin{equation*}
		F=\left(\begin{tikzcd}
			a\dar\rar & b\\
			c
		\end{tikzcd}\right)\longmapsto
		\Omega^{-1}\left(\begin{tikzcd}
			\Omega a\dar\rar\drar[pullback] & \Omega b\dar\\
			\Omega c\rar & x
		\end{tikzcd}\right)
	\end{equation*}
	(technically we have only defined the inverse on objects, but its clear how to make it functorial since limits are functorial).
	
	To construct pushouts using \itememph{\boxtimes}, let $F\colon \Lambda_0^2\morphism\Cc$ be a span $c\lmorphism a\morphism b$ as above. We know that it can be uniquely (up to contractible choice) extended to a pullback square, where the bottom right corner is some object $d\in \Cc$. The same goes for the trivial span consisting of identities $x=x=x$ for some $x\in \Cc$, and in this case the object we have to add is $x$ again of course. Hence
	\begin{equation*}
		\Nat\left(\begin{tikzcd}
			a\dar\rar & b\\
			c
		\end{tikzcd},\begin{tikzcd}
		x\eqar[r]\eqar[d] & x\\
		x
	\end{tikzcd}\right)\simeq \Nat\left(\begin{tikzcd}
	 a\dar\rar\drar[pullback] &  b\dar\\
	 c\rar & d
	\end{tikzcd},\begin{tikzcd}
	x\eqar[r]\eqar[d]\drar[pullback] & x\eqar[d]\\
	x\eqar[r] & x
	\end{tikzcd}\right)\simeq \Hom_\Cc(d,x)
	\end{equation*}
	because $\Delta^1\times \Delta^1$ has terminal vertex $(1,1)$. This computation shows that $d$ is a pushout of the given span. Moreover, we get the property that pushouts agree with pullbacks for free. This finishes the proof of \itememph{a} $\Rightarrow$ \itememph{c}. For \itememph{b} $\Rightarrow$ \itememph{c} just dualize everything.
\end{proof}
An immediate consequence of \cref{propdef:StableInftyCategory} is that $\Sp(\Cc)$ is stable for all $\infty$-categories $\Cc$ with finite limits. In particular, it holds for $\Sp$ and $\Dd(R)$ for any ring $R$ by \cref{exm:MyFirstSpectra}\itememph{b} (but it's also true for $\Kk(R)$). Moreover, $\Fun(\Ii,\Cc)$ is stable whenever $\Cc$ is.
%\addtocounter{dummy}{1}
\begin{cor}
	\upshape\lecture[Spectra and prespectra, spectrification. $\Sigma^\infty$ and the Baratt--Priddy-Quillen theorem. Another model for spectra. Towards a symmetric monoidal structure on $\Sp$.]{2020-12-15}\itshape
	For a functor $F\colon \Cc\morphism\Dd$ between stable $\infty$-categories the following are equivalent:
	\begin{alphanumerate}
		\item $F$ preserves finite limits.
		\item $F$ preserves finite colimits.
	\end{alphanumerate}
\end{cor}
\begin{proof}
	Since $\Cc$ and $\Dd$ are additive, $F$ preserves finite coproducts iff it preserves finite products. Since also pushout squares and pullback squares coincide, $F$ preserves the former iff it preserves the latter. This suffices to get all finite colimits and limits.
\end{proof}
\begin{defi}
	\begin{alphanumerate}
		\item Let $F\colon \Cc\morphism\Dd$ be a functor between $\infty$-categories with finite limits. We call $F$ \emph{left exact} if it preserves finite limits.
		\item We denote by $\Cat_\infty^\mathrm{lex}\subseteq \Cat_\infty$ the (non-full) sub-$\infty$-category  spanned by these. Dually, $\Cat_\infty^\mathrm{rex}\subseteq \Cat_\infty$ is the full sub-$\infty$-category spanned by \emph{right-exact} functors, i.e.\ finit colimit-preserving functors between $\infty$-categories with finite colimits.
		\item Finally, we denote by $\Cat_\infty^\mathrm{st}$ the full subcategory of both $\Cat_\infty^\mathrm{lex}$ and $\Cat_\infty^\mathrm{rex}$ spanned by the stable $\infty$-categories.
	\end{alphanumerate}
\end{defi}
For example, the functor $\Omega^\infty\colon \Sp(\Cc)\morphism \Cc$ is left exact for every $\Cc$ with finite limits. Also note that $\Omega^\infty$ factors canonically over $\CGrp(\Cc)$. This needs doesn't need an argument as in \cref{rem*:OmegaFactorsOverGrp}, simply recall that $\Sp(\Cc)\simeq \Sp(\CGrp(\Cc))$ by \cref{prop:SpCGrpIsSpAgain}.
\begin{rem*}
	Before we move on, I would like to point out a subtlety that's perhaps easy to overlook: In \cref{thm:SpLeftAdjoint} below, we'll investigate the functor $\Sp(-)\colon \Cat_\infty^\mathrm{lex}\morphism\Cat_\infty^\mathrm{st}$. But why is it a functor though? My own knee-jerk reaction was \enquote{well, limits are functorial}, but that's not the problem. The problem is that $\Omega\colon {*/\Cc}\morphism */\Cc$ is also supposed to be functorial in $\Cc$! Essentially this leads to the following question:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}] \itshape Let $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}\subseteq \Cat_\infty$ be the \embrace{non-full} subcategory spanned by $\infty$-categories with $\Ii$-shaped limits and functors preserving these. Why do the maps $\limit_\Ii\colon \Fun(\Ii,\Cc)\morphism \Cc$ for $\Cc\in \Cat_\infty^{\Ii\mhyph\mathrm{ex}}$ assemble into a natural transformation
		\begin{equation*}
			\limit_\Ii\colon \Fun(\Ii,-)\Longrightarrow (-)
		\end{equation*}
		of functors $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}\morphism \Cat_\infty$?
	\end{alphanumerate}
	There are a few more steps involved to show that $\Omega$ is natural too, namely one has to produce natural transformations $(-)\Rightarrow */(-)\Rightarrow \Fun(\Lambda_2^2,*/(-))$, but I'll leave that to you.
	
	To show \itememph{\boxtimes}, let's first produce the \enquote{adjoint} transformation $\const\colon (-)\Rightarrow \Fun(\Ii,-)$. Since the adjunction $-\times\Ii\colon \Cat_\infty\shortdoublelrmorphism \Cat_\infty\noloc \Fun(\Ii,-)$ extends to $\Fun(\Cat_\infty^{\Ii\mhyph\mathrm{ex}},\Cat_\infty)$ by \cref{obs:AdjunctionOfFunctorCats}, we may equivalently give a transformation $-\times \Ii\Rightarrow (-)$. Here the projection to the first factor is an obvious candidate and it is indeed the correct one.
	
	We may view the natural transformation $\const$ as a functor $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}\morphism\Ar (\Cat_\infty)$. Its image lies in the full subcategory spanned by those $\Delta^1\morphism\Cat_\infty$ that represent left-adjoint functors (because $\limit_\Ii$ is a pointwise right adjoint). But in fact, more is true (and that's the crucial point). Consider objects $(L\colon \Cc\morphism\Dd)$ and $(L'\colon \Cc'\morphism\Dd')$ in $\Ar(\Cat_\infty)$ as well as a morphism between them, which we view as a solid diagram
	\begin{equation*}
		\begin{tikzcd}
			\Cc\dar["L"']\rar& \Cc'\dar["L'"']\\
			\Dd\uar[dotted, bend right, "R"{swap,anchor=west}]\rar  & \Dd'\uar[dotted, bend right,"R'"{swap, anchor=west}]
		\end{tikzcd}
	\end{equation*}
	If $L$ and $L'$ are left adjoints, then the dotted arrows exist, but the resulting new square only commutes up to a natural transformation, not up to natural equivalence in general. We let $\Ar^L(\Cat_\infty)$ be the non-full sub-$\infty$-category spanned by those squares for which the adjoint square does in fact commute. Then $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}\morphism\Ar (\Cat_\infty)$ already factors over $\Ar^L(\Cat_\infty)$ since morphisms in $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}$ preserve $\Ii$-shaped limits.
	
	Now note that under the equivalence $\Un^\cocart\colon\Ar(\Cat_\infty)\isomorphism \Cocart(\Delta^1)$, the non-full sub-$\infty$-category $\Ar^L(\Cat_\infty)$ corresponds to $\cat{Bicart}(\Delta^1)$, the $\infty$-category of bicartesian fibrations over $\Delta^1$ with morphisms that preserve both cocartesian and cartesian edges (we know from \cite[Proposition~XI.10]{HigherCatsII} that bicartesian fibrations correspond to adjunctions, and the additional condition unravels to the condition that cartesian edges are preserved as well). Now we can apply the cartesian straightening $\St^\cart\colon \cat{Bicart}(\Delta^1)\morphism \Fun((\Delta^1)^\op,\Cat_\infty)$ to get a functor $\Cat_\infty^{\Ii\mhyph\mathrm{ex}}\morphism \Fun((\Delta^1)^\op,\Cat_\infty)$. After currying, this gives a map $(\Delta^1)^\op\morphism \Fun(\Cat_\infty^{\Ii\mhyph\mathrm{ex}},\Cat_\infty)$ which finally provides the desired transformation.
\end{rem*}
\begin{thm}\label{thm:SpLeftAdjoint}
	The functor $\Sp(-)\colon \Cat_\infty^\mathrm{lex}\morphism\Cat_\infty^\mathrm{st}$ is right-adjoint to the inclusion $\Cat_\infty^\mathrm{st}\subseteq \Cat_\infty^\mathrm{lex}$, the counit being given by $\Omega^\infty\colon \Sp(\Cc)\morphism \Cc$. In particular, if $\Cc$ is a stable $\infty$-category, we get a canonical lift
	\begin{equation*}
		\begin{tikzcd}
			& \Sp\dar["\Omega^\infty"]\\
			\Cc^\op\times \Cc \rar["\Hom_\Cc"']\urar[dashed,"\hom_\Cc"] & \An
		\end{tikzcd}
	\end{equation*}
	of the $\Hom_\Cc$ functor.
\end{thm}
Fabian remarks that $\Cat_\infty^\mathrm{st}\subseteq \Cat_\infty^\mathrm{lex}$ also has a left adjoint given by $\colimit (\ActsOn{*/\Cc}{\Omega})$
but we probably won't ever use this. More interestingly, we can apply \cref{thm:SpLeftAdjoint} to the stable $\infty$-categories $\Dd(R)$ and $\Kk(R)$ for any ring $R$, we obtain
\begin{equation*}
	\hom_{\Dd(R)}(C,D)\simeq H\big(R\!\Hom_R(C,D)\big)\quad\text{and}\quad\hom_{\Kk(R)}(C,D)\simeq H\big(\Hhom_R(C,D)\big)\,.
\end{equation*}
To prove the left equivalence, it suffices to check that we get $\Hom_{\Dd(R)}(C,D)$ after applying $\Omega^\infty$ (and that everything is functorial, but that will be clear). So we compute
\begin{align*}
	\Omega^\infty H\big(R\!\Hom_R(C,D)\big)\simeq K\big(R\!\Hom_R(C,D)\big)&\simeq \Hom_\An\big(*,K(R\!\Hom_R(C,D))\big)\\
	&\simeq \Hom_{\Dd(\IZ)}\big(\IZ,R\!\Hom_R(C,D)\big)\\
	&\simeq \Hom_{\Dd(R)}\left(\IZ\otimes_\IZ^LC,D\right)\\
	&\simeq	\Hom_{\Dd(R)}(C,D)\,,
\end{align*}
using $C_\bullet(*)\simeq \IZ$ and the derived tensor-$\Hom$ adjunction. The right equivalence can be proved analogously, but one should first check that $C_\bullet\colon \An\morphism \Dd_{\geq 0}(\IZ)$ already factors over $\Kk_{\geq 0}(\IZ)$ and gives rise to the same Eilenberg--MacLane functor $K\colon \Kk_{\geq 0}(\IZ)\morphism \An$. We haven't done this, but one can simply modify the construction in Very Long Example~\cref{exm:EilenberMacLane}.
\begin{proof}[Proof of \cref{thm:SpLeftAdjoint}]
	By the dual of Proposition~\labelcref{prop:LLaddendum}, all we need to show is that the two functors $\Omega^\infty\colon \Sp(\Sp(\Cc))\isomorphism\Sp(\Cc)$ and $\Omega^\infty_*\colon \Sp(\Sp(\Cc))\morphism\Sp(\Cc)$ are equivalences. But we know that $\Omega^\infty$ is one by \cref{exm:MyFirstSpectra}\itememph{a}. Also $\Omega_*^\infty$ is an equivalence too because it is a \enquote{coordinate flip} of $\Omega^\infty$. By that, we mean the following: Plugging in the definitions, we can write $\Sp(\Sp(\Cc))$ as a limit indexed by $\IN^\op\times\IN^\op$. Using the dual of \cref{prop:ColimitsCommute}, we can flip that diagram around, swapping $\Omega^\infty$ and $\Omega^\infty_*$, which proves the latter is an equivalence as well.
	
	For the \enquote{in particular}, we need another small argument similar to the proof* of \cref{cor:HomSemiAdditveFactorsThroughCGrpAn}, since $\Hom_\Cc\colon \Cc^\op\times\Cc\morphism \An$ isn't left exact. Every $\Hom_\Cc(x,-)\colon \Cc\morphism\An$ is, however, hence the adjunction provides us with canonical lifts $\hom_\Cc(x,-)\morphism\Sp$ for all $x\in \Cc$ when $\Cc$ is a stable $\infty$-category. To show that these combine into a functor $\hom_\Cc\colon \Cc^\op\times \Cc\morphism \An$, consider the full subcategory $\Fun^{\mathrm{lex}}(\Cc,\An)\subseteq \Fun(\Cc,\An)$ spanned by left exact functors. We claim that
	\begin{equation*}
		\Omega_*^\infty\colon\Fun^\mathrm{ex}(\Cc,\Sp)\isomorphism \Fun^\mathrm{lex}(\Cc,\An)
	\end{equation*}
	is an equivalence. Indeed, it becomes one after applying $\core(-)$ by the adjunction we've just proved. To show that it is an equivalence after $\core\Ar(-)$, we can use the same argument once we convince ourselves that $\Ar\Fun^\mathrm{ex}(\Cc,\Sp)\simeq \Fun^\mathrm{ex}(\Cc,\Ar(\Sp))$ (use that limits in arrow categories are pointwise by \cref{lem:f^*preservesColimits}) and that $\Ar(\Sp)\simeq \Sp(\Ar(\An))$ (use that $\Ar(-)$ commutes with limits).
	
	Now the Yoneda embedding $\Cc^\op\morphism \Fun(\Cc,\An)$ has image in $\Fun^\mathrm{lex}(\Cc,\An)\simeq \Fun^\mathrm{ex}(\Cc,\Sp)$ and we get our desired $\hom_\Cc$ after currying.
\end{proof}

\numpar*{Spectra and Prespectra}
We already know that $\Sp$ is complete and $\Omega^{\infty-i}\colon \Sp\morphism\An$ preserve limits. We also know from \cref{propdef:StableInftyCategory} that $\Sp$ has finite colimits because it is stable. But in fact we can even show that it is cocomplete! To see this, we will write $\Sp$ as a Bousfield localization of the $\infty$-category of \emph{prespectra}.

This can be introduced in general. So let $\Cc$ be an $\infty$-category with finite limits and (thus) a terminal object $*\in \Cc$. We let
\begin{equation*}
	\cat{PSp}(\Cc)\subseteq \Fun(\IN^2,*/\Cc)
\end{equation*}
be the full subcategory of functors that \enquote{vanish away from the diagonal}. So the objects of $\cat{PSp}(\Cc)$ can be pictured as lattice diagrams
\begin{equation*}
	\begin{tikzcd}[row sep=1.2em,column sep=1.2em]
		\vdots & \vdots & \vdots & \\
		*\rar\uar & *\rar\uar & X_2\rar\uar & \cdots \\
		*\rar\uar & X_1\rar\uar & *\rar\uar & \cdots\\
		X_0\rar\uar & *\rar\uar & *\rar\uar &\cdots
	\end{tikzcd}	
\end{equation*}
The diagonal squares induce morphisms $\Sigma X_i\morphism X_{i+1}$ (provided $\Cc$ has pushouts) or equivalently $X_i\morphism \Omega X_{i+1}$. If the latter were to be isomorphisms, we would recover $\Sp(\Cc)$, as we'll see in a moment.


To construct a fully faithful embedding $\Sp(\Cc)\monomorphism \cat{PSp}(\Cc)$, write $\IN^2=\colimit_{n\in \IN}\IN^2_{\leq (n,n)}$ as an ascending union of finite pieces $\IN^2_{\leq (n,n)}$ and consider the diagram
\begin{equation*}
	\begin{tikzcd}
		\cat{PSp}(\Cc)\rar[symbol=\subseteq] & \limit\limits_{n\in \IN^\op}\Fun\big(\IN^2_{\leq (n,n)},*/\Cc\big)\\
		\Sp(\Cc)\uar[dashed]\rar[iso] & \limit\limits_{n\in\IN^\op}*/\Cc\uar["\eta=\limit \eta_n"']
	\end{tikzcd}
\end{equation*}
The morphisms $\eta_n\colon {*/\Cc}\morphism \Fun(\IN^2_{\leq (n,n)},*/\Cc)$ send an object $X\in */\Cc$ to the right Kan extension of the functor
\begin{center}
	\begin{tikzpicture}[x=3em,y=3em,line cap=round]
		\node (00) at (0,0) {$\phantom{W}$};
		\node (10) at (1,0) {$*$};
		\node (20) at (2,0) {$\cdots$};
		\node (30) at (3,0) {$*$};
		\node (01) at (0,1) {$*$};
		\node (11) at (1,1) {$\phantom{W}$};
		\node (21) at (2,1) {$*$};
		\node[inner sep=0] (31) at (3,1) {$\raisebox{1.25ex}{\vdots}$};
		\node[inner sep=0] (02) at (0,2) {$\raisebox{1.25ex}{\vdots}$};
		\node (12) at (1,2) {$*$};
		\node (22) at (2,2) {$\phantom{W}$};
		\node (32) at (3,2) {$*$};
		\node (03) at (0,3) {$*$};
		\node (13) at (1,3) {$\cdots$};
		\node (23) at (2,3) {$*$};
		\node (33) at (3,3) {$X$};
		\draw[-to] (00) -- (01);
		\draw[-to] (01) -- (02);
		\draw[-to] (02) -- (03);
		\draw[-to] (10) -- (11);
		\draw[-to] (11) -- (12);
		\draw[-to] (12) -- (13);
		\draw[-to] (20) -- (21);
		\draw[-to] (21) -- (22);
		\draw[-to] (22) -- (23);
		\draw[-to] (30) -- (31);
		\draw[-to] (31) -- (32);
		\draw[-to] (32) -- (33);
		\draw[-to] (00) -- (10);
		\draw[-to] (10) -- (20);
		\draw[-to] (20) -- (30);
		\draw[-to] (01) -- (11);
		\draw[-to] (11) -- (21);
		\draw[-to,shorten >=1ex] (21) -- (31);
		\draw[-to,shorten <=1ex] (02) -- (12);
		\draw[-to] (12) -- (22);
		\draw[-to] (22) -- (32);
		\draw[-to] (03) -- (13);
		\draw[-to] (13) -- (23);
		\draw[-to] (23) -- (33);
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (00) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (11) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (22) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\path (0,-0.5) to node {$\underbrace{\hspace{10em}}$} node[below=0.5ex] {$\scriptstyle n+1$} (3,-0.5);
		\path (3.5,0) to node[sloped] {$\underbrace{\hspace{10em}}$} node[right=0.5ex] {$\scriptstyle n+1$} (3.5,3);
		\node[left] at (-0.25,1.5) {$\IN^2_{\leq(n,n)}$};
	\end{tikzpicture}
\end{center}
Note the blank spots along the diagonal, except for the $(n,n)\ordinalth$ entry! So we right-Kan extend along the inclusion $\IN^2_{\leq (n,n)}\smallsetminus \{(0,0),\dotsc,(n-1,n-1)\}\subseteq \IN^2_{\leq (n,n)}$. Since this inclusion is fully faithful, \cref{cor:FullyFaithfulKanExtension} (combined with \cref{propdef:BousfieldLocalization}\itememph{a}) shows that $\eta_n$ is fully faithful, and thus also the limit $\eta$ over all $\eta_n$ gives a fully faithful map between the limits. One easily checks that the image of $\eta$ lands in the full subcategory $\cat{PSp}(\Cc)$ and thus we get the desired fully faithful functor $\Sp(\Cc)\monomorphism \cat{PSp}(\Cc)$.

As another consequence of the maps $\eta_n$ being defined by right Kan extension, we obtain canonical equivalences
\begin{equation*}
	\Hom_{\cat{PSp}(\Cc)}(X,Y)\simeq \limit_{n\in \IN^\op}\Hom_{*/\Cc}(X_n,Y_n)
\end{equation*}
for all $X\in \cat{PSp}(\Cc)$ and $Y\in \Sp(\Cc)$ (just compute the left-hand side as a $\Hom$ anima in $\limit_{n\in \IN^\op}\Fun(\IN_{\leq (n,n)}^2,*/\Cc)$ and use the universal property of right Kan extension).

Note that $\cat{PSp}(\Cc)$ inherits all limits and colimits from $*/\Cc$. Also $\Sp(\Cc)\subseteq \cat{PSp}(\Cc)$ is closed under limits, but not colimits. To show that $\Sp(\Cc)$ is cocomplete (under appropriate conditions), we need to show that it is in fact a Bousfield localization of $\cat{PSp}(\Cc)$. This is done by the following proposition (which we prove only after some consequences are discussed).
\begin{prop}\label{prop:Spectrification}
	If $*/\Cc$ has sequential colimits and $\Omega\colon {*/\Cc}\morphism*/\Cc$ commutes with them, then the inclusion $\Sp(\Cc)\subseteq\cat{PSp}(\Cc)$ has a left adjoint $(-)^\mathrm{sp}\colon \cat{PSp}(\Cc)\morphism\Sp(\Cc)$. On objects it is given by
	\begin{equation*}
		\Omega^{\infty-i}(X^\mathrm{sp})\simeq \colimit_{n\in \IN}\Omega^nX_{n+i}\,,
	\end{equation*}
	where the transition maps are induced by the morphisms $X_i\morphism\Omega X_{i+1}$ that where constructed on the previous page.
\end{prop}
Observe that $\Cc=\An$ meets the condition of \cref{prop:Spectrification}. Indeed, we can replace any sequential diagram $(X_1\morphism X_2\morphism \dotso)$ in $\An$ by a diagram $(X_1'\monomorphism X_2'\monomorphism \dotso)$ $\Kan$ such that all transition maps are cofibrations; then \cref{thm:HomotopyLimits} allows us to compute the colimit in $\Kan$ instead. Now write $\Omega\simeq \F_*(\IS^1,-)$ as the pointed mapping space out of $\IS^1$ (or any simplicial model for it, it doesn't even need to be Kan) and observe that the right-hand side commutes with filtered colimits in $\Kan$ because $\IS^1$ is compact. Thus we see that $\Sp$ is a Bousfield localization of $\cat{PSp}$ and therefore cocomplete by \cref{cor:CoLimitsInBousfield}.

Similarly to our construction of the embedding $\Sp(\Cc)\subseteq \cat{PSp}(\Cc)$, one can show that $\ev_{(0,0)}\colon \cat{PSp}(\Cc)\morphism */\Cc$ has a left adjoint $\snake{\Sigma}^\infty\colon {*/\Cc}\morphism \cat{PSp}(\Cc)$ if $\Cc$ has finite colimits. On objects $c\in */\Cc$, we define $\Sigma^\infty c$ to be the left Kan extension of
\begin{center}
	\begin{tikzpicture}[x=3em,y=3em,line cap=round]
		\node (00) at (0,0) {$c$};
		\node (10) at (1,0) {$*$};
		\node (20) at (2,0) {$\cdots$};
		\node (30) at (3,0) {$*$};
		\node (01) at (0,1) {$*$};
		\node (11) at (1,1) {$\phantom{W}$};
		\node (21) at (2,1) {$*$};
		\node[inner sep=0] (31) at (3,1) {$\raisebox{1.25ex}{\vdots}$};
		\node[inner sep=0] (02) at (0,2) {$\raisebox{1.25ex}{\vdots}$};
		\node (12) at (1,2) {$*$};
		\node (22) at (2,2) {$\phantom{W}$};
		\node (32) at (3,2) {$*$};
		\node (03) at (0,3) {$*$};
		\node (13) at (1,3) {$\cdots$};
		\node (23) at (2,3) {$*$};
		\node (33) at (3,3) {$\phantom{W}$};
		\draw[-to] (00) -- (01);
		\draw[-to] (01) -- (02);
		\draw[-to] (02) -- (03);
		\draw[-to] (10) -- (11);
		\draw[-to] (11) -- (12);
		\draw[-to] (12) -- (13);
		\draw[-to] (20) -- (21);
		\draw[-to] (21) -- (22);
		\draw[-to] (22) -- (23);
		\draw[-to] (30) -- (31);
		\draw[-to] (31) -- (32);
		\draw[-to] (32) -- (33);
		\draw[-to] (00) -- (10);
		\draw[-to] (10) -- (20);
		\draw[-to] (20) -- (30);
		\draw[-to] (01) -- (11);
		\draw[-to] (11) -- (21);
		\draw[-to,shorten >=1ex] (21) -- (31);
		\draw[-to,shorten <=1ex] (02) -- (12);
		\draw[-to] (12) -- (22);
		\draw[-to] (22) -- (32);
		\draw[-to] (03) -- (13);
		\draw[-to] (13) -- (23);
		\draw[-to] (23) -- (33);
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (33) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (11) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\draw[FabiansPurple!67!FabiansPink,dotted, rounded corners=2] (22) ++ (-1ex,-1ex) -- ++ (2ex,0) -- ++ (0,2ex) -- ++(-2ex,0) -- cycle;
		\path (0,-0.5) to node {$\underbrace{\hspace{10em}}$} node[below=0.5ex] {$\scriptstyle n+1$} (3,-0.5);
		\path (3.5,0) to node[sloped] {$\underbrace{\hspace{10em}}$} node[right=0.5ex] {$\scriptstyle n+1$} (3.5,3);
		\node[left] at (-0.25,1.5) {$\IN^2_{\leq(n,n)}$};
	\end{tikzpicture}
\end{center}
Again, note the blank spots along the diagonal, so the Kan extension is along the inclusion $\IN^2_{\leq (n,n)}\smallsetminus \{(1,1),\dotsc,(n,n)\}\subseteq \IN^2_{\leq (n,n)}$ this time.

Combining this with \cref{prop:Spectrification}, we see that $\Omega^\infty\colon\Sp\morphism {*/\An}$ has a left adjoint $\Sigma^\infty=(\snake{\Sigma}^\infty)^\mathrm{sp}\colon {*/\An}\morphism\Sp$. Plugging in the explicit formulas for Kan extension (\cref{thm:KanExtension}) to compute $\snake{\Sigma}^\infty$, we get
\begin{equation*}
	\Omega^\infty\Sigma^\infty(X,x)\simeq \colimit_{n\in \IN}\Omega^n\Sigma^n(X,x)
\end{equation*}
for all $(X,x)\in */\An$. The left-hand side is sometimes denoted $Q(X,x)$, but that has nothing to do with the Quillen $Q$-construction (see page~\labelcpageref{par:QuillenQConstruction}).

We will denote the composite
\begin{equation*}
	\IS[-]\colon \An\xrightarrow{(-)_+}*/\An\morphism[\Sigma^\infty]\Sp\,.
\end{equation*}
In particular, we obtain $\IS\coloneqq\IS[*]\simeq \Sigma^\infty(\IS^0,*)$, the mythical \emph{sphere spectrum}. Plugging in the adjunctions we know gives $\Hom_\Sp(\IS,-)\simeq \Hom_\An(*,\mathop{\Omega^\infty}-)\simeq \Omega^\infty$, so $\IS$ represents the functor $\Omega^\infty\colon \Sp\morphism\An$. Its homotopy groups are
\begin{equation*}
	\pi_i(\IS)=\colimit_{n\in\IN} \pi_i\Omega^n\Sigma^n(\IS^0,*)=\colimit_{n\in\IN}\pi_{i+n}(\IS^n,*)\,,
\end{equation*}
i.e.\ the \emph{stable homotopy groups of spheres}. In contrast to the vastly complicated problem of computing these, the homology of $\IS$ (defined as in \cref{par:HomologyOfSpectra}) is rather boring:
\begin{equation*}
	H_i(\IS,A)=\begin{cases*}
		A & if $i=0$\\
		0 & else
	\end{cases*}\,.
\end{equation*}
Proving this is not completely trivial, however, since one needs a bit of homotopy theory to compute $H_*(\Omega^n\IS^n,A)$ in low degrees.
\begin{cor}[Baratt--Priddy--Quillen]\label{cor:BarattPriddyQuillen}
	The functor $\ev_1\colon \CGrp(\An)\morphism */\An$ has a left adjoint $\Free^\CGrp\colon {*/\An}\morphism \CGrp(\An)$ given by
	\begin{equation*}
		\Free^\CMon(X,x)^\inftygrp\simeq\Free^\CGrp(X,x)\simeq \Omega^\infty\Sigma^\infty(X,x)\,.
	\end{equation*}
	Here $\Omega^\infty\colon \Sp_{\geq 0}\isomorphism \CGrp(\An)$ denotes the inverse of $B^\infty\colon \CGrp(\An)\isomorphism \Sp_{\geq 0}$, which we recall is an equivalence by \cref{cor:RecognitionForInfiniteLoopSpaces}.
\end{cor}
\begin{proof*}
	We didn't spell this out in the lecture since there isn't much to do: It's evident that $\Sigma^\infty\colon {*/\An}\morphism \Sp$ lands in the full subcategory $\Sp_{\geq 0}$, hence it's also a left-adjoint to $\Omega^\infty\colon \Sp_{\geq 0}\morphism */\An$. After applying the other $\Omega^\infty$ (i.e.\ the inverse of $B^\infty$) we obtain the second equivalence. For the first equivalence, recall that \cref{cor:CommutativeHorizontalAdjoints} actually shows that the $\IE_1$-group completion of an $\IE_\infty$-monoid has a canonical $\IE_\infty$-group structure.
\end{proof*}
Applying \cref{cor:BarattPriddyQuillen} to the unnumbered example on page~\labelcpageref{par:FreeCMon}, we see that
\begin{equation*}
	\big(\{\text{finite sets, bijection}\},\sqcup\big)^\inftygrp\simeq \Free^\CMon(*)^\inftygrp\simeq \Omega^\infty\IS\,,
\end{equation*}
an example that Fabian already terrified us with in the introduction.


\begin{proof}[Proof of \cref{prop:Spectrification}]
	By \cref{cor:AdjointsPointwise}, it suffices to check that $X^\mathrm{sp}$ as defined there is really a spectrum and a left-adjoint object to $X$ for all $X\in \cat{PSp}(\Cc)$. To check the first, we compute
	\begin{equation*}
		\Omega X_{i+1}^\mathrm{sp}\simeq \Omega\colimit_{n\in \IN}\Omega^nX_{n+i+1}\simeq \colimit_{n\in \IN}\Omega^{n+1}X_{n+i+1}\simeq \colimit_{n\in\IN}\Omega^nX_{n+i}\simeq X_i^\mathrm{sp}
	\end{equation*}
	(and all of this is functorial) since $\Omega$ commutes with sequential colimits. To check that $X^\mathrm{sp}$ is really a left-adjoint object of $X$, we compute
	\begin{align*}
		\Hom_{\Sp(\Cc)}(X^\mathrm{sp},Y)&\simeq \limit_{i\in \IN^\op}\Hom_{*/\Cc}\left(X_i^\mathrm{sp},Y_i\right)\\
		&\simeq\limit_{i\in\IN^\op}\left(\colimit_{n\in \IN}\Omega^nX_{n+i},Y_i\right)\\
		&\simeq \limit_{i\in\IN^\op}\Hom_{*/\Cc}\bigg(\colimit_{n\in\IN_{\geq i}}\Omega^{n-i}X_n,\Omega^{n-i}Y_n\bigg)\\
		&\simeq \limit_{i\in\IN^\op}\limit_{n\in \IN^\op_{\geq i}}\Hom_{*/\Cc}\left(\Omega^{n-i} X_n,\Omega^{n-i}Y_n\right)\\
		&\simeq \limit_{n\in \IN^\op}\limit_{j\in \IN_{\leq n}}\Hom_{*/\Cc}\left(\Omega^jX_n,\Omega^jY_n\right)\\
		&\simeq \limit_{n\in \IN^\op}\Hom_{*/\Cc}(X_n,Y_n)\\
		&\simeq \Hom_{\cat{PSp}(\Cc)}(X,Y)\,.
	\end{align*}
	The first two equivalences are just plugging in definitions. For the third equivalence, we do an index shift by $-i$ and use $\Omega^{n-i}Y_n\simeq Y_i$ since $Y$ is a spectrum. The fourth equivalence is \cref{cor:HomPreservesColimits}. For the fifth equivalence, we substitute $j=n-i$ and use that limits commute (by the dual of \cref{prop:ColimitsCommute}). Since $j$ has \enquote{negative slope in $i$}, we really take the limit over $j\in \IN_{\leq n}$; the missing $(-)^\op$ is no typo (and crucial). The sixth equivalence now follows from the fact that $j=0$ is initial in $0\in \IN_{\leq n}$. Finally, the seventh equivalence is the formula we deduced just before the formulation of \cref{prop:Spectrification}. 
\end{proof}
Our next goal is to define a more \enquote{Segal style} model for $\Sp(\Cc)$. To do this, we construct another $\infty$-category $\IF^\op$. Fabian remarks that this symbol is not the \texttt{\textbackslash mathbb}-version of the Roman letter F, but of the archaic Greek letter Digamma, which was the letter after Gamma and Delta in the ancient Greek alphabet, so $\IGamma^\op$, $\IDelta^\op$, and $\IF^\op$ fit together nicely. \href{https://en.wikipedia.org/wiki/Digamma}{Wikipedia} claims, however, that Digamma was only the sixth letter and that Epsilon came between it and Delta. Nevertheless, I'll obediently stick to Fabian's notation. I took the liberty though to typeset that symbol using \verb|\mathbb{F}| (I'm already going to \LaTeX hell for my $\IGamma$ being a \verb|\mathbb{L}| turned upside down \dotso).
\begin{defi}
	Let $\IF^\op\subseteq */\An$ be the smallest sub-$\infty$-category containing $\IS^0$ and closed under finite colimits. There's a functor $\IGamma^\op\morphism\IF^\op$ sending $\langle n\rangle$ to $\langle n\rangle_+$ (i.e.\ we add a basepoint to the discrete anima $\langle n\rangle$) and any partially defined map $\alpha\colon\langle m\rangle \morphism\langle n\rangle$ to the map $\alpha_+\colon \langle m\rangle_+\morphism\langle n\rangle_+$ which is $\alpha$ wherever it is defined and sends everything else to the basepoint.
	
	Finally, if $\Cc$ is an $\infty$-category with finite limits and (thus) a terminal object $*\in\Cc$, we define $\widetilde{\Sp}(\Cc)\subseteq \Fun(\IF^\op,*/\Cc)$ to be the full subcategory of functors taking pushouts to pullbacks and $*=\langle 0\rangle_+$ to $*\in \Cc$. 
\end{defi}
Note that $\widetilde{\Sp}(\Cc)$ is stable: It has finite limits inherited from $*/\Cc$ and $\Omega$ is an equivalence with inverse induced by precomposition with $\Sigma\colon \IF^\op\morphism \IF^\op$. Hence the criterion from \cref{propdef:StableInftyCategory}\itememph{a} is fulfilled.
\begin{prop}
	There is a natural equivalence of $\infty$-categories
	\begin{align*}
		\widetilde{\Sp}(\Cc)&\isomorphism \Sp(\Cc)\\
		F&\longmapsto \big(F(\IS^0),F(\IS^1),\dotsc\big)\,.
	\end{align*}
\end{prop}
\begin{proof}[Proof sketch]
	There are multiple ways to prove this. One can directly show that $\widetilde{\Sp}(\Cc)$ satisfies the universal property from \cref{thm:SpLeftAdjoint}. Or one can simply check that both $\ev_{\IS^0}\colon \widetilde{\Sp}(\widetilde{\Sp}(\Cc))\isomorphism \widetilde{\Sp}(\Cc)$ and $\ev_{\IS^0,*}\colon \widetilde{\Sp}(\widetilde{\Sp}(\Cc))\isomorphism\widetilde{\Sp}(\Cc)$ are equivalences and then apply the same reasoning as in the proof of that theorem.
	
	We will sketch a third way by constructing an inverse functor. For this, we use the following general construction: Let $\An^\mathrm{fin}\subseteq \An$ denote the smallest sub-$\infty$-category containing $*$ and closed under finite colimits. Let $\Dd$ be any $\infty$-category with finite limits and colimits. For $d\in \Dd$ we put
	\begin{equation*}
		X\otimes d\coloneqq \colimit_X\const_d\quad\text{and}\quad d^X\coloneqq \limit_X\const_d\,.
	\end{equation*}
	These exist by assumption and are functorial in $X$ and $d$. If $(X,x)\in \IF^\op$ and $\Dd$ is \emph{pointed}, i.e.\ has a zero object, then we put
	\begin{equation*}
		(X,x)\otimes d\coloneqq \cofib\left(\colimit_{\{x\}}\const_d\rightarrow \colimit_Xd\right)\,.
	\end{equation*}
	The inverse functor $\Sp(\Cc)\morphism\widetilde{\Sp}(\Cc)$ now sends a spectrum $E\in \Sp(\Cc)$ to the functor $\Omega^\infty(-\otimes E)\colon \IF^\op\morphism */\Cc$. Note that $\Sp(\Cc)$ has finite colimits since it is stable, so the functor $-\otimes E\colon \IF^\op\morphism \Sp(\Cc)$ is well-defined.
\end{proof}
The functors $-\otimes E$ and $E^{(-)}$ for spectra are interesting on their own. Observe for example that $X\otimes HA\simeq H(C_\bullet(X)\otimes_\IZ^LA)$, since both sides are colimit-preserving functors $\An\morphism\Sp$ with value $HA$ on $*\in \An$, hence they are equal by \cref{thm:ColimitPreservingRepresentable} and the fact that $\Sp$ is cocomplete. This motivates the following definition.
\begin{defi}
	Let $E\in \Sp$ and $X\in \An$. The \emph{homology} and \emph{cohomology theory} associated to $E$ are defined by
	\begin{equation*}
		E_*(X)=\pi_*(X\otimes E)=\pi_*\left(\colimit_XE\right)\quad\text{and}\quad
		E^*(X)=\pi_{-*}(E^X)=\pi_{-*}\left(\limit_XE\right)\,.
	\end{equation*}
\end{defi}
A little bit of foreshadowing: We can also extend the tensor product (or \emph{smash product}) $-\otimes -$ to all of $\Sp$ by defining
\begin{equation*}
	E\otimes E'\coloneqq\colimit_{i\in \IN}\Omega^i\big((\Omega^{\infty-i}E')\otimes E\big)
\end{equation*}
(the outer $\Omega^i$ is the intrinsic loop functor on $\Sp$, the inner is $\Omega^{\infty-i}\colon \Sp\morphism*/\An$). It turns out that this defines a symmetric monoidal structure on $\Sp$ behaving like $-\otimes_\IZ^L-$ on $\Dd(\IZ)$, although not even symmetry is in any way obvious from the definition. Proving this will be the content of the next few lectures. 

In the end we will see that $X\otimes E\simeq \IS[X]\otimes E$ and $E^X\simeq \hom_\Sp(\IS[X],E)$ for all $X\in\An$. If $X$ is an $\IE_\infty$-monoid, it's usually very hard to understand its group completion $X^\inftygrp$. But we can sometimes understand $\IS[X^\inftygrp]\in \Sp$. This is still good enough to compute $H_*(X^\inftygrp,A)$ or even $E_*(X^\inftygrp)$, which will be the  content of the \enquote{group completion theorem}. Once we have this, we're in business to compute some $K$-groups!
\subsection{An Interlude on Operads}
\lecture[Operads. Symmetric monoidal $\infty$-category as operads, strict vs.\ lax monoidal functors. Some examples. A technical lemma about presheaves.]{2020-12-17}
Recall that a morphism in $\IGamma^\op$ is \emph{inert} if it is a bijection (where it is defined) and \emph{active} if it is defined everywhere. This yields two subcategories $\IGamma^\op_{\mathrm{act}}$ and $\IGamma^\op_{\mathrm{int}}$. Recall also that symmetric monoidal $\infty$-categories are precisely the objects of $\CMon(\Cat_\infty)$, which is a full subcategory of $\Cocart(\IGamma^\op)$ via cocartesian unstraightening.
\begin{defi}\label{def:Operad}
	A \emph{\embrace{multicoloured and symmetric} operad \embrace{in anima}} is a functor $p\colon \Oo\morphism \IGamma^\op$ of $\infty$-categories such that the following conditions hold:
	\begin{alphanumerate}
		\item Every inert in $\IGamma^\op$ has cocartesian lifts with arbitrary sources (in the invariant sense of \cref{def:WeirdCocartesianDefinition}\itememph{b}).
		\item The functor $\Oo\colon\IGamma_\mathrm{int}^\op\morphism \Cat_\infty$ arising by cocartesian straightening satisfies the Segal condition. That is, $\Oo_0\simeq *$ and $\Oo_n\simeq \prod_{i=1}^n\Oo_1$ via the Segal maps $\rho_1,\dotsc,\rho_n\colon \langle n\rangle \morphism \langle 1\rangle$.
		\item Let $x,y\in \Oo$ with $p(x)=\langle m\rangle$ and $p(y)=\langle n\rangle$. By \itememph{b}, we can write $y\simeq (y_1,\dotsc,y_n)$ for some $y_i\in \Oo_1$. Then we require that the diagram
		\begin{equation*}
			\begin{tikzcd}[column sep=large]
				\Hom_\Oo(x,y)\rar["{(\rho_1,\dotsc,\rho_n)}"]\drar[pullback]\dar["p"'] & \displaystyle\prod_{i=1}^n\Hom_\Oo(x,y_i)\dar[shorten <=-2.5ex,shorten >=-2ex,"p"] \\
				\Hom_{\IGamma^\op}\big(\langle m\rangle,\langle n\rangle\big)\rar["{(\rho_1,\dotsc,\rho_n)}"]& \displaystyle\prod_{i=1}^n\Hom_{\IGamma^\op}\big(\langle m\rangle,\langle 1\rangle\big)
			\end{tikzcd}
		\end{equation*}
		is a pullback. Note that the bottom arrow is an injective map of sets!
	\end{alphanumerate}
	We call a morphism $f\colon x\morphism y$ in $\Oo$ \emph{inert} if it is a $p$-cocartesian lift of an inert morphism in $\IGamma$. We call $f$ \emph{active} if it is a (not necessarily $p$-cocartesian) lift of an active morphism. We also call $\Oo_1$ the \emph{underlying $\infty$-category} of $\Oo$.
	
	Finally, the $\infty$-category $\cat{Op}$ of operads is the (non-full) sub-$\infty$-category of $\Cat_\infty/\IGamma^\op$ spanned by the operads and by functors which preserve inert morphisms.
\end{defi}
\begin{exm}
	\begin{alphanumerate}
		\item The cocartesian unstraightening induces a functor
		\begin{equation*}
			(-)^\otimes=\Un^\cocart\colon \CMon(\Cat_\infty)\morphism \cat{Op}\,.
		\end{equation*}
		To see this, note that conditions \cref{def:Operad}\itememph{a} and \itememph{b} are trivially satisfied, so we only have to check \itememph{c}. We've already remarked that the bottom row of the diagram in question is an injection of discrete anima, hence we must show that the top row is an inclusion of the corresponding path components. So let $\alpha\colon \langle m\rangle \morphism\langle n\rangle $ be some morphism and denote by $\Hom_\Oo^\alpha(x,y)$ the path component over $\alpha$. Let $x\morphism \alpha_*(x)$ be a $p$-cocartesian lift of $\alpha$ and consider the diagram
		\begin{equation*}
			\begin{tikzcd}[column sep=large]
				\Hom_{\Oo_n}(\alpha_*x,y)\rar[iso]\dar[iso] & \displaystyle\prod_{i=1}^n\Hom_{\Oo_1}\big((\alpha_*x)_i,y_i\big)\dar[shorten <=-2.5ex,shorten >=-2ex,iso] \\
				\Hom_{\Oo}^\alpha(x,y)\rar & \displaystyle\prod_{i=1}^n\Hom_{\Oo}^{\rho_i\circ\alpha}(x,y)
			\end{tikzcd}
		\end{equation*}
		That the vertical arrows are equivalences follows easily from the fact that $x\morphism \alpha_*x$ is $p$-cocartesian and the pullback diagram in \cref{def:WeirdCocartesianDefinition}\itememph{a}. The top arrow is an equivalence by the Segal condition. Hence the bottom arrow is an equivalence as well, which is what we wanted to show. Thus $(-)^\otimes$ has its image in contained in $\cat{Op}\subseteq \Cat_\infty/\IGamma^\op$, as claimed.
		
		However, $(-)^\otimes$ is not fully faithful. In $\CMon(\Cat_\infty)$ a morphism is a \emph{strongly} symmetric monoidal functor, i.e.\ it has to preserve the tensor product. We define a \emph{lax symmetric monoidal functor} $\Cc\morphism\Dd$ to be a map of operads $\Cc^\otimes\morphism\Dd^\otimes$. We can now define $\infty$-categories $\cat{SymMonCat}_\infty\simeq \CMon(\Cat_\infty)$ and $\cat{SymMonCat}_\infty^\mathrm{lax}\subseteq \cat{Op}$ to be the essential image of $(-)^\otimes$.
		
		How do we recognize the essential image of $(-)^\otimes$? By the Segal condition and the fact that $p\colon \Oo\morphism \IGamma^\op$ has $p$-cocartesian lifts for all inert morphisms, it suffices to check that it has $p$-cocartesian lifts for the unique active maps $f_n\colon \langle n\rangle \morphism \langle 1\rangle$ (we leave it as an exercise to work out a proper argument). This is in turn equivalent to the following: For elements $(a_1,\dotsc,a_n)\in \Oo_n$ and $b\in \Oo_1$ define the \emph{multi-morphism space}
		\begin{equation*}
			\begin{tikzcd}
				\Hom_\Oo^\mathrm{act}\big((a_1,\dotsc,a_n),b\big)\dar\drar[pullback]\rar & \Hom_\Oo\big((a_1,\dotsc,a_n),b\big)\dar\\
				*\rar["f_n"] & \Hom_{\IGamma^\op}\big(\langle n\rangle,\langle 1\rangle\big)
			\end{tikzcd}
		\end{equation*}
		Then a morphism $g\colon (a_1,\dotsc,a_n)\morphism a$ over $f_n$ is a $p$-cocartesian lift iff the precomposition $g^*\colon \Hom_{\Oo_1}(a,-)\isomorphism \Hom_\Oo^\mathrm{act}((a_1,\dotsc,a_n),-)$ is an equivalence of functors $\Oo_1\morphism \An$. The way to think about this is that \enquote{$a\simeq a_1\otimes\dotsb\otimes a_n$} and that an operad $\Oo$ is the data you need to make a \enquote{category in which you specify what a map out of a tensor product should be}. Whether such a category exists should equivalent to whether $\Oo\simeq \Cc^\otimes$ for some $\Cc\in \CMon(\Cat_\infty)$.
		
		\item There is an entirely dual theory of \emph{dual operads} (but that's not the same thing as cooperads). These are the functors to $\IGamma$ satisfying \cref{def:Operad}\itememph{a}, \itememph{b}, and \itememph{c} for cartesian lifts. The resulting category $\cat{dOp}$ is equivalent to $\cat{Op}$ via $(-)^\op\colon \cat{Op}\isomorphism \cat{dOp}$. Note, however, that this doesn't preserve underlying $\infty$-categories. Instead it fits into a diagram
		\begin{equation*}
			\begin{tikzcd}
				\cat{Op}\rar[iso]\dar["{(-)_1}"'] & \cat{dOp}\dar["{(-)_1}"]\\
				\Cat_\infty\rar["{(-)^\op}"] & \Cat_\infty
			\end{tikzcd}
		\end{equation*}
		The image of the cartesian unstraightening $\Un^\cart\colon \CMon(\Cat_\infty)\morphism\cat{dOp}$ is denoted $\cat{SymMonCat}_\infty^{\mathrm{oplax}}$, thought of as symmetric monoidal $\infty$-categories with oplax monoidal functors.
		\item Here are some trivial operads: The functors $\IGamma^\op_\mathrm{int}\morphism\IGamma^\op$, $\langle 0\rangle\morphism \IGamma^\op$, and $\id\colon \IGamma^\op\morphism \IGamma^\op$.
		\item Let $\Cc^\otimes\morphism\IGamma^\op$ be a symmetric monoidal structure on $\Cc$ and $\Dd\subseteq \Cc$ a full sub-$\infty$-category. Define $\Dd^\otimes\subseteq \Cc^\otimes$ to be the full sub-$\infty$-category spanned by the $d\simeq(d_1,\dotsc,d_n)$ with $d_i\in \Dd$. Then $\Dd^\otimes\morphism\IGamma^\op$ is an operad which is a symmetric monoidal category iff $d\otimes d'\in \Dd$ for all $d,d'\in \Dd$ and $1_\Cc\in \Dd$.
		
		Since I didn't find this completely obvious, here's a full argument. To check that $\Dd^\otimes$ is an operad, the conditions from \cref{def:Operad}\itememph{b} and \itememph{c} are immediately inherited from $\Cc^\otimes$. To check the remaining condition \itememph{a}, we must check that whenever $d\morphism d'$ is a cocartesian lift of an inert morphism in $\IGamma^\op$ with $d\in \Dd^\otimes$, then also $d'\in \Dd^\otimes$. Say $d\in \Dd_n^\otimes$ and let $d\simeq (d_1,\dotsc,d_n)$. Then the components $d_i\in \Dd_1^\otimes$ are precisely the endpoints of cocartesian lifts $d\morphism d_i$ of $\rho_i\colon \langle n\rangle \morphism\langle 1\rangle$. Since cocartesian lifts compose (see \cite[Proposition~IX.5]{HigherCatsII}), we see that the components of $d'$ are a subset of the components of $d$, hence $d'\in \Dd^\otimes$ as well. This shows that $\Dd^\otimes$ is indeed an operad. The further claim about when it is a symmetric monoidal category follows from the recognition criterion sketched in \itememph{a}.		 
		\item Let $R$ be a commutative ring. One can check that $\Ch(R)$ is symmetric monoidal under $-\otimes_R-$ as a Kan-enriched category, hence its coherent nerve $\Kk(R)$ is symmetric monoidal. Now recall from \cref{exm:MyFirstBousfield}\itememph{c} that $\Dd(R)$ is a Bousfield localization of $\Kk(R)$. More precisely, $\Dd(R)$ can be embedded fully faithfully into $\Kk(R)$ as the full sub-$\infty$-category $\Dd(R)^{K\mhyph\mathrm{proj}}\subseteq \Kk(R)$ of $K$-projective complexes, i.e.\ those $C$ such that $\Hom_{\Kk(R)}(C,-)$ inverts quasi-isomorphisms. Clearly the tensor unit $R[0]$ is $K$-projective (as is any bounded below degree-wise projective complex) and if $C$ and $D$ are $K$-projective, then so is $C\otimes_RD$ as $\Hom_{\Kk(R)}(C\otimes_RD,-)\simeq \Hom_{\Kk(R)}(C,\Hhom_R(D,-))$ inverts quasi-isomorphisms too.
		
		We may thus apply \itememph{d} to obtain a symmetric monoidal structure $-\otimes_R^L-$ on $\Dd(R)$. The localization functor $\Kk(R)\morphism\Dd(R)$ (\enquote{taking $K$-projective resolutions}) is lax symmetric monoidal in the sense explained in \itememph{a}. In particular, there are canonical maps $C\otimes_R^LD\morphism C\otimes_RD$ for all $C,D\in \Kk(R)$.
	\end{alphanumerate}
\end{exm}
Our next goal is to make cartesian and cocartesian monoidal structures on $\infty$-categories with products, and eventually to define the symmetric monoidal structure on $\Sp$. While Lurie writes down explicit simplicial sets to construct the desired operads, we will cheat a bit and use complete Segal spaces instead. This is based on the following lemma.
\begin{lem}\label{lem:TautologicalPresheafLemma}
	Let $\Ee$ be an $\infty$-category. For a presheaf $X\in \Pp(\Ee)$, consider the slice category $\Ee/X$ with respect to the Yoneda embedding $Y^\Ee\colon \Ee\morphism P(\Ee)$ and $\{X\}\morphism \Pp(\Ee)$ \embrace{in the notation of \cref{lem*:PresheafColimitOfRepresentables} this would have been $Y^\Ee/X$ instead}. The canonical functor
	\begin{equation*}
		\Pp(\Ee/X)\isomorphism \Pp(\Ee)/X\,,
	\end{equation*}
	constructed as the unique colimit-preserving extension of $Y^\Ee\colon\Ee/X\morphism \Pp(\Ee)/X$ via \cref{thm:ColimitPreservingRepresentable}, is an equivalence of $\infty$-categories.
\end{lem}
Applying \cref{lem:TautologicalPresheafLemma} to $\Ee=\IDelta$ and $X=\N^r(\Cc)\in \cat{sAn}$ for some $\infty$-category $\Cc$, we obtain $\Pp(\IDelta/\N^r(\Cc))\simeq \cat{sAn}/\N^r(\Cc)$. We will usually abbreviate the left-hand side as $\Pp(\IDelta/\Cc)$. This allows us to specify functors to $\Cat_\infty/\Cc$ as functors to $\Pp(\IDelta/\Cc)$ and then compose with 
\begin{equation*}
	\Pp(\IDelta/\Cc)\simeq \cat{sAn}/\N^r(\Cc)\xrightarrow{\asscat}\Cat_\infty/\Cc\,.
\end{equation*}
\begin{proof}[Proof of \cref{lem:TautologicalPresheafLemma}]
	Before we start, observe that $\Pp(\Ee)/X$ is indeed cocomplete since one immediately checks that it inherits colimits from $\Pp(\Ee)$. We will use the following criterion:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}]\itshape\label{claim:EquivalenceCondition} Let $F\colon \Cc\morphism\Dd$ be a functor from a small $\infty$-category to a cocomplete $\infty$-category. Let $|\blank|_F\colon \Pp(\Cc)\shortdoublelrmorphism \Dd\noloc \Sing_F$ denote the adjunction resulting from \cref{thm:ColimitPreservingRepresentable}. Suppose furthermore that the following conditions hold:
		\begin{alphanumerate}
			\item $F$ is fully faithful.
			\item $\Hom_\Dd(F(c),-)\colon\Dd\morphism\An$ commutes with colimits for all $c\in \Cc$.
			\item $\Sing_F\colon \Dd\morphism \Pp(\Cc)$ is conservative.
		\end{alphanumerate}
		Then $|\blank|_F\colon \Pp(\Cc)\isomorphism\Dd$ is an equivalence.
	\end{alphanumerate}
	We prove \itememph{\boxtimes} first. Condition~\itememph{b} implies that $\Sing_F$ commutes with colimits. Indeed, this can be checked pointwise by \cref{thm:JoyalEquivalence}\itememph{b} since there always is a natural transformation $\colimit_\Ii\Sing_F\Rightarrow\Sing_F\colimit_\Ii$. Moreover, colimits in $\Pp(\Cc)$ are computed pointwise. Plugging in the explicit description of $\Sing_F$ that \cref{cor:ExplicitAdjoint} offers us, we must thus check that $\colimit_\Ii\Hom_\Dd(F(c),d_i)\simeq \Hom_\Dd(F(c),\colimit_\Ii d_i)$ for all $c\in \Cc$ and $d_i\in \Dd$. This is \itememph{b}.
	
	Now since $F$ is fully faithful, the unit $\id_{\Pp(\Cc)}\Rightarrow\Sing_F|\blank|_F$ is an equivalence on representables. Indeed, the right-hand side sends $c\in \Cc$ to $\Hom_\Dd(\mathop{F}-,F(c))\simeq \Hom_\Cc(-,c)$ by \cref{cor:ExplicitAdjoint} again. Now both sides preserve colimits and every presheaf on $\Cc$ can be written as a colimit of representatives by \cref{lem*:PresheafColimitOfRepresentables}, hence the unit is an equivalence everywhere. By the triangle identities and the fact that $\Sing_F$ is conservative by \itememph{c}, this implies that the counit $|\Sing_F-|_F\Rightarrow \id_\Dd$ is an equivalence as well. This finishes the proof of \itememph{\boxtimes}.
	
	Now to check that \itememph{\boxtimes} is applicable for $\Cc=\Ee/X$ and $\Dd=\Pp(\Ee)/X$. We already argued that $\Pp(\Ee)/X$ is cocomplete. It's easily checked that $\Ee/X\morphism\Pp(\Ee)/X$ is fully faithful since it's induced by the fully faithful Yoneda embedding, so \itememph{a} holds. To check \itememph{c}, let $\alpha\colon F\morphism F'$ be a morphism in $\Pp(\Ee)/X$ such that $\alpha_*\colon \Hom_{\Pp(\Ee/X)}(-,F)\morphism \Hom_{\Pp(\Ee/X)}(-,F')$ is an equivalence on representable presheaves. We must check that $\alpha$ is an equivalence itself. But if $\alpha_*$ is an equivalence on representables, then the Yoneda lemma implies that $\alpha\colon F(e)\morphism F'(e)$ is an equivalence for all $e\in \Ee$ (except those $e\in \Ee$ for which $X(e)=\emptyset$ since these aren't contained in the image of $\Ee/X\morphism \Ee$, but in that case we have $F(e)=\emptyset=F'(e)$ too since $F$ and $F'$ come with a map to $X$), hence $\alpha$ is an equivalence of presheaves.
	
	Finally, we have to check \itememph{b}. Given a representable object $\Hom_\Ee(e,-)\morphism X$ and an arbitrary object $F\morphism X$ of $\Pp(\Ee)/X$, the Yoneda lemma and \cite[Corollary~VIII.6]{HigherCatsII} provide a pullback square
	\begin{equation*}
		\begin{tikzcd}
			\Hom_{\Pp(\Ee)/X}\big(\Hom_\Ee(e,-),F\big)\rar\dar\drar[pullback]& \Hom_{\Pp(\Ee)}\big(\Hom_\Ee(e,-),F\big)\rar[iso] \dar & F(e)\dar\\
			*\rar & \Hom_{\Pp(\Ee)}\big(\Hom_\Ee(e,-),X\big)\rar[iso]& X(e)
		\end{tikzcd}
	\end{equation*}
	Clearly $F(e)$ commutes with colimits in $F$ because colimits in functor categories are computed pointwise (\cref{lem:f^*preservesColimits}). Hence it suffices to check that colimits in $\An$ commute with pullbacks. In other words, if $f\colon K\morphism L$ is any morphism of anima, then $f^*\colon \An/L\morphism \An/K$ preserves colimits. But $\Right(K)\simeq \An/K$ since every morphism to $K$ can be factored into a right anodyne and a right fibration, and likewise for $L$, so we are done since we verified in \cref{lem*:SmoothBaseChange} that $f^*\colon \Right(L)\morphism \Right(K)$ has a right adjoint $f_*$.
\end{proof}



\backmatter\KOMAoption{chapterprefix}{false}
\printbibliography
\end{document}