\documentclass[a4paper, 10pt, oneside, DIV=9, chapterprefix=true, numbers=enddot,bibliography=totoc]{scrbook}
\usepackage{StyleFF}
\usepackage{ShortcutsFF}

\usetikzlibrary{shapes.geometric,patterns}
\DeclareRobustCommand{\Attention}{\tikz[baseline, anchor=base]\node[draw, regular polygon, regular polygon sides=3, rounded corners=2, thick, inner sep=-0.25pt] at (0,0) {\textbf{!}};}


\subject{Lecture Notes for}
\title{The Fargues--Fontaine Curve}
\subtitle{Or: \enquote{The Fundamental Curve of $p$-adic Hodge Theory}}
\author{{\normalsize Lecturer}\\
	Johannes Anschütz}
\date{{\normalsize Notes typed by}\\
	Ferdinand Wagner}
\publishers{Winter Term 2019/20\\
University of Bonn}

%\includeonly{nothingtoseehere}
\begin{document}
\frontmatter
\KOMAoption{chapterprefix}{false}
\maketitle
\noindent This text consists of notes on the lecture Selected Topics in Algebra (The Fargues--Fontaine Curve), taught at the University of
Bonn by Dr.\ Johannes Anschütz in the winter term (Wintersemester) 2019/20.

Some changes and some additions have been made by the author. To distinguish them from the lecture's actual contents, they are labelled with an asterisk. So any \emph{Lemma}* or \emph{Remark}* or \emph{Proof}* that the reader might encounter are wholly the author's responsibility.\\[\thmsep]Please report errors, typos etc.\ through the \emph{Issues} feature of GitHub.


\tableofcontents
\listoftoc{lol}
\setcounter{llecture}{-1}
\include{./Chapters/FFintro}

\mainmatter\KOMAoption{chapterprefix}{true}
\renewcommand{\thedummy}{\thesection.\arabic{dummy}}

\include{./Chapters/FF11to12}


\section{Newton Polygons and Factorizations}
\subsection{The Power Series Case}
\lecture[Newton polygons of polynomials. The Legendre Transform. Newton polygons of power series. Newton polygons in $\IA_\inf$ and untilts of $\Oo_F$.]{2019-11-13}
Let $K$ be a non-archimedean field, $v\colon K\morphism\IR\cup\{\infty\}$ its valuation (written additively). Let $f=a_0+a_1T+\dotsb+a_nT^n\in K[T]$ be a polynomial.
\begin{defi}
	The \defemph{Newton polygon} $\Newt_\poly(f)$ is the largest convex polygon below $\{(i,v(a_i))\}_{i\in\IZ}$, where we put $a_i=0$ for $i\notin\{0,1,\dotsc,n\}$ by convention.
\end{defi}
There is a better description via the \defemph{Legendre transform}. To set this up, we introduce the notations $\ov{\IR}=\IR\cup\{\pm\infty\}$ and $\Ff=\{\phi\colon \ov{\IR}\morphism\ov{\IR}\}$.
\begin{defi}
	We define the \defemph{Legendre transform} $\Ll\colon \Ff\morphism\Ff$ and the \defemph{inverse Legendre transform} $\snake{\Ll}\colon \Ff\morphism\Ff$ via
	\begin{align*}
		\Ll\phi(\lambda)&=\inff_{x\in\IR}\{\phi(x)+\lambda x\}\,\\
		\snake{\Ll}\phi(x)&=\sup_{x\in\IR}\{\phi(\lambda)-\lambda x\}\,.
	\end{align*}
\end{defi}
Note that $\snake{\Ll}\phi=-\Ll(-\phi)$. As a Slogan: \enquote{$\Ll$ and $\snake{\Ll}$ interchange $x$-coordinates and slopes}.
\begin{exm}\label{exm:LegendreOfLinear}
	If $\phi(x)=ax+b$, then one easily verifies
	\begin{equation*}
		\Ll\phi(\lambda)=\begin{cases}
			b & \text{if }\lambda=-a\\
			-\infty & \text{else}
		\end{cases}\,.
	\end{equation*}
	Also note that $\snake{\Ll}\Ll\phi=\phi$ in this case.
\end{exm}
\begin{lem}\label{lem:Legendre}
	Let $\phi,\psi\in\Ff$. Then the following hold.
	\begin{numerate}
		\item The Legendre transform $\Ll\phi$ is always concave, i.e., it satisfies the inequality
		\begin{equation*}
			\Ll\phi(a\lambda+b\mu)\geq a\Ll\phi(\lambda)+b\Ll\phi(\mu)
		\end{equation*}
		for all $a,b\geq 0$ such that $a+b=1$. Similarly $\snake{\Ll}\phi$ is convex.
		\item If $\phi\leq \psi$, then $\Ll\phi\leq \Ll\psi$ and $\snake{\Ll}\phi\leq \snake{\Ll}\psi$.
		\item We have $\snake{\Ll}\Ll\phi\leq \phi\leq \Ll\snake{\Ll}\phi$.
		\item If $\phi$ admits a supporting line at $x$ of slope $\lambda$, i.e., $\phi(y)\geq \phi(x)+\lambda(y-x)$ for all $y$, then $\Ll\phi$ admits a capping line at $-\lambda$ of slope $x$.
		\item $\snake{\Ll}\Ll\phi$ is the largest convex function below $\phi$, and likewise $\Ll\snake{\Ll}\phi$ is the smallest concave function over $\phi$.
		\item $\Ll$ and $\snake{\Ll}$ define inverse bijections $\{\text{convex }\phi\colon \IR\morphism\ov{\IR}\}\lrisomorphism \{\text{concave }\psi\colon \IR\morphism\ov{\IR}\}$.
	\end{numerate}
\end{lem}
\begin{proof}
	Parts \itememph{1} to \itememph{4} are straightforward from the definitions. We only prove \itememph{5} and \itememph{6}. For $a,b\in \IR$ put $\psi_{a,b}(x)=ax+b$ and consider the set $M\coloneqq\left\{(a,b)\st \psi_{a,b}\leq \phi\right\}$. Then $\psi=\sup_M\left\{\psi_{a,b}\right\}$ is the largest convex function below $\phi$. By \itememph{1} and \itememph{3} we get $\snake{\Ll}\Ll\phi\leq \psi$. Moreover, \cref{exm:LegendreOfLinear} and \itememph{2} show 
	\begin{equation*}
		\psi_{a,b}=\snake{\Ll}\Ll\psi_{a,b}\leq \snake{\Ll}\Ll\phi\,,
	\end{equation*}
	hence $\psi\leq \snake{\Ll}\Ll\phi$. This proves that $\snake{\Ll}\Ll\phi$ is the largest convex function below $\phi$. The second part of \itememph{5} is completely analogous.
	
	Part~\itememph{6} is a formal consequence of \itememph{3} and \itememph{5}. We know that $\Ll\colon(\Ff,\leq)\doublelrmorphism (\Ff,\leq)\noloc \snake{\Ll}$ define an adjoint pair of functors. Hence $\Ll$ and $\snake{\Ll}$ induce inverse bijections between the full subcategories on which the unit resp.\ the counit of this adjunction is a natural isomorphism. Now $\left\{\phi\st \snake{\Ll}\Ll\phi=\phi\right\}=\{\phi\text{ convex}\}$ and likewise $\left\{\psi\st \psi=\Ll\snake{\Ll}\psi\right\}=\{\psi\text{ concave}\}$.
\end{proof}
\numpar{Example \smash{\Attention}}
$\Ll$ and $\snake{\Ll}$ preserve piece-wise linear functions. In pictures, this looks roughly as follows.
\begin{center}
	\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
	\begin{scope}[xshift=-6.75cm]
	\draw[-to] (-0.5,0) -- (4,0);
	\draw[-to] (0,-0.5) -- (0,4);
	\fill (3,0.25) circle (0.5ex) node (4) {};
	\fill (1.5,1) circle (0.5ex) node (3) {};
	\fill (0.75,1.75) circle (0.5ex) node (2) {};
	\fill (0.25,2.75) circle (0.5ex) node (1) {};
	\draw[thick] (0.25,2.75) -- (0.75,1.75) node[pos=0.5,right=1.5] {$\lambda_1$} -- (1.5,1) node[pos=0.5,above right=-2] {$\lambda_2$} -- (3,0.25) node[pos=0.5,above=1.5] {$\lambda_3$};
	\draw (0.25,0.75ex) -- (0.25,-0.75ex) node[below] {$x_1$};
	\draw (0.75,0.75ex) -- (0.75,-0.75ex) node[below] {$x_2$};
	\draw (1.5,0.75ex) -- (1.5,-0.75ex) node[below] {$x_3$};
	\draw (3,0.75ex) -- (3,-0.75ex) node[below] {$x_4$};
	\end{scope}
	\begin{scope}[xshift=0.25cm]
	\draw[-to] (-0.5,0) -- (4,0);
	\draw[-to] (0,-0.5) -- (0,4);
	\fill (2,3.25) circle (0.5ex) node (3) {};
	\fill (1,2.5) circle (0.5ex) node (2) {};
	\fill (0.5,1.75) circle (0.5ex) node (1) {};
	\draw[thick] (-0.1875,-0.3125) -- (0.5,1.75) -- (1,2.5) -- (2,3.25) -- (3.5,3.625);
	\draw[dotted] (0.5,1.75) -- (1.25,4);
	\draw[dotted] (-0.5,1.375) -- (1,2.5);
	\draw[dotted] (2,3.25) -- (3,4);
	\draw[dotted] (0.5,1.75) -- (-0.5,0.25);
	\draw[dotted] (1,2.5) -- (2,4);
	\draw[dotted] (2,3.25) -- (-0.5,2.625);
	\draw (0.5,0.75ex) -- (0.5,-0.75ex);
	\node[below] at (0.45,-0.75ex) {$-\lambda_3$};
	\draw (1,0.75ex) -- (1,-0.75ex);
	\node[below] at (1.175,-0.75ex) {$-\lambda_2$};
	\draw (2,0.75ex) -- (2,-0.75ex) node[below] {$-\lambda_1$};
	\node at (0.9,3.75) {$x_4$};
	\node at (1.55,3.75) {$x_3$};
	\node at (-0.25,1.85) {$x_2$};
	\node at (-0.25,2.9) {$x_1$};
	\end{scope}
	\draw[-to,bend left] (-2.5,2.125) to node[pos=0.5,above] {$\Ll$} (-1,2.125);
	\draw[-to,bend left] (-1,1.875) to node[pos=0.5,below] {$\snake{\Ll}$} (-2.5,1.875);
	\end{tikzpicture}
\end{center}

Back to Newton polynoms for polygonials. Let $f\in K[T]$ be as above. As $\Newt_\poly(f)$ is the largest convex function below $\{(i,v(a_i))\}_{i\in \IZ}$, we have
\begin{equation*}
	\Ll\Newt_\poly(f)(r)=\inff_{i\in\IZ}\left\{v(a_i)+ri\right\}\eqqcolon v_r(f)\,.
\end{equation*}
The expression on the right-hand side has a nice geometric interpretation for $r\in v(\ov{K})$. In this case we have
\begin{equation*}
	v_r(f)\coloneqq \inff_{i\in\IZ}\left\{v(a_i)+ri\right\}=\inff\left\{v(f(x))\st x\in\ov{K}\text{ and }v(x)=r\right\}\,.
\end{equation*}
Indeed, as $v(a_ix^i)=v(a_i)+ri$, it's clear that \enquote{$\geq $} holds. For the converse, choose $x_0\in\ov{K}$ with $v(x_0)=r$. We want to find a $y\in\ov{K}$ such that $v(y)=0$ and $v(f(x_0y))=v_r(f)$. Let $b\in \ov{K}$ such that $v(b)=-v_r(f)$ and put $b_i=ba_ix_0^i$. Then $v(b_i)\geq 0$. Let $n_0\leq n$ be the largest index such that $v(b_{n_0})=0$. Let $c\in\ov{K}$ such that $v(c)=0=v(b_0-c)$, which exists as $\Oo_{\ov{K}}/\mm_{\ov{K}}$ is an algebraically closed field, hence has at least two non-zero elements. Now let $y\in\ov{K}$ be a solution of $c=b_0+\dotsb+b_{n_0}y^{n_0}$. As $v(b_{n_0})=0$, $y\in\Oo_{\ov{K}}$, and then a simple inspection shows $v(y)=0$. Now it's easy to check that indeed $v(f(x_0y))=v_r(f)$, hence we are done. 
\begin{exc}\label{exc:vrOfProduct}
	For all polynomials $f,g\in K[T]$ and all $r\in\IR$ we have 
	\begin{equation*}
		v_r(fg)=v_r(f)+v_r(g)\,.
	\end{equation*}
\end{exc}
\begin{proof*}
	Let $(a_i)$ and $(b_j)$ be the coefficients of $f$ and $g$, and $(c_k)$ the coefficients of $fg$. Then $c_k=\sum_{i+j=k}a_ib_j$. Hence $v(c_k)+rk\geq \inf\{v(a_i)+ri+v(b_j)+rj\}$ by the strong triangle inequality. This shows \enquote{$\geq$}. 
	
	For the converse, let $s\geq 0$ and $t\geq 0$ be minimal indices such that $v(a_s)+rs=v_r(f)$ and $v(b_t)+rt=v_r(g)$. For all $(i,j)\neq (s,t)$ satisfying $i+j=s+t$, we have 
	\begin{equation*}
		v(a_i)+ri+v(b_j)+rj>v(a_s)+rs+v(b_t)+rt\,,
	\end{equation*}
	hence $v(a_i)+v(b_j)>v(a_s)+v(b_t)$, hence $v(c_{s+t})=v(a_s)+v(b_t)$. This finally proves $v(c_{s+t})+r(s+t)=v_r(f)+v_r(g)$ and we are done.
\end{proof*}
\begin{rem}\label{rem:Ladditive}
	For $f=a_0+a_1T+\dotsb+a_nT^n$ let $\phi_f$ be the piece-wise linear function connecting the $\{(i,v(a_i))\}_{i\in\IZ}$. Then \cref{exc:vrOfProduct} shows $\Ll\phi_{fg}=\Ll\phi_f+\Ll\phi_g$. As a slogan, we \enquote{concatenate the concave piece-wise linear functions to a new one}.
\end{rem}
\begin{defi}
	Let $\phi,\psi\in\Ff$ such that $-\infty\notin \im\phi\cup\im\psi$. Then we define the \defemph{convolution} $\phi*\psi\colon \IR\morphism\ov{\IR}$ as
	\begin{equation*}
		(\phi*\psi)(x)=\inff_{y+z=x}\left\{\phi(y)+\psi(z)\right\}\,.
	\end{equation*}
\end{defi}
\begin{lem}\label{lem:convolution}
	Let $\phi,\psi\in\Ff$ such that $-\infty\notin \im\phi\cup\im\psi$.
	\begin{numerate}
		\item If $\phi$ and $\psi$ are convex, then so is $\phi*\psi$.
		\item We have $\Ll(\phi*\psi)=\Ll\phi+\Ll\psi$.
	\end{numerate}
\end{lem}
\begin{proof*}
	We start with \itememph{1}. Let $x_1,x_2\in\IR$ and $a,b\geq 0$ such that $a+b=1$. We need to show
	\begin{equation*}
		(\phi*\psi)(ax_1+bx_2)\leq a(\phi*\psi)(x_1)+b(\phi*\psi)(x_2)\,.
	\end{equation*}
	Let $y_1,y_2,z_1,z_2\in\IR$ such that $x_1=y_1+z_1$ and $x_2=y_2+z_2$. Put $x=ax_1+bx_2$, $y=ay_1+bz_1$, and $z=ay_2+by_2$. Then $x=y+z$ and 
	\begin{equation*}
		\phi(y)+\psi(z)\leq a(\phi(y_1)+\psi(y_2))+b(\phi(z_1)+\psi(z_2))
	\end{equation*}
	by convexity of $\phi$ and $\psi$. Taking infima shows the required inequality. This shows \itememph{1}. Part~\itememph{2} follows straight from the definitions.
\end{proof*}
\begin{cor}\label{cor:NewtConvolution}
	If $f,g\in K[T]$ are polynomials, then
	\begin{equation*}
		\Newt_\poly(fg)=\Newt_\poly(f)*\Newt_\poly(g)\,.
	\end{equation*}
\end{cor}
\begin{proof}
	Both sides are convex by definition, and agree after applying $\Ll$ (use \cref{rem:Ladditive} and \cref{lem:convolution}), so they are already equal by \cref{lem:Legendre}.
\end{proof}
\begin{exm}\label{exm:NewtConvolution}
	Let's illustrate \cref{cor:NewtConvolution} for $f=T-\alpha$ and $g=T-\beta$:
	\begin{center}
		\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
		\begin{scope}[xshift=-9.5cm]
		\draw[-to] (-0.5,0) -- (2.5,0);
		\draw[-to] (0,-0.5) -- (0,2.5);
		\fill (0,1) circle (0.5ex);
		\fill (0.5,0) circle (0.5ex);
		\draw[thick] (0,1) -- (0.5,0) node[pos=0.5,above right=-2] {$-v(\alpha)$};
		\node at (1.25,2) {$\Newt_\poly(f)$};
		\end{scope}
		\begin{scope}[xshift=-5.5cm]
		\draw[-to] (-0.5,0) -- (2.5,0);
		\draw[-to] (0,-0.5) -- (0,2.5);
		\fill (0,0.4) circle (0.5ex);
		\fill (1.25,0) circle (0.5ex);
		\draw[thick] (0,0.4) -- (1.25,0);
		\node[above] at (0.75,0.25) {$-v(\beta)$};
		\node at (1.25,2) {$\Newt_\poly(g)$};
		\end{scope}
		\begin{scope}[xshift=0cm]
		\draw[-to] (-0.5,0) -- (2.5,0);
		\draw[-to] (0,-0.5) -- (0,2.5);
		\fill (0,1.4) circle (0.5ex);
		\fill (0.5,0.4) circle (0.5ex);
		\fill (1.75,0) circle (0.5ex);
		\draw[thick] (0,1.4) -- (0.5,0.4) node[pos=0.5,above right=-2] {$-v(\alpha)$} -- (1.75,0);
		\node[above] at (1.25,0.25) {$-v(\beta)$};
		\node at (1.25,2) {$\Newt_\poly(fg)$};
		\end{scope}
		\draw[-to,bend left] (-2.5,1) to node[pos=0.5,above=1] {convolution} (-1,1);
		\end{tikzpicture}
	\end{center}
	In particular, if $f\in K[T]$ is a polynomial of degree $n$ and $\alpha_1,\dotsc,\alpha_n\in\ov{K}$ its zeros counted with multiplicity, then induction on $n$ shows that $\Newt_\poly(f)$ has exactly $-v(\alpha_1),\dotsc,-v(\alpha_n)$ as its slopes, with the same multiplicities.
\end{exm}
Now we want to define Newton polygons for power series. So let $f\in \Oo_K\llbracket T\rrbracket$ be a power series, say, $f=\sum_{i=0}^\infty a_iT^i$.
\begin{defi}
	The \defemph{Newton polygon} $\Newt(f)$ is the largest \defemph{decreasing} convex function below $\{(i,v(a_i))\}_{i\in\IZ}$, where $a_i=0$ for $i<0$ by convention. In other words,
	\begin{equation*}
		\Ll\Newt(f)(r)=\begin{cases}
		v_r(f)\coloneqq\inff_{i\in\IZ}\{v(a_i)+ri\} & \text{if }r\geq 0\\
		-\infty & \text{if }r<0
		\end{cases}\,.
	\end{equation*}
\end{defi}
\begin{rem}
	\begin{numerate}
		\item A power series $f$ defines a function on the \enquote{open rigid-analytic unit disc} $\ID=\left\{x\st |x|<1\right\}$. In fact, one can handle general $f\in K\llbracket T\rrbracket$ as functions if one is careful with domains of convergence.
		\item For $f\in\Oo_K[T]$, $\Newt(f)$ omits the positive slopes from $\Newt_\poly(f)$, as these correspond to zeros outside of $\ID$. In particular, $\Newt(f)\neq \Newt_\poly(f)$ in general.
	\end{numerate}
\end{rem}
Similar to the polynomial case in \cref{exm:NewtConvolution}, there is a connection between slopes of the Newton polygon of a power series $f$ and zeros of $f$ (but we won't prove this). 
\begin{thm}[Lazard]\label{thm:Lazard}
	Let $f\in\Oo_K\llbracket T\rrbracket$. Let $\lambda\neq 0$ be a slope of $\Newt(f)$. Then there exists a zero $\alpha\in\roof{\ov{K}}$ of $f$ with $v(\alpha)=-\lambda$. In other words, in $\Oo_{\roof{\ov{K}}}\llbracket T\rrbracket$ the power series $f$ an be factored as $f=(T-\alpha)g$.
\end{thm}
\begin{rem}\label{rem:log}
	\begin{numerate}
		\item Suppose $\Newt(f)$ is eventually constant (this is e.g.\ the case if $K$ is discretely valued), i.e., $f=a\snake{f}$ for $a\in\Oo_K$ and $\snake{f}$ is primitive of some degree $d$. Then the Weierstraß preparation theorem shows $f=aPg$, where $a\in \Oo_K$, $P$ is a monic polynomial of degree $d$, and $g\in\Oo_K\llbracket T\rrbracket^\times$ is a unit.
		\item Suppose $\cha K=0$. Then $\log_p(1-x)=\sum_{i=0}^\infty (-1)^{i-1}x^i/i$ has zeros precisely at $\mu_{p^\infty}(\ov{K})$. Draw the Newton polygon of $\log_p(1-x)$ and prove this!
	\end{numerate}
\end{rem}
\subsection{Newton Polygons in \texorpdfstring{$\IA_\inf$}{Ainf}}
With notation as usual we put $\IA_\inf=W_{\Oo_E}(\Oo_F)$. We want to introduce an analogue of Newton polygons of power series for $\IA_\inf$. As a side note, there is no \enquote{subring of polynomials in $\IA_\inf$}: $\left\{\sum_{i=0}^n[a_i]\pi^i\st a_i\in\Oo_F\right\}$ is not closed under addition. So there's no sensible generalization of Newton polygons of polynomials to $\IA_\inf$.
\begin{defi}\label{def:AinfNewton}
	Let $f=\sum_{i=0}^\infty[a_i]\pi^i\in\IA_\inf$. Then the \defemph{Newton polygon $\Newt(f)$ of $f$} is the largest decreasing convex function below $\{(i,v(a_i))\}_{i\in\IZ}$. In other words,
	\begin{equation*}
		\Ll\Newt(f)(r)=\begin{cases}
		v_r(f)\coloneqq\inff_{i\in\IZ}\{v(a_i)+ri\} & \text{if }r\geq 0\\
		-\infty & \text{if }r<0
		\end{cases}\,.
	\end{equation*}
\end{defi}
\numpar{Lemma \smash{\Attention}}\label{lem:vrValuation}\itshape
For all $r\geq 0$, $v_r\colon \IA_\inf\morphism\IR\cup\{\infty\}$ is a valuation. In particular, for $f,g\in\IA_\inf$ we have
\begin{equation*}
	\Newt(fg)=\Newt(f)*\Newt(g)\,.
\end{equation*}\upshape
\begin{proof*}
	It's clear that $v_r(f)=\infty$ iff $f=0$. We first establish the strong triangle inequality. This is essentially straightforward, but still technical. Define \enquote{twisted Witt polynomials}
	\begin{equation*}
		\snake{S}_n(X_0,\dotsc,X_n,Y_0,\dotsc,Y_n)=S_n\left(X_0^{q^0},\dotsc,X_n^{q^n},Y_0^{q^0},\dotsc,Y_n^{q^n}\right)\,.
	\end{equation*}
	Using the inductive construction of the $S_n$, it's easy to check that $\snake{S}_n$ is homogeneous of degree $q^n$. If $\alpha X_0^{s_0}\dotsm X_n^{s_n}Y_0^{t_0}\dotsm Y_n^{t_n}$ is a monomial of total degree $q^n$, we define its \defemph{weight} as $q^{-n}\sum_{i=0}^ni(s_i+t_i)$. We claim:
	\begin{alphanumerate}
		\item[\itememph{*}] There is a polynomial $T_n$ such that $\snake{S}_n\equiv T_n\mod \pi$, no coefficient of $T_n$ is divisible by $\pi$, and every monomial of $T_n$ has weight $\leq n$.
	\end{alphanumerate}
	Let's first see why \itememph{*} implies the strong triangle inequality for $v_r$. Let $f,g\in \IA_\inf$, say, $f=\sum_{n=0}^\infty [a_n]\pi^n$, $g=\sum_{n=0}^\infty [b_n]\pi^n$, and let $f+g=\sum_{n=0}^\infty[c_n]\pi^n$. Since $\pi=0$ in $\Oo_F$, we have $c_n=T_n(a_0,\dotsc,a_n,b_0,\dotsc,b_n)^{1/q^n}$. Now let $\alpha X_0^{s_0}\dotsm X_n^{s_n}Y_0^{t_0}\dotsm Y_n^{t_n}$ be a monomial of $T_n$. Since this monomial has weight $\leq n$, we have
	\begin{equation*}
		q^{-n}v\big(\alpha a_0^{s_0}\dotsm a_n^{s_n}b_0^{t_0}\dotsm b_n^{t_n}\big)+rn\geq q^{-n}\sum_{i=0}^n\big(s_i(v(a_i)+ri)+t_i(v(b_i)+ri)\big)\,.
	\end{equation*}
	Since the right-hand side is a convex combination of $v(a_i)+ri$ and $v(b_i)+ri$ for $i=0,\dotsc,n$, it is bounded below by the minimal value of these guys. This shows
	\begin{equation*}
		v(c_n)+rn\geq \min_{i=0,\dotsc,n}\left\{v(a_i)+ri,v(b_i)+ri\right\}\,.
	\end{equation*}
	If you think about this a bit, this is enough to prove the strong triangle inequality.
	
	We prove \itememph{*} by induction on $n$. The case $n=0$ is clear. Now assume \itememph{*} holds up to $n-1$. Revisiting the proof of \cref{prop:WittPolynomials}, we see that
	\begin{equation*}
		\snake{S}_n=\pi^{-n}\Bigg(\sum_{i=0}^n\pi^i\left(X_i^{q^n}+Y_i^{q^n}\right)-\sum_{i=0}^{n-1}\pi^i\snake{S}_i^{q^{n-i}}\Bigg)\,.
	\end{equation*}
	Clearly, all monomials of the first sum have weight at most $n$. For the second sum, our key \cref{lem:keyLemma} implies $\snake{S}_i^{q^{n-i}}\equiv T_i^{q^{n-i}}\mod\pi^{n-i+1}$, and multiplying by $\pi^i$, we get a congruence modulo $\pi^{n+1}$, as usual. Moreover, since all monomials of $T_i$ have weight at most $i$, the same is true for $T_i^{q^{n-i}}$. This shows that $T_n$ can be defined in an appropriate way.
	
	It remains to show $v_r(fg)=v_r(f)+v_r(g)$. In his notes, Johannes Anschütz writes that $v_r(fg)\geq v_r(f)+v_r(g)$ is trivial, but I don't quite agree on that one. It's certainly trivial for power series, but multiplication in $\IA_\inf$ is more complicated than that. So here we sketch a proof: introduce \enquote{twisted Witt polynomials} $\snake{P}_n$ as above. An easy induction shows that $\snake{P}_n$ is homogeneous of degree $2q^n$, and moreover, that it can be written as a polynomial in $Z_{i,j}$, where we put $Z_{i,j}=X_iY_j$ (and then this polynomial has degree $q^n$). As above, we introduce a notion of \defemph{weight} of a monomial $\alpha Z_{i_0,j_0}^{s_0}\dotsm Z_{i_t,j_t}^{s_t}$ of total degree $q^n$. It is defined as $q^{-n}\sum_{k=0}^t(i_k+j_k)s_k$. We claim:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}] There is a polynomial $Q_n$ such that $\snake{P}_n\equiv Q_n\mod \pi$, no coefficient of $Q_n$ is divisible by $\pi$, and every monomial of $Q_n$ has weight $\leq n$.
	\end{alphanumerate}
	Claim~\itememph{\boxtimes} can be proved in the exact same way as \itememph{*}. Likewise, we can adapt the above arguments to see that \itememph{\boxtimes} indeed implies $v_r(fg)\geq v_r(f)+v_r(g)$.
	
	To show equality, it suffices to consider the case $r>0$, since it is easy to see that $v_0(f)=\lim_{r\to 0}v_r(f)$, so the $r=0$ case will follow automatically. Let $f=\sum_{n=0}^\infty [a_n]\pi^n$, $g=\sum_{n=0}^\infty [b_n]\pi^n$, and $fg=\sum_{n=0}^\infty[c_n]\pi^n$. Since $r>0$, there are minimal indices $m$, $n$ such that $v(a_m)+rm=v_r(f)$ and $v(b_n)+rn=v_r(g)$. Put $N=m+n$. We will show that $v(c_N)=v(a_m)+v(b_n)$, which will conclude the proof. 
	
	We claim that $(1+\pi \beta)Z_{m,n}^{q^N}$ is a monomial in $Q_N$ for some $\beta\in\Oo_E$. To see this, we use the proof of \cref{prop:WittPolynomials} to get
	\begin{equation*}
		\snake{P}_N=\pi^{-N}\Bigg(\sum_{i=0}^N\pi^iX_i^{q^N}\cdot \sum_{j=0}^N\pi^iY_i^{q^N}-\sum_{i=0}^{N-1}\pi^i\snake{P}_i^{q^{N-i}}\Bigg)\,.
	\end{equation*}
	Clearly, $\pi^NZ_{m,n}^{q^N}$ occurs as a summand if we expand the product of the two sums. So we only need to show that $Z_{m,n}^{q^N}$ doesn't occur, up to multiples of $\pi^{N+1}$, in the right-most sum. For that, note that $Z_{m,n}^{q^N}$ doesn't occur, up to multiples of $\pi^{N-i+1}$, in any $Q_i^{q^{N-i}}$ for $i\leq N-1$. This follows from \itememph{\boxtimes} as $Z_{m,n}^{q^N}$ has weight $N$. But $\snake{P}_i^{q^{N-i}}\equiv Q_i^{q^{N-i}}\mod \pi^{N-i+1}$ by our key \cref{lem:keyLemma}. This does it.
	
	As in the proof of the strong triangle inequality, $c_N=Q_N(a_0,\dotsc,a_N,b_0,\dotsc,b_N)^{1/q^N}$. If $\alpha Z_{i_0,j_0}^{s_0}\dotsm Z_{i_t,j_t}^{s_t}$ is a monomial of $Q_N$ different from $(1+\pi\beta)Z_{m,n}^{q^N}$, then
	\begin{equation*}
		q^{-N}v\big(\alpha (a_{i_0}b_{j_0})^{s_0}\dotsm (a_{i_t}b_{j_t})^{s_t}\big)+rN\geq q^{-N}\sum_{k=0}^ts_k\big((v(a_{i_k})+ri_k)+(v(b_{j_k})+rj_k)\big)\,,
	\end{equation*}
	using that the monomial in question has weight $\leq N$. The sum on the right-hand side is a convex combination of terms $(v(a_{i_k})+ri_k)+(v(b_{j_k})+rj_k)$ for $k=0,\dotsc,t$, each of which is at least $v_r(f)+v_r(g)$. So the right-hand side is $\geq v_r(f)+v_r(g)$. But since $m$ and $n$ are minimal with the property that $v(a_m)+rm=v_r(f)$ and $v(b_n)+rn=v_r(g)$ and since the weight is $\leq N$, some terms will be strictly greater than $v_r(f)+v_r(g)$. Thus, the right-hand side is $>v_r(f)+v_r(g)=v(a_m)+v(b_n)+rN$. In particular, $(1+\pi\beta)(a_mb_n)^{q^N}$ is the unique summand with minimal valuation, proving indeed $v(c_N)=v(a_m)+v(b_n)$.
\end{proof*}
Let now $a=[a_0]-u\pi$ be an element of $\Prim_1$, where $u\in\IA_\inf^\times$ is a unit and $a_0\in\mm_F\setminus \{0\}$. Put $D=\IA_\inf/a\IA_\inf$. Then we have Fontaine's map $\theta\colon \IA_\inf\morphism D$.
\begin{prop}\label{prop:D}
	Suppose we are in the above situation.
	\begin{numerate}
		\item $D$ is $\pi$-complete and $\pi$-torsionfree.
		\item We have $D^\flat\cong \Oo_F$.
		\item The $p\ordinalth$ power map $D\morphism D$, $x\mapsto x^p$ is surjective. In particular, every element of $D$ is the of the form $\theta([x])$ for some $x\in\Oo_F$.
	\end{numerate}
\end{prop}
\begin{proof*}
	Part~\itememph{1} and~\itememph{2} are easy: $a$ is distinguished and $\Oo_F$ is $a_0$-complete as $a\in\mm_F$. By \cref{rem:perfectoid}, $(\IA_\inf,a)$ is thus a perfect prism, hence $\pi$-complete by \cref{lem*:perfectoidComplete}. In particular, $D$ is perfectoid, so \itememph{2} already follows from \cref{rem:perfectoid}\itememph{4}. For \itememph{1}, it remains to show that $D$ is $\pi$-torsionfree. Suppose $x,y\in\IA_\inf$ are such that $\pi x=ay$. Put $x=\sum_{n=0}^\infty[x_n]\pi^n$ and $y=\sum_{n=0}^\infty[y_n]\pi^n$. Then $[a_0y_0]=0$, hence $y_0=0$ as $a_0\in\mm_F\setminus\{0\}$. So $y=\pi y'$, and since $\IA_\inf$ is $\pi$-torsionfree, we obtain $x=ay'$. This shows that $D$ is indeed $\pi$-torsionfree.
	
	Proving that the $p\ordinalth$ power map is surjective is a technical nightmare, but I still want to sketch the proof here. The key to the proof is the following claim:
	\begin{alphanumerate}
		\item[\itememph{*}] For all $x\in\IA_\inf$ with non-zero image in $D$ and all $N\geq 1$ there is an $m\geq 0$ and $y=\sum_{n=0}^\infty[y_n]\pi^n\in\IA_\inf$ such that $v(y_0)< v(a_0)$, $y_n=0$ for all $n=1,\dotsc,N-1$, and
		\begin{equation*}
			x\equiv [a_0]^my\mod a\,.
		\end{equation*}
	\end{alphanumerate}
	We first describe how \itememph{*} implies \itememph{3}. Let $e$ be the ramification index of $\pi$, i.e., $\pi^e\Oo_E=p\Oo_E$, and normalize the valuation $v$ of $\Oo_F$ in such a way that $v(a_0)=1/e$. To show that the image of $x$ in $D$ admits a $p\ordinalth$ root, choose $y$ as above such that $N/e>1+v(a_0)+1/(p-1)$. It suffices to construct a $p\ordinalth$ root of the image of $y$, since $[a_0]$ already admits a $p\ordinalth$ root in $\IA_\inf$. Consider the \enquote{Taylor series expansion of $\sqrt[p]{y}$ around $[y_0]$}, i.e., the series
	\begin{equation*}
		\sum_{n=0}^\infty\prod_{k=0}^n\left(\frac{1-kp}{p}\right)\frac{[y_0]^{(-p(n-1)+1)/p}}{n!}(y-[y_0])^n
	\end{equation*}
	(right now this doesn't make sense at all, but soon it will). We claim that in $D$ this sum can be rewritten into a converging series. It is well-known that $v_p(n!)<n/(p-1)$. Hence the denominator $p^nn!$ divides $\pi^{e(n+n/(p-1))}$ in $\Oo_E$ and thus also in $\IA_\inf$. Likewise, since $v(y_0)<v(a_0)$ and since $[a_0]$ and $\pi$ only differ by a unit in $D$, we see that $[y_0]^{(p(n-1)-1)/p}$ divides $\pi^{n}$ in $D$. Since $y-[y_0]$ is, by assumption on $y$, divisible by $\pi^N$ and $N/e>1+v(a_0)+1/(p-1)$, all terms in the above sum can be interpreted as elements of $D$, and moreover they converge to $0$ in the $\pi$-adic topology. By \itememph{1}, $D$ is $\pi$-complete, so we can indeed represent $\sqrt[p]{y}$ as a convergent series in $D$.
	
	It suffices to show \itememph{*}. If $v(x_0)\geq v(a_0)$, we may subtract a suitable multiple of $a$ to kill the $\pi^0$-term of $x$. In other words, we find $x'$ such that $x\equiv \pi x'\equiv [a_0]u^{-1}x'\mod a$. Now iterate this argument for $u^{-1}x'$. If this doesn't end at some point, the image of $x$ in $D$ is divisible by arbitrary powers of $\pi$, hence $0$ by $\pi$-completeness.
	
	So let's assume $v(x_0)<v(a_0)$. Then it's easy to check that $v(y_0)<v(a_0)$ for all $y\in\IA_\inf$ satisfying $x\equiv y\mod a$. Therefore it suffices to find some $b\in \IA_\inf$ such that $y=x+ab$ satisfies $y_n=0$ for all $n=1,\dotsc,N-1$. We will see that this amounts to a system of polynomial equations for $b_0,\dotsc,b_{N-1}$, which has a solution in $\Oo_F$. To get $y_n=0$, we would like to have
	\begin{equation*}
		S_n\left(x_0^{q^0},\dotsc,x_n^{q^n},Q_0,\dotsc,Q_n\right)=0\quad\text{for all }n=1,\dotsc,N-1\,,
	\end{equation*}
	where $Q_n=Q_n(a_0,\dotsc,a_n,b_0,\dotsc,b_n)$ is defined as in the proof of Lemma~\cref{lem:vrValuation}. If $b_0,\dotsc,b_{n-1}$ are known, then $S_n=0$ uniquely determines $b_n$. Indeed, using the recursive definition of the $S_n$ (compare this to the proof of Lemma~\cref{lem:vrValuation}), we see that $b_n$ only occurs in the summand $Q_n$. And in $Q_n$, $b_n$ only occurs as $a_0^{q^n}b_n^{q^n}$. This shows that $b_n^{q^n}=-\text{some polynomial in $b_0,\dotsc,b_{n-1}$})/a_0^{q^n}$ is uniquely determined, and then $b_n$ is unique since the Frobenius is an automorphism of $\Oo_F$. Moreover, we need to ensure that the value of the polynomial in question is divisible by $a_0^{q^n}$, to get $b_n\in\Oo_F$.
	
	Our goal now is to use the above observation to eliminate $b_1,\dotsc,b_{N-2}$ from the equations. We know that $b_1^q$ is a polynomial (with coefficients not in $\Oo_F$, but in $a_0^{-1}\Oo_F$) in $b_0$. Replacing all subsequent polynomial equations by their $q\ordinalth$ powers, which we may do since the Frobenius is an automorphism, we may substitute each $b_1^q$ by the polynomial in $b_0$ to eliminate $b_1$ everywhere. Now repeat this procedure with $b_2,\dotsc,b_{N-2}$. What we obtain in the end is a huge polynomial $\Psi(b_0)$ with coefficients in $a_0^{-K}\Oo_F$ for some very large $K$. We want to choose $b_0$ to be a root of $\Psi$, to get that $b_{N-1}^{q^M}=-\Psi(b_0)/a_0^{q^M}=0$ (for some very large $M$) is in $\Oo_F$ (actually, it would suffice to choose $b_0$ in such a way that $\Psi(b_0)$ is divisible by a very large power of $a_0$). To show that the roots of $\Psi$ are in $\Oo_F$, we claim that $\Psi$ is \defemph{quasi-monic}, which is to say that all coefficients of $\Psi$ are in $a_0^{-K}\Oo_F$ for some $K$ and its leading coefficient has the form $\epsilon a_0^{-K}$, where $\epsilon\in\Oo_F^\times$ is a unit. For a quasi-monic polynomial, $-K$ as above is called its \defemph{valuation}.
	
	Let $b_n^{q^{M_n}}=-\Psi_n(b_0)$ be the polynomial equation we get by the above procedure.	We claim that all $\Psi_n$ are quasi-monic, and that the valuation of $\Psi_n$ is smaller than that of $\Psi_{n-1}$. This can be seen by induction on $n$. The key part in the inductive step is that $Q_n$ contains the monomial $a_1^{q^n}b_{n-1}^{q^n}$ up to multiples of $\pi$ (this was seen in the proof of Lemma~\cref{lem:vrValuation}). Moreover, any other monomial containing $b_{n-1}^{q^n}$ must also contain $a_0$ since its weight is $\leq n$. Now $a_1^{q^n}\in\Oo_F^\times$ and $a_0\in\mm_F\setminus\{0\}$ by assumption on $a$, so if we group all monomials containing $b_{n-1}^{q^n}$ we get a coefficient in $\Oo_F^\times$. This being the key idea, we omit the details of the induction.
	
	In particular, this shows that $\Psi$ is quasi-monic since it is a the product of $\Psi_{N-1}$ with some power of $a_0$. So $b_0,b_{N-1}\in \Oo_F$ by construction. For $n=1,\dotsc,N-2$ we define $b_n=-\Psi_n(b_0)$. By construction, $(b_0,\dotsc,b_{N-1})$ satisfy all polynomial equations, so it suffices to see $b_n\in\Oo_F$ for all $n=1,\dotsc,N-2$. If, for the sake of contradiction, $n$ is a minimal index such that $0>v(b_n)$, then an induction as above shows $v(b_n)>v(b_{n+1})>\dotsb>v(b_{N-1})$, contradicting $b_{N-1}\in\Oo_F$.
	
	This shows that $D$ admits $p\ordinalth$ roots. To finish the proof of \itememph{3}, we need to show that every $d\in D$ is of the form $\theta([x])$. Using \cref{lem:WAb->A}, it suffices to show that $(-)^\sharp\colon \Oo_F\morphism D$ is surjective. But \itememph{2} together with \cref{prop:(A/I)b} shows $\Oo_F\cong D^\flat\cong \limit_{d\mapsto d^q}D$. Since $D$ admits $p\ordinalth$ roots, it's clear that the right-hand side surjects onto $D$.
\end{proof*}
\begin{cor}\label{cor:D}
	Suppose we are in the above situation.
	\begin{numerate}
		\item $D$ is a complete valuation ring, with well-defined valuation $v\colon D\morphism\IR\cup\{\infty\}$ constructed as follows: for $d=\theta([x])$ we put $v(d)=v_F(x)$, where $v_F$ denotes the valuation of $F$.
		\item The fraction field $C=\Frac(D)$ is algebraically closed.
	\end{numerate}
\end{cor}
\begin{proof}
	We start with \itememph{1}. The first thing to show is that $v$ is well-defined. Suppose $x,y\in \Oo_F$ satisfy $x^\sharp=\theta([x])=\theta([y])=y^\sharp$ (the outer equalities are due to \cref{lem:WAb->A}). Suppose $v_F(x)\geq v_F(y)$, so w.l.o.g.\ $x=yz$. Then $z^\sharp=1$, and it suffices to show $z\in\Oo_F^\times$. Write $z=(z_0,z_1,\dotsc)\in\limit_{d\mapsto d^q}D$, where $z_0=1$. Then each $z_n$ is invertible in $D$, so $z$ is invertible in $D^\flat\cong \Oo_F$.
	
	We proceed to show that $D$ is an integral domain. Assume $de=0$ with $d,e\in D$. Write $d=x^\sharp$ and $e=y^\sharp$. Then $[xy]=az$ for some $z\in \IA_\inf$. But $\Newt([xy])$ is a horizontal line, whereas $\Newt(az)=\Newt(a)*\Newt(z)$ contains $-v(a_0)$ as a slope if $z\neq 0$.
	
	Now it is completely formal to see that $D$ is a valuation ring. The map $v$ clearly extends to $C=\Frac(D)$ via $v(d/e)=v_F(x)-v_F(y)$ if $d=x^\sharp$ and $e=y^\sharp$. This $v$ is multiplicative and satisfies $v(d/e)=\infty$ iff $d/e=0$. Moreover, an element $d/e\in C$ lies in $D$ precisely iff $v(d/e)>0$. Indeed, if $x$ and $y$ are as above, then $v_F(x)\geq v_F(y)$, hence $x=yz$ because $\Oo_F$ is a valuation ring. Then $d/e=z^\sharp\in D$. This already implies the strong triangle inequality: if $d,e\in D$ and $v(d)\geq v(e)$, then $d/e\in D$, hence $v(1+d/e)\geq 0$, hence $v(d+e)=v(e)+v(1+d/e)\geq v(e)$. This proves \itememph{1}.
	
	For \itememph{2}, let $P(T)=T^n+b_{n-1}T^{n-1}+\dotsb+b_0\in D[T]$ be an irreducible polynomial. Since $C$ is a non-archimedean field (which, by our convention, always implies completeness), the Newton polygon $\Newt_\poly(P)$ is a single line. This follows from the classical theory of Newton polygons (e.g.\ \cite[Ch.\:II\:(6.4)]{NEUKIRCH}), or from \cref{exm:NewtConvolution} if one shows that all roots of $P$ have the same valuation, which boils down to the fact that $v$ extends uniquely to any finite extension of $C$. Choose $c_0\in D$ such that $nv(c_0)=v(b_0)$ (such a $c_0$ exists by construction of $v$ and the fact that $\Oo_F$ is integrally closed). Since $\Newt_\poly(P)$ is a single line, $c_0^{-n}P(c_0T)$ is monic and has coefficients in $D$ again, where  Replacing $P$ by $c_0^{-n}P(c_0T)$ we may thus assume $v(b_0)=0$.
	
	Now let $Q_0\in\Oo_F[T]$ be a monic polynomial such that the images of $P$ and $Q_0$ in the polynomial ring $(D/\pi D)[T]\cong (\Oo_F/a_0\Oo_F)[T]$ coincide. Let $y_0\in \Oo_F$ be a zero of $Q_0$. Then $P(T+y_0^\sharp)$ is still irreducible and its constant coefficient is divisible by $\pi$. Now choose $c_1\in D$ such that $nv(c_1)=v(P(y_0^\sharp))\geq v(\pi)$. As above, $P_1(T)=c_1^{-n}P(c_1T+y_0^\sharp)$ is monic, has coefficients in $D$, and its constant coefficient is invertible. Now choose $Q_1$ and $y_1$ as above and iterate the argument. The series $y_0+c_1y_1+\dotsb$ converges to a zero of $P$.
\end{proof}
We can now finally prove \cref{lem:perfectoidOC}, a result that was already announced long ago in the $2\ordinalnd$ lecture.
\begin{proof*}[Proof of \cref{lem:perfectoidOC}]
	Combining \cref{lem:OcflatisOF} and \cref{cor:D} immediately shows this result. More generally, these results show that there is a bijection
	\begin{equation*}
		\{\text{iso.\ classes of }C/E\text{ non-arch.\ alg.\ closed s.th. }\Oo_C^\flat\cong \Oo_F\}\lrisomorphism \Prim_1/\IA_\inf^\times\,.
	\end{equation*}
	If $C/E$ is as on the left-hand side, then $\Oo_C$ is perfectoid by Example~\cref{exm:OCperfectoid}, hence the kernel of $\theta\colon \IA_\inf\morphism\Oo_C$ is generated by an element of $\Prim_1$, which is unique up to $\IA_\inf$. Conversely, if $a\in \Prim_1$ is given, then $D=\IA_\inf/a\IA_\inf$ and $C=\Frac(D)$ define an element of the left-hand side. These maps induce inverse bijections as required.
\end{proof*}
\subsection{The Space \texorpdfstring{$|Y|$}{|Y|} and Factorizations}
\lecture[Elements of $\IA_\inf$ are \enquote{functions on $|Y|$}. An ultra-metric on $|Y|$. Proof of \cref{thm:NewtonSlope}.]{2019-11-20}Let notation be as usual and recall our construction of the Newton polygon for elements of $\IA_\inf$ in \cref{def:AinfNewton}. The goal for today is to prove the following analogue of Lazard's \cref{thm:Lazard}.
\begin{thm}[Fargues--Fontaine]\label{thm:NewtonSlope}
	If $f\in\IA_\inf$ and $\lambda\neq 0$ is a slope of $\Newt(f)$, then there exists an $a\in\Oo_F$ such that $v(a)=-\lambda$ and $f=(\pi-[a])g$ for some $g\in\IA_\inf$.
\end{thm}
Crucial to the proof of \cref{thm:NewtonSlope} will be to interpret $\IA_\inf$ as \enquote{functions on the punctured open unit disc in mixed characteristic}. This leads to the following definition.
\begin{defi}
	We define the space
	\begin{align*}
		|Y|&\coloneqq\left\{\pp\in\Spec\IA_\inf\st\pp\text{ is generated by a primitve element of degree $1$}\right\}\\
		&\mathrel{{\phantom{\coloneqq}}\mathllap{\cong}} \Prim_1/\IA_\inf^\times\\
		&\mathrel{{\phantom{\coloneqq}}\mathllap{\cong}}\{\text{iso.\ classes of }C/E\text{ non-arch.\ alg.\ closed s.th. }\Oo_C^\flat\cong \Oo_F\}
	\end{align*}
\end{defi}
Note that $\mm_F\setminus\{0\}$ surjects onto $|Y|$ via $a\mapsto(\pi-[a])$ (to prove this, we must show that any $[a_0]-u\pi\in\Prim_1$ can be multiplied by a suitable unit to become of the form $\pi-[a]$; the coefficients of such a unit can be constructed inductively), but this need not be a bijection. The notation suggests that $|Y|$ should be thought of the underlying space of some $Y$. This should not be taken too literally, but in some sense this is indeed the case. More about this in \cref{rem:Y}
\begin{nota}
	\begin{numerate}
		\item For $y\in|Y|$, let $\pp_y$ denote the corresponding prime ideal, $C_y$ its residue field which is a non-archimedean algebraically closed extension of $E$ with valuation $v_y\colon C_y\morphism \IR\cup\{\infty\}$, and finally let $\theta_y\colon \IA_\inf\morphism\Oo_{C_y}$  denote Fontaine's map.
		\item For $f\in\IA_\inf$, let $f(y)$ denote the class of $f$ in $C_y$ (think of this as \enquote{$f\in\Global(|Y|,\Oo_{|Y|})$}), and for $y\in |Y|$ we put $v(f(y))=v_y(f)$.
		\item For $y_1,y_2\in|Y|$, we put $d(y_1,y_2)=v_{y_1}(\theta_{y_1}(\xi_{y_2}))$, where $\xi_{y_2}\in\pp_{y_2}$ is a distinguished generator. We will see in \cref{lem:d} below that $d(-,-)$ defines a ultra-metric on $|Y|$. In particular, $d(y,0)=v_y(\pi(y))$ is in some sense the \enquote{distance to the origin}.
	\end{numerate}
\end{nota}
\begin{rem}\label{rem:Y}
	\begin{numerate}
		\item One can define $\Yy=\Spf(\IA_\inf)^\mathrm{ad}\setminus V(\pi[\varpi])$ as an adic space, where $\varpi\in\mm_f\setminus\{0\}$. Then $|Y|\subseteq \Yy$ is the set of classical points, and $\IA_\inf\subseteq \Global(\Yy,\Oo_\Yy)$.
		\item There is a properly discontinuous action $\phi\curvearrowright\Yy$ (think of this as \enquote{$d(\phi(y),0)=\frac1qd(y,0)$}). One can define $\Xx=\Yy/\phi^\IZ$, the \enquote{adic Fargues--Fontaine curve}.
	\end{numerate}
\end{rem}
Now we can reformulate \cref{thm:NewtonSlope} as follows: if $f\in\IA_\inf$ and $\lambda\neq 0$ is a slope of $\Newt(f)$, then there exists a $y\in |Y|$ such that $v(\pi(y))=-\lambda$ and $f(y)=0$. This is the form in which we will prove it below.
\begin{lem}\label{lem:d}
	For $r\geq 0$ let $\aa_r=\left\{x\in\IA_\inf\st v_0(x)\geq r\right\}$. Then for all $y_1,y_2\in|Y|$,
	\begin{equation*}
		d(y_1,y_2)=\sup\left\{r\st \pp_{y_1}+\aa_r=\pp_{y_2}+\aa_r\right\}\,.
	\end{equation*}
	In particular, $d\colon |Y|\times|Y|\morphism \IR\cup\{\infty\}$ is an ultra-metric.\footnote{As a slogan, an ultra-metric is related to a metric in the same way a valuation is related to a (non-archimedean) norm.} That is:
	\begin{numerate}
		\item $d(y_1,y_2)=d(y_2,y_1)$.
		\item For all $y_3\in|Y|$, $d(y_1,y_2)\geq \min\{d(y_1,y_2),d(y_2,y_3)\}$.
		\item $d(y_1,y_2)=\infty$ iff $y_1=y_2$.
	\end{numerate}
\end{lem}
\begin{proof}
	Let $\pp_{y_i}=(\xi_{y_i})$ and write $\xi_{y_1}=\sum_{n=0}^\infty [x_n]\xi_{y_2}^n$. The coefficients $x_n$ exist and can be constructed inductively as follows: since $(-)^\sharp\colon \Oo_F\cong \Oo_{C_{y_2}}^\flat\epimorphism \Oo_{C_{y_2}}$ is surjective by \cref{prop:D}\itememph{3}, the image of $\xi_{y_1}$ in $\Oo_{C_{y_2}}$ has the form $\theta_{y_2}([x_0])$. As $(\xi_{y_2})=\ker\theta_{y_2}$, $\xi'=\xi_{y_1}-[x_0]$ is divisible by $\xi_{y_2}$. Now iterate the argument for $\xi_{y_2}^{-1}\xi'$. Then
	\begin{equation*}
		d(y_2,y_1)=v_{y_2}\big(\theta_{y_2}(\xi_{y_1})\big)=v(x_0)\,.
	\end{equation*}
	Applying $\theta_{y_1}$, we see $0=\theta_{y_1}(\xi_{y_1})=\sum_{n=0}^\infty\theta_{y_1}([x_n])\theta_{y_1}(\xi_{y_2}^n)$, hence
	\begin{equation*}
		\theta_{y_1}([x_0])=\theta_{y_1}(\xi_{y_2})\Bigg(\sum_{n=1}^\infty\theta_{y_1}([x_n])\theta_{y_1}(\xi_{y_2})^{n-1}\Bigg)\,.
	\end{equation*}
	Note that the sum on the left-hand side is convergent in $\Oo_{C_{y_1}}$ because in $\xi_{y_2}=[a_{y_2}]-u_{y_2}\pi$ both $a_{y_2}\in\mm_F$ and $\pi$ have positive valuation. This shows
	\begin{equation*}
		d(y_2,y_1)=v(x_0)=v_{y_1}\big(\theta_{y_1}([x_0])\big)\geq v_{y_1}\big(\theta_{y_1}(\xi_{y_2})\big)=d(y_1,y_2)\,,
	\end{equation*}
	with equality iff $v_{y_1}(\theta_{y_1}([x_1]))=0$, which is fulfilled iff $x_1\in\Oo_F^\times$. But by symmetry we also get $d(y_1,y_2)\geq d(y_2,y_1)$, hence equality must hold.
	
	In particular $x_1\in\Oo_F^\times$ is indeed true. Thus, $\xi_{y_1}=[x_0]+u\xi_{y_2}$ for some unit $u\in \IA_\inf^\times$. This shows $\pp_{y_1}+\aa_{v(x_0)}=\pp_{y_2}+\aa_{v(x_0)}$. Therefore
	\begin{equation*}
		d(y_1,y_2)\leq \sup\left\{r\st \pp_{y_1}+\aa_r=\pp_{y_2}+\aa_r\right\}\,.
	\end{equation*}
	It remains to show the converse inequality. Let $r\geq 0$ such that $\pp_{y_1}+\aa_r=\pp_{y_2}+\aa_r$. Applying $\theta_{y_2}$, we see the ideal $\theta_{y_2}(\xi_{y_1})\Oo_{C_{y_2}}=\theta_{y_2}([x_0])\Oo_{C_{y_2}}$ is continued in $\left\{c\in\Oo_{C_{y_2}}\st v_{y_2}(c)\geq r\right\}$. Thus $v(x_0)=v_{y_2}(\theta_{y_2}([x_0]))\geq r$. This shows $d(y_1,y_2)\geq r$, as required.
	
	Properties \itememph{1} and \itememph{2} are now clear. For \itememph{3}, we observe that $\Oo_{C_{y_1}}\cong \IA_\inf/\pp_{y_1}$ is complete in its valuative topology, which is the topology induced by the images of the $\aa_r$. Thus, $\pp_{y_1}=\bigcap_{r\geq 0}(\pp_{y_1}+\aa_r)$. The same is true for $\pp_{y_2}$. Now $\dim(y_1,y_2)=\infty$ implies $\bigcap_{r\geq 0}(\pp_{y_1}+\aa_r)=\bigcap_{r\geq 0}(\pp_{y_2}+\aa_r)$. Therefore $\pp_{y_1}=\pp_{y_2}$, as required.
\end{proof}
\begin{defi}
	For $r>0$ let $|Y_r|=\left\{y\in|Y|\st d(y,0)=r\right\}$ denote the \defemph{\enquote{circle of radius $r$}}.
\end{defi}

\numpar{Proposition \smash{\Attention}}\label{prop:YrComplete}
\itshape For $r>0$, the space $|Y_r|$ is complete with respect to the ultra-metric $d$.\upshape
\begin{proof}
	Let $(y_n)_{n\in\IN}$ be a Cauchy sequence in $|Y_r|$. We need to show that $(y_n)_{n\in\IN}$ converges. To this end we claim:
	\begin{alphanumerate}
		\item[\itememph{*}] For all $s>0$ the sequence $(\pp_{y_n}+\aa_s)_{n\in\IN}$ of ideals is constant for $n\gge 0$.
	\end{alphanumerate}
	Indeed, there exists a $n_0$ such that $d(y_n,y_m)>s$ for all $n,m\geq n_0$. By \cref{lem:d} this implies $\pp_{y_n}+\aa_{s}=\pp_{y_m}+\aa_{s}$ and \itememph{*} is proven.
	
	Set $I_s=(\pp_{y_n}+\aa_s)/\aa_s\subseteq \IA_\inf/\aa_s$, where $n\gge 0$ so that the eventual constant value is reached. Put $I=\lim_{s\geq 0}I_s$. This is an ideal in $\lim_{s\geq 0}\IA_\inf/\aa_s\cong \IA_\inf$ (here we use that $\IA_\inf$ is $v_0$-complete; to prove this, you can use the first part of the proof of \cref{lem*:nonTrivial}). Then $I_s=(I+\aa_s)/\aa_s$. We claim:
	\begin{alphanumerate}
		\item[\itememph{\boxtimes}] The ideal $I$ is a prime ideal generated by a primitive element of degree $1$, and $(\pp_{y_n})_{n\in\IN}$ converges to $I$ (and then automatically $I\in |Y_r|$; indeed, if the sequence is to converge in $|Y|$ at all, then the limit will be in $|Y_r|$ since this is  a closed subspace).
	\end{alphanumerate}
	To prove this, fix $s>r$ and $n\gge 0$ such that $\pp_{y_n}+\aa_s=I+\aa_s$. Writing $\pp_{y_n}=(\xi_{y_n})$, we see that there exists $x\in\aa_s$ such that $a\coloneqq \xi_{y_n}+x$ is an element of $I$. Then $a\in\Prim_1$. Indeed, writing $\xi_{y_n}=[\xi_0]+[\xi_1]\pi+\dotsb$ and $x=[x_0]+[x_1]\pi+\dotsb$, we get $v(\xi_0)=r$ and $v(\xi_1)=0$ because $\xi_{y_n}$ is a distinguished generator of $\pp_{y_n}\in|Y_r|$, and $v(x_0),v(x_1)\geq s> r$ because $x\in\aa_s$. Then using the explicit descriptions for the first two coefficients of $a$ one easily confirms $a\in\Prim_1$.
	
	We claim that $a$ generates $I$. Clearly $(a)\subseteq I$, so assume this inclusion is not an equality. Since $\IA_\inf/(a)$ is a valuation ring by \cref{cor:D}\itememph{1}, there exists $r_0>0$ such that $(a)+\aa_{r_0}\subseteq I$. Let $t>\max\{r_0,s\}$ and choose $m$ such that $I+\aa_t=\pp_{y_m}+\aa_t$. But since $\aa_{r_0}\subseteq I\subseteq \pp_{y_m}+\aa_t$ we get $r_0\geq t$ (after applying $\theta_{y_m}$), a contradiction!
	
	Now that we know $I\in|Y|$, it's clear that $(\pp_{y_n})_{n\in\IN}$ converges to $I$ as $n\to \infty$, because $\pp_{y_n}+\aa_s=I+\aa_s$ for all $s>0$ and $n\gge 0$. This proves \itememph{\boxtimes} and we are done.
\end{proof}
\begin{proof}[Sketch of a proof of \cref{thm:NewtonSlope}]
	\emph{Step~1.} We reduce to the case where $f\in\IA_\inf$ is primitive of some degree $d$. So assume the assertion is proved in this case and write $f=\sum_{i=0}^\infty [x_i]\pi^i$, $f_n=\sum_{i=0}^n[x_i]\pi^i$. Each $f_n$ is primitive of some degree up to multiplying by a Teichmüller element, so the theorem holds for the $f_n$. Choose $n_0$ such that for all $n\geq n_0$, $\lambda$ occurs as a slope in $\Newt(f_n)$ with the same multiplicity it does in $\Newt(f)$. Let $Y_n=\left\{y\in|Y|\st f(y)=0\text{ and }d(y,0)=-\lambda\right\}$. It suffices to show that we can find a Cauchy sequence $(y_n)_{n\in\IN}$ such that $y_n\in Y_n$. Indeed, by Proposition~\cref{prop:YrComplete}, this sequence converges to a limit $y\in |Y_{-\lambda}|$. We claim that $f(y)=0$. To see this, it suffices to show $v_y(f)\geq r$ for all $r>0$. Choose $N$ such that $-\lambda N>r$ and $N'$ such that $d(y_n,y)>r$ for all $n\geq N'$. Now if $n\geq\max\{N,N'\}$ we have $v_{y_n}(f)\geq (n+1)v_y(\pi)=-\lambda(n+1)>r$ since $f_n(y_n)=0$ and $f-f_n$ is divisible by $\pi^{n+1}$. Hence $f\in\pp_{y_n}+\aa_r$. But $d(y_n,y)>r$ implies $\pp_{y_n}+\aa_r=\pp_y+\aa_r$ by \cref{lem:d}, hence also $v_y(f)\geq r$.
	
	So it remains to construct the Cauchy sequence. We will only hint on how to do that. Let $m<n$ be very large and let $y_n$ be a zero of $f_n$. We wish to find a zero $y_m$ of $f_m$ that is close to $y_n$. Using the theorem repeatedly on $f_m$, we can factor it as $f_m=\xi_1\dotsm\xi_\ell\cdot [a] u$, where $\xi_1,,\dots,\xi_\ell$ are distinguished elements corresponding to the roots of $f_m$ inside $|Y|$, $a\in\Oo_F$ is some element, and $u\in\IA_\inf^\times$ is a unit. Clearly $v_{y_n}(u)=0$ and $v_{y_n}([a])=v(a)\leq v_0(f_m)$. Let $x_i\in|Y|$ be the zero corresponding to $\xi_i$. There are only a bounded number, say at most $N$, of $x_i$ with $d(x_i,0)>-\lambda$, since these correspond to smaller slopes of $\Newt(f)$, and the strong triangle inequality gives $d(x_i,y_n)=-\lambda$ in this case. Similarly, there are at most $M$ indices such that $d(x_i,0)=-\lambda$ (these are the interesting ones). All the rest satisfies $d(x_i,0)<-\lambda$, hence $d(x_i,y_n)\leq -\lambda'$ by the strong triangle inequality, where $\lambda'>\lambda$ is the next slope after $\lambda$ in $\Newt(f)$. Thus,
	\begin{align*}
		v_{y_n}(f_m)&=\sum_{i=0}^\ell v_{y_n}(\xi_i)+v_{y_n}([a]u)=\sum_{i=0}^\ell d(x_i,y_n)+v_{y_n}([a]u)\\
		&\leq N\lambda+\sum_{d(x_i,0)=-\lambda}d(x_i,y_n)+(\ell-M-N)\lambda'+v_0(f)\,.
	\end{align*}
	However, $v_{y_n}(f_m)\geq (m+1)v_{y_n}(\pi)=-\lambda(m+1)$ since $f_n(y_n)=0$ and $f_n-f_m$ is divisible by $\pi^{m+1}$. This shows that $\sum_{d(x_i,0)=-\lambda}d(x_i,y_n)$ must be quite large. But these are at most $M$ summands, so we find a summand such that $d(x_i,y_n)$ is pretty large. Now take $y_m=x_i$. Up to some technical stuff we will omit, this allows us to construct the desired Cauchy sequence.
	
	\emph{Step~2.} Having done the reduction to $f\in\Prim_d$ for some $d$, we may moreover assume that $\lambda$ is the maximal slope of $\Newt(f)$ (i.e., the least steep, since all slopes are negative), by factorizing $f$ and using induction. We claim that there exists a sequence $(y_n)_{n\in\IN}$ in $|Y|$ satisfying
	\begin{alphanumerate}
		\item $v_{y_n}(f)\geq -\lambda(d+n)$,
		\item $d(y_n,y_{n+1})\geq -\lambda(d+n)/d$, and
		\item $d(y_n,0)=-\lambda$ for all $n\in\IN$.
	\end{alphanumerate}
	This will immediately imply the theorem, since \itememph{b} and \itememph{c} show that $(y_n)_{n\in\IN}$ is a Cauchy sequence in $|Y_{\-\lambda}|$, hence convergent by Proposition~\cref{prop:YrComplete}, and \itememph{a} ensures that the limit $y$ is a zero of $f$ by a similar argument as above. We will construct this sequence inductively.
	
	Write $f= \sum_{n=0}^\infty[x_n]\pi^n$, where $x_d\in\Oo_F^\times$. Let $z\in\Oo_F$ be a zero of $\sum_{i=0}^dx_iT^i\in\Oo_F[T]$ such that $v(z)=-\lambda$, using that $F$ is non-archimedean algebraically closed (and for $v(z)=-\lambda$ we use the classical Newton polygon theory, as in \cref{exm:NewtConvolution}). As $\lambda <0$ is the maximal slope, we have $v(x_i)\geq \lambda(d-i)$ for all $i=0,\dotsc,d$. Thus $x_iz^i=w_iz^d$ for some $w_i\in\Oo_F$. Now put $\pp_{y_1}=(\pi-[z])$. Clearly $y_1$ satisfies \itememph{c}. Moreover,
	\begin{equation*}
		f(y_1)=\theta_{y_1}(f)=\sum_{i=0}^d\theta_{y_1}([x_iz^i])+\pi^{d+1}\sum_{i=d+1}^\infty\theta_{y_1}([x_i])\pi^{i-(d+1)}\,.
	\end{equation*}
	To show \itememph{a} for $y_1$, it suffices to check that the first sum is divisible by $\pi^{d+1}$. As $x_iz^i=w_iz^d$ and $\pi=[z]$ in $\Oo_{C_{y_1}}$, we get
	\begin{equation*}
		\sum_{i=0}^d\theta_{y_1}([x_iz^i])=\pi^d\sum_{i=0}^d\theta_{y_1}([w_i])\,.
	\end{equation*}
	By construction of $z$ and the $w_i$ we have $\sum_{i=0}^dw_i=0$. Hence $\sum_{i=0}^d[w_i]\in\pi\IA_\inf$, whence we conclude that \itememph{a} holds for $y_1$. Since we were cut short by a sudden evaluation of the lecture, we will finish the induction next time \dotso
	
	\lecture[Finish the proof of \cref{thm:NewtonSlope}. An amusing exercise. The rings $B^b$ and $B_I$. Definition of the Fargues--Fontaine curve. Newton polygons in $B_I$.]{2019-11-27}\dotso that is, right now. Assume $y_n$ has been constructed. As in the proof of \cref{lem:d}, we can write $f=\sum_{i=0}^\infty [a_i]\xi_{y_n}^i$ with $a_i\in\Oo_F$. Let $z\in F$ be a zero of $\sum_{i=0}^da_iT^i\in\Oo_F[T]$ of maximal valuation. We claim $z\in\Oo_F$. To see this, it suffices to check $a_d\in\Oo_F^\times$, i.e., that $a_d$ maps to a unit in $k=\Oo_F/\mm_F$. Consider $\IA_\inf\morphism W_{\Oo_E}(k)$, where $k=\Oo_F/\mm_F$. Since we can choose $\xi_{y_n}$ to be of the form $\pi-[\varpi]$ with $\varpi\in \mm_F$, its image in $W_{\Oo_E}(k)$ coincides with the image of $\pi$. Thus, reducing $f=\sum_{i=0}^\infty [a_i]\xi_{y_n}^i$ modulo $\mm_F$ shows $a_d\equiv x_d\mod \mm_F$, so $a_d\in\Oo_F^\times$ is indeed a unit. Now we claim that $\pp_{y_{n+1}}=(\xi_{y_n}-[z])$ works.
	
	First of all, since $z$ has maximal valuation among the $d$ zeros of $\sum_{i=0}^da_iT^i$, we get $v(z)\geq v(a_0)/d=v_{y_n}(f)/d\geq -\lambda(d+n)/d$. In particular, $v(z)>-\lambda$, so by the explicit descriptions of $S_0$ and $S_1$ it's easy to check that $\xi_{y_n}-[z_{n+1}]$ is primitive of degree $1$, hence $y_{n+1}\in|Y|$. Moreover, $d(y_n,y_{n+1})=v_{y_n}(-[z])=v(z)\geq -\lambda(d+n)/d$, as required. By the strong triangle inequality this also implies $d(y_{n+1},0)$, so \itememph{b} and \itememph{c} hold. It remains to check \itememph{a}. Since $v(z)$ is maximal among the zeros of $\sum_{i=0}^da_iT^i$, $-v(z)$ is the minimal (i.e., steepest) slope in the Newton polygon of that polynomial. In other words, $v(a_i)\geq v(a_0)-iv(z)$. Thus we may write $a_iz^i=a_0b_i$. Calculating in a similar way as above, we obtain
	\begin{equation*}
		f(y_{n+1})=\theta_{y_{n+1}}(f)=\theta_{y_{n+1}}([a_0])\sum_{i=0}^d\theta_{y_{n+1}}([b_i])+\xi_{y_n}^{d+1}\sum_{i=d+1}^\infty \theta_{y_{n+1}}([a_i])\xi_{y_n}^{i-(d+1)}\,.
	\end{equation*}
	By construction we have $\sum_{i=0}^db_i=0$ (or $a_0=0$, but in this case $f(y_n)=0$ and we are already done), hence $\sum_{i=0}^d[b_i]\in\pi\IA_\inf$. Thus, the first term has valuation at least $v(a_0)+v_{y_{n+1}}(\pi)=v(a_0)+d(y_{n+1},0)\geq -\lambda (d+n+1)$. The second term has valuation at least $(d+1)v_{y_{n+1}}(\xi_{y_n})=(d+1)d(y_n,y_{n+1})\geq -\lambda(d+1)(d+n)/d>-\lambda(d+n+1)$. This shows
	\begin{equation*}
		v_{y_{n+1}}(f)\geq -\lambda(d+n+1)\,,
	\end{equation*}
	hence \itememph{a} holds and the induction is complete.
\end{proof}
\begin{exc}
	We have seen that there is a surjection $\mm_F\setminus\{0\}\epimorphism |Y|$ sending $a$ to $(\pi-[a])$, but this doesn't tell much. The goal of this exercise is to work out a better description in the special case $E=\IQ_p$.
	\begin{numerate}
		\item Let $\epsilon\in (1+\mm_F)\setminus\{1\}$ and put
		\begin{equation*}
			u_\epsilon=\frac{[\epsilon]-1}{[\epsilon^{1/p}]-1}=1+[\epsilon^{1/p}]+\dotsb+[\epsilon^{(p-1)/p}]\,.
		\end{equation*}
		Show that $u_\epsilon$ is primitive of degree $1$!
		\item Show that $(1+\mm_F)\setminus\{1\}\epimorphism |Y|$ given by $\epsilon\mapsto (u_\epsilon)$ is surjective!	{\footnotesize(\emph{Hint:} If $C/\IQ_p$ is non-archimedean algebraically closed  together with an isomorphism $\iota\colon \Oo_C^\flat\isomorphism \Oo_F$, and if $\epsilon=(1,\zeta_p,\dotsc)$ is an element of $\Oo_C^\flat\cong \Oo_F$ where $\zeta_p\neq 1$ is a $p\ordinalth$ root of unity, show that the kernel of $\theta\colon \IA_\inf\morphism \Oo_C$ is generated by $u_\epsilon$, using that for $a,b\in\Prim_1$ we have $a\in(b)$ iff $(a)=(b)$.)}
		\item Let $\IZ_p^\times$ act on $(1+\mm_F)\setminus\{1\}$ via exponentiation, i.e., as $(a,\epsilon)\mapsto \epsilon^a=\sum_{i=0}^\infty \binom{a}{i}(\epsilon-1)^i$. Show that
		\begin{equation*}
			|Y|\cong \big((1+\mm_F)\setminus\{1\}\big)/\IZ_p^\times\,!
		\end{equation*}
		That is, show if $(u_\epsilon)=(u_{\epsilon'})$, then $\epsilon'=\epsilon^a$ for some $a\in \IZ_p^\times$! {(\footnotesize\emph{Hint:} Let $C=\IA_\inf/(u_\epsilon)\big[\frac 1p\big]$. Then $\epsilon\in\Oo_F\cong \Oo_C^\flat$ is a generator of $T_pC^\times=\left\{a=(a_0,a_1,\dotsc)\in\Oo_C^\flat\st a_0=1\right\}$. If $(u_\epsilon)=(u_{\epsilon'})$, show $\epsilon'\in T_pC^\times$.)} 
	\end{numerate}
	 A similar description can be given for arbitrary $E$  actually, but the general case needs Lubin--Tate group laws.
\end{exc}

\section{The Ring \texorpdfstring{$B$}{B}}
As usual, let $p$ be a prime, $E/\IQ_p$ a finite extension with uniformizer $\pi\in\Oo_E$ and residue field $\IF_q=\Oo_E/\pi \Oo_E$, and $F/\IF_q$ an algebraically closed non-archimedean field extension (i.e., $F$ is complete with respect to a non-archimedean valuation $v\colon F\morphism \IR\cup\{\infty\}$).

To warm up for the construction of $B$, we first define its \enquote{bounded version} $B^b$ as follows: for $\varpi\in\mm_F\setminus\{0\}$ we put
\begin{equation*}
	B^b=\IA_\inf\big[\textstyle\frac{1}{\pi},\frac{1}{[\varpi]}\big]\displaystyle=\left\{\sum_{i\gge -\infty}^\infty [x_i]\pi^i\st x_i=0\text{ for }i\lle 0\text{, }\inff_{i\in\IZ}v(x_i)>-\infty\right\}\,.
\end{equation*}
Here we allow the notation $[x]$ also for elements $x\in F$ that need not be in $\Oo_F$. This works as follows: for sufficiently large $n$, we have $\varpi^nx\in\Oo_F$. Then we put $[x]=[\varpi^nx]/[\varpi]^n$, which is indeed an element of $B^b$. And since the Teichmüller lift $[-]$ is multiplicative, it's clear that $[x]$ is independent of the choice of $n$, thus well-defined. Also $B^b$ is clearly independent of the choice of $\varpi$.

Recall the valuations $v_r\colon \IA_\inf\morphism\IR\cup\{\infty\}$ from Lemma~\cref{lem:vrValuation}. Then $v_r$ and the construction of the Newton polygon can be extended to $B^b$; $v_r$ can now attain negative values, and the Newton polygon of an element $f\in \Newt(f)$ need not be contained in the first quadrant $[0,\infty)\times [0,\infty)\subseteq \IR^2$, but in $[x,\infty)\times[y,\infty)$ for some $x,y\in \IR$.
\begin{defi}
	Let $I\subseteq (0,\infty)$ be an intervall. We define the \defemph{ring $B_I$} to be the completion of $B^b$ with respect to the family of valuations $\{v_r\}_{r\in I}$.
\end{defi}
The intuition behind this is that \enquote{$B_I=\Global(|Y_I|,\Oo_{|Y|})$}, where $|Y_I|$ denotes the \enquote{annulus} $\left\{y\in |Y|\st d(y,0)\in I\right\}$ that is depicted below.
\begin{center}
	\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
	\fill[pattern=north west lines,even odd rule] (0,0) circle (1.5) (0,0) circle (0.85);
	\draw (0,0) circle (1.5);
	\draw (0,0) circle (0.85);
	\fill (0,0) circle (0.5ex) node[below=1] {$r=\infty$};
	\draw (0,0) circle (2);
	\node[below right=-1] at (1.414,-1.414) {$r=0$};
	\node [below right] (Y) at (2,2) {$|Y|$};
	\node [below left] (YI) at (-2,2) {$|Y_I|$};
	\draw[-to, shorten >=0.5ex] (YI) -- (147.5:1.5);
	\draw[-to, shorten >=0.5ex] (Y) -- (32.5:2);
	\end{tikzpicture}
\end{center}
\begin{rem}
	If $R$ is a topological ring such that $0$ has a fundamental system $\Ff$ of neighbourhoods which are open subgroups, then
	\begin{equation*}
		\roof{R}=\limit_{U\in\Ff}R/U
	\end{equation*}
	is the completion of $R$. Here $R/U$ is a priori only an abelian group since $U$ need not be an ideal. However, by continuity of multiplication in $R$, the completion $\roof{R}$ becomes a ring again in a canonical way.
	
	For $B_I$ the situation is a bit different, since there is no single topology on $B^b$, but one for every valuation $v_r$ (and in fact these are incompatible for different values of $r$).  In this case we take the family $\Ff=\left\{\bigcap_{i=1}^nv_{r_i}^{-1}[m,\infty)\st m,n\in\IN\text{ and }r_i\in I\right\}$ and then define
	\begin{equation*}
		B_I=\limit_{U\in \Ff}B^b/U
	\end{equation*}
	as above. In the case where $I=[a,b]$ is compact, this is indeed the \enquote{smallest} ring in which all sequences that are Cauchy with respect to every $r\in I$ are convergent. Indeed, every $r\in I$ can be written as $r=\lambda a+(1-\lambda)b$ for $0\leq \lambda\leq 1$, and if $v_a(f),v_b(f)\geq m$, then also $v_r(f)\geq \lambda m+(1-\lambda)m=m$. For non-compact $I$, the situation is not that easy, but at least the above construction shows
	\begin{equation*}
		B_I=\limit_{J\subseteq I}B_J\,,
	\end{equation*}
	where the limit is taken over all compact subintervalls of $J\subseteq I$. In particular, this applies to the most important special case $I=(0,\infty)$.
\end{rem}
\begin{defi}
	The \defemph{ring $B$} is defined as $B=B_{(0,\infty)}$.
\end{defi}
So $B$ can be viewed as the \enquote{ring of global sections of $\Oo_{|Y|}$}. Note that the Frobenius $\phi\curvearrowright B^b$ extends, by continuity, to an automorphism of $B$. More generally, $\phi$ induces an isomorphism $\phi\colon B_I\isomorphism B_{qI}$ for $I\subseteq (0,\infty)$. For every $d\in\IZ$, let $B^{\phi=\pi^d}$ be the eigenspace of $\phi$ with respect to the eigenvalue $\pi^d$.
\numpar{Definition~\smash{\Attention}}\label{def:FFC}
The \defemph{schematic Fargues--Fontaine curve} (with respect to $E$ and $F$) is the scheme
\begin{equation*}
	X=X_\FFC\coloneqq \Proj\Bigg(\bigoplus_{d\geq 0}B^{\phi=\pi^d}\Bigg)\,.
\end{equation*}
\begin{rem}
	As already remarked in \cref{rem:Y}, there is an adic analogue of the Fargues--Fontaine curve: put $\Yy=\Spf(\IA_\inf)^\mathrm{ad}\setminus V(\pi[\varpi])$ and let $\Xx=\Yy/\phi^\IZ$. Then $B\cong \Global(\Yy,\Oo_\Yy)$.
	\begin{center}
		\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
		\draw[-to] (0,0) -- (3.5,0) node[below] {$[\varpi]$};
		\draw[-to] (0,0) -- (0,3.5) node[left] {$\pi$};
		\draw[->, shift={(0,0)}] (35:1.95cm) arc (35:55:1.95cm) node[pos=0.5,above right] {$\phi$};
		\draw[rotate around={-45:(0.5,2.5)}, shift={(0.675,2.5)},rounded corners=12.5, thick] (-3ex,-3ex) rectangle (2.5cm+3ex,3ex);
		\node at (0.6,2.4) {$\Yy$};
		\end{tikzpicture}
	\end{center}
	One can show that $\pi^{-1}\colon \phi^*\Oo_\Yy\isomorphism \Oo_\Yy$ defines the descent datum for a line bundle $\Oo(1)$ on $\Xx$. Moreover, one has
	\begin{equation*}
		H^0\big(\Xx,\Oo(1)^{\otimes d}\big)\cong B^{(\pi^{-1}\phi)^d=1}=B^{\phi=\pi^d}\,.
	\end{equation*}
\end{rem}
The goal of the next few lectures is to understand the scheme $X_\FFC$, and in particular the rings $B$ and $B^b$. We start with a lemma that essentially says that the eigenspaces of $\phi$ on $B^b$, i.e., before completion, are rather boring.
\begin{lem}\label{lem:BbEigenspaces}
	For $d\in\IZ$ let $(B^b)^{\phi=\pi^d}\subseteq B^b$ be the eigenspace of $\phi$ with respect to the eigenvalue $\pi^d$. Then
	\begin{equation*}
		(B^b)^{\phi=\pi^d}=\begin{cases}
			E & \text{if }d=0\\
			0 & \text{else}
		\end{cases}\,.
	\end{equation*}
\end{lem}
\begin{proof}
	For $d=0$, let $f=\sum_{i\gge -\infty}^\infty [x_i]\pi^i\in B^b$. If $f$ is fixed under $\phi$, then $\phi(x_i)=x_i$ for all $i$, hence $x_i\in\IF_q\subseteq \Oo_F$. This shows $f\in W_{\Oo_E}(\IF_q)\big[\frac 1\pi\big]\cong E$. The converse can be shown in the same way.
	Now let $d\neq 0$. If $f\in (B^b)^{\phi=\pi^d}$ and $x\in \IR$, then 
	\begin{equation*}
		q\Newt(f)(x)=\Newt(\phi(f))(x)=\Newt(\pi^d f)(x)=\Newt (f)(x-d)\,.
	\end{equation*}
	Iterating gives $q^n\Newt(f)(x)=\Newt(f)(x-dn)$ for all $n\geq 1$. For $d>0$, we have $\Newt(f)(x-dn)=+\infty$ for $n\gge 0$, hence already $\Newt(f)(x)=+\infty$. This implies $f=0$. For $d<0$ pick $x_0\gge 0$ with $\Newt(f)(x_0)=+\infty$. Since $\Newt(f)$ is decreasing, for all $x\in\IR$ there exists an $n$ such that $\Newt(f)\geq \Newt(x_0-nd)=q^n\Newt(f)(x_0)=+\infty$. Thus $f=0$ follows as before. 
\end{proof}
\begin{lem}\label{lem:convergeInB}
	Let $(x_n)_{n\in\IZ}$ be a sequence in $F$ such that $\lim_{|n|\to\infty}v(x_n)+rn=\infty$ for all $r\in(0,\infty)$. Then $\sum_{n\in\IZ}[x_n]\pi^n$ converges in $B$.
\end{lem}
\begin{proof}
	It suffices to show that $v_r([x_n]\pi^n)\to\infty$ as $|n|\to\infty$ for all $r\in(0,\infty)$. But $v_r([x_n]\pi^n)=v(x_n)+rn$, so this holds by assumption.
\end{proof}
\begin{rem}\label{lem:convergenceInB}
	\begin{numerate}
		\item For all $a\in \mm_F$, the series $f_a\coloneqq \sum_{i\in\IZ}[a^{q^{-i}}]\pi^i$ coverges in $B$, and $f_a\in B^{\phi=\pi}$. To prove this we need to check $q^{-i}v(a)+ri=v(a^{q^{-i}})+ri\to \infty$ as $|i|\to\infty$ for all $r\in(0,\infty)$, using \cref{lem:convergeInB}. This is clear as $v(a)>0$. Also one immediately checks $\phi(f_a)=\pi f_a$, hence indeed $f_a\in B^{\phi=\pi}$. In fact, we will prove later that the above construction gives a bijection $\mm_F\cong B^{\phi=\pi}$. This should seem a bit weird at first since the right-hand side $B^{\phi=\pi}$ is an $E$-vector space, so the left-hand side better be one as well. One can indeed construct a $E$-vector space structure on $\mm_F$ by Lubin--Tate theory.
		\item In general, it is not known whether elements in $B$ can be written as $\sum_{n\in\IZ}[x_n]\pi^n$ for $[x_n]\in F$. So we need different tools to study $B$.
	\end{numerate}
\end{rem}
The goal for the next few lectures is to prove that $X=X_\FFC$ is indeed a curve.
\begin{thm}[Fargues--Fontaine]\label{thm:FFCisACurve}
	The Fargues--Fontaine curve $X_\FFC$ is a Dedekind scheme. More precisely, for each $t\in B^{\phi=\pi}$, the open subset $D_+(t)\cong \Spec B\big[\frac 1t\big]^{\phi=1}$ is the spectrum of a principal ideal domain.
\end{thm}
The first ingredient in the proof of \cref{thm:FFCisACurve} is to construct Newton polygons for elements in $B_I$, where $I\subseteq (0,\infty)$ is an ideal. Note that for all $r\in I$, the valuation $v_r\colon B^b\morphism \IR\cup\{\infty\}$ extends to $B_I$ by continuity.
\begin{defi}\label{def:NewtOpen}
	Assume $I\subseteq (0,\infty)$ is an open intervall, and $f\in B_I$. Let $\Newt_I^0(f)$ be the decreasing convex function whose Legendre transform is
	\begin{equation*}
		\Ll\Newt_I^0(f)(r)=\begin{cases}
		v_r(f) & \text{if }r\in I\\
		-\infty & \text{else}
		\end{cases}\,.
	\end{equation*}
	The \defemph{Newton polygon $\Newt_I(f)\subseteq \IR^2$} is the subset of the graph of $\Newt_I^0(f)$ with slopes in $-I$.
\end{defi}
\begin{rem}\label{rem:uniformOnCompact}
	If $K\subseteq I$ is compact and $(f_n)_{n\in\IN}$ a sequence in $B^b$ converging to $f\neq 0$, then there exists an $N$ such that for all $n\geq N$ we have $v_r(f_n)=v_r(f)$ for all $r\in K$. In particular, $\Ll\Newt_I^0(f)$ is a concave piece-wise linear function with integral slopes. Thus, $\Newt_I^0(f)$ is a decreasing convex polygon with integral breakpoints.
\end{rem}
\begin{rem}
	\begin{numerate}
		\item If $a\in\mm_F$ and $f_a$ is as above, then $\Newt_{(0,\infty)}(f_a)$ is a \enquote{polygon version} of the exponential function $i\mapsto v(a)q^{-i}$:
		\begin{center}
			\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
			\draw[-to] (-3.5,0) -- (3.5,0);
			\draw[-to] (0,-0.5) -- (0,3.5);
			\draw[thick] (-1.6875,3.375) -- (-1,2) -- (0,1) -- (1,0.5) -- (2,0.25) -- (3,0.125) -- (3.375,0.110375);
			\fill (0,1) circle (0.5ex) node [above right] {$v(a)$};
			\fill (-1,2) circle (0.5ex);
			\fill (1,0.5) circle (0.5ex);
			\fill (2,0.25) circle (0.5ex);
			\fill (3,0.125) circle (0.5ex);
			\draw (2,0.75ex) -- (2,-0.75ex) node[below] {$2$};
			\draw (1,0.75ex) -- (1,-0.75ex) node[below] {$1$};
			\draw (-1,0.75ex) -- (-1,-0.75ex) node[below] {$-1$};
			\draw (-2,0.75ex) -- (-2,-0.75ex) node[below] {$-2$};
			\draw (3,0.75ex) -- (3,-0.75ex) node[below] {$3$};
			\draw (-3,0.75ex) -- (-3,-0.75ex) node[below] {$-3$};
			\end{tikzpicture}
		\end{center}
		Note that there is no $x\in\IR$ where $\Newt_{(0,\infty)}(f_a)(x)=+\infty$.
		\item If $f\in B$ and $\lambda_i$ is the slope of $\Newt_{(0,\infty)}(f)$ on $[i,i+1]$, then
		\begin{equation*}
			\lambda_i\leq 0\,,\quad\lim_{i\to\infty}\lambda_i=0\,,\quad\text{and}\lim_{i\to-\infty}\lambda_i=-\infty\,.
		\end{equation*}
	\end{numerate}
\end{rem}
So far we have defined Newton polygons for open intervalls $I$. In the case of compact intervalls $I=[a,b]$, the above \cref{def:NewtOpen} doesn't work any more and we need slightly more complicated one.
\begin{defi}
	Let $I=[a,b]$ be a compact intervall and $0\neq f\in B_I$. We define $\Newt_I^0(f)$ to be the decreasing convex function whose Legendre transform is
	\begin{equation*}
		\Ll\Newt_I^0(f)(r)=\begin{cases}
		v_r(f) & \text{if }r\in I\\
		-\infty & \text{if }r<0\\
		v_a(f)+(r-a)\partial_-v_a(f) & \text{if }r<a\\
		v_b(f)+(r-b)\partial_+v_b(f) & \text{if }r\geq b
		\end{cases}\,,
	\end{equation*}
	and again $\Newt_I(f)\subseteq \IR$ is the subset of the graph of $\Newt_I^0(f)$ with slopes in $-I$.
\end{defi}
\begin{rem}
	\begin{numerate}
		\item If $(f_n)_{n\in\IN}$ is a sequence in $B^b$ converging to $f$, then
		\begin{equation*}
			\partial_+v_r(f)=\lim_{n\to\infty}\partial_+v_r(f_n)\quad\text{and}\quad\partial_-v_r(f)=\lim_{n\to\infty}\partial_-v_r(f_n)\,.
		\end{equation*}
		Here $\partial_+v_r(f)$ denotes the right-derivative of the function $s\mapsto v_s(f)$ at $s=r$. Likewise $\partial_-$ denotes left-derivatives.
		\item For $f\in B^b$ and $\lambda$ a slope of $\Newt(f)$, then $\partial_+v_r(f)-\partial_-v_r(f)$ is precisely the multiplicity of $\lambda$ in $\Newt(f)$.
	\end{numerate}
\end{rem}
\section{Proof that the Fargues--Fontaine Curve is a Curve}
\subsection{The Graded Algebra \texorpdfstring{$P$}{P}}
\lecture[$P$ is graded factorial. Effective divisors on $|Y|$.]{2019-12-11}As usual, let $p$ be a prime, $E/\IQ_p$ a finite extension with ring of integers $\Oo_E$ and residue field $\Oo_E/\pi\Oo_E\cong \IF_q$. Let $F/\IF_q$ be a non-archimedean algebraically closed extension and $\varpi\in\mm_F\setminus\{0\}$.
Last time we defined the ring $B=B_{(0,\infty)}$. Now let
\begin{equation*}
	P\coloneqq \bigoplus_{d\geq 0}P_d\,,\quad\text{where}\quad P_d=B^{\phi=\pi^d}\,,
\end{equation*}
so that $X_\FFC=\Proj P$ is the Fargues--Fontaine curve as defined in Definition~\cref{def:FFC}. The goal for today is to prove the following theorem, working towards \cref{thm:FFCisACurve}, i.e.\ that $X_\FFC$ is indeed a curve.
\begin{thm}[Fargues--Fontaine]\label{thm:PGradedFactorial}
	$P$ is graded factorial with irreducible elements of degree $1$, i.e., the multiplicative monoid
	\begin{equation*}
		\bigcup_{d\geq 0}\big(P_d\setminus\{0\}\big)/E^\times
	\end{equation*}
	is free on $(P_1\setminus\{0\})/E^\times$. In particular, if $d\geq 1$ and $x\in P_d$, then there exist $t_1,\dotsc,t_d\in P_1$ (unique up $E^\times$ and order) such that $x=t_1\dotsm t_d$.
\end{thm}
Mind that \cref{thm:PGradedFactorial} does \emph{not} imply $P\cong \Sym_{\IQ_p}^*P_1$. In fact, the right-hand side has non-noetherian $\Proj$, whereas $\Proj P=X_\FFC$ will turn out to be noetherian. For the proof we need
\begin{thm}\label{thm:BIPID}
	Assume $I\subseteq (0,\infty)$ is compact. Then $B_I$ is a PID, and $\Spec B_I\setminus\{0\}$ is in canonical bijection with $|Y_I|$.
\end{thm}
\begin{proof}
	We use the easy to prove fact that an integral domain $A$ is a PID iff $A$ is factorial and each (non-invertible) irreducible element generates a maximal ideal. Thus, it suffices to prove the following three claims:
	\begin{numerate}
		\item For $y\in |Y_I|$ the map $\theta_y\colon B^b\epimorphism C_y$ has a unique extension to a continuous morphism $\theta_y'\colon B_I\epimorphism C_y$. Moreover, if $\ker \theta_y=(\xi_y)$, then $\xi_y$ is also a generator of $\ker\theta_y$.
		\item If $f\in B_I\setminus\{0\}$ such that $\Newt_I(f)=\emptyset$, then $f\in B_I^\times$ is a unit.
		\item If $f\in B_I$ and $\lambda$ is a slope of $\Newt_I(f)$, then there exists a $y\in|Y_{-\lambda}|$ such that $f=\xi_yg$ for some $g\in B_I$. Note that by \itememph{1} this is equivalent to the existence of some $y\in |Y_{-\lambda}|$ such that $f(y)\coloneqq\theta_y'(f)=0$.
	\end{numerate}
	We first deduce the theorem from these two claims. Note that since $I$ is compact and the slopes of $\Newt_I^0(f)$ approach $0$, only finitely many of them can be contained in $I$. Hence $\Newt_I(f)$ has only finitely many segments. Using \itememph{3} and \itememph{2} and induction on the number of segments, we see that any non-zero $f$ can be decomposed into a product $f=u\xi_{y_1}\dotsm\xi_{y_n}$ of a unit $u\in B_I^\times$ and prime elements $\xi_{y_i}$. This shows that $B_I$ is factorial. By \itememph{1}, every $\xi_y$ generates a maximal ideal, so $B_I$ is indeed a PID by the fact cited in the beginning. Moreover, we remark that this implies
	\begin{equation*}
		(B_I)_{\xi_y}^\complete\cong B_{\dR,y}^+\cong(B^b)_{\xi_y}^\complete\,.
	\end{equation*}
	The isomorphism on the right-hand side is due to $\IA_\inf\localize{\pi}/(\xi_y^n)\cong B^b/(\xi_y^n)$ for all $n\geq 1$, which follows from the easy fact that $[\varpi]$ is already invertible in $\IA_\inf\localize{\pi}/(\xi_y^n)$. Hence we get a morphism $B_{\dR,y}^+\morphism (B_I)_{\xi_y}^\complete$ of complete DVRs. This induces an isomorphism on residue fields $C_y$ and $\xi_y$ is a uniformizer on both sides, thus is indeed an isomorphism.


	Now we prove the three claims, beginning with \itememph{1}. Let $y\in |Y_I|$ and $r=d(y,0)=v_y(\pi)$, so that $r\in I$. We claim:
	\begin{alphanumerate}
		\item[\itememph{*}] The map $\theta_y\colon B^b\epimorphism C_y$ is continuous for the $v_r$-topology on $B^b$.
	\end{alphanumerate}
	Indeed, if $x=\sum_{i\gge -\infty}^\infty [x_i]\pi^i\in B^b$, then $\theta_y(x)=\sum_{i\gge -\infty}^\infty \theta_y([x_i])\pi^i$, hence
	\begin{equation*}
		v_y\big(\theta_y(x)\big)\geq \inf_{i\in\IZ}\big\{v_y\big(\theta_y([x_i])\big)+iv_y(\pi)\big\}=v_r(x)\,,
	\end{equation*}
	using $r=v_y(\pi)$. This immediately implies continuity of $\theta_y$, so \itememph{*} is proved. Since every element of $B_I$ can be written as a sequence of elements of $B^b$ which is a Cauchy sequence in the $v_r$-topology (in fact, even a Cauchy sequence in the $v_s$-topology for all $s\in I$), we see that $\theta_y$ has indeed a unique continuous extension $\theta_y'\colon B_I\morphism C_y$.
	
	In the lecture it was claimed to be a \enquote{general fact} that $\ker \theta_y'=\ov{\ker\theta_y}$, the closure being taken in $B_I$. I don't see what fact that should be (please enlighten me), so here's a proof. Since $\theta_y'$ is continuous and $0\in C_y$ is closed, the inclusion \enquote{$\supseteq$} is clear. For the converse, let $f\in\ker\theta_y'$ and $(f_n)_{n\in\IN}$ a Cauchy sequence in $B^b$ converging to $f$. Every $f_n$ can be written as $f_n=[x_n]+\xi_y g_n$ for some $x_n\in F$ and $g_n\in B^b$. Indeed, we may assume $\xi_y=\pi-[a]$. For $N\gge 0$ we have $\pi^N\theta_y(f)\in \Oo_{C_y}$, hence by \cref{prop:D}\itememph{3} we may write $\pi^N\theta_y(f)=[z_n]$ for some $z_n\in \Oo_F$. Then $x_n=z_na^{-N}$ does it. Since $v_y(\theta_y(f_n))=v_F(x_n)=v_s([x_n])$ for all $s\in (0,\infty)$, we see that $([x_n])_{n\in\IN}$ is a Cauchy sequence in the $v_s$-topology for all $s\in (0,\infty)$. Thus, $(\xi_yg_n)_{n\in\IN}$ is a Cauchy sequence in the $v_s$-topology for all $s\in I$, and converges to $f$. This proves $f\in\ov{\ker\theta_y}$.
	
	The fact that $\ker\theta_y'=(\xi_y)$ is now an easy consequence: suppose $f\in\ov{\ker\theta_y}$ and write $f$ as the limit of a Cauchy sequence $(f_n)_{n\in\IN}$ such that $f_n=\xi_yg_n$. For all $s\in I$ we have
	\begin{equation*}
		v_s(g_n-g_m)=v_s(f_n-f_m)-v_s(\xi_y)\,,
	\end{equation*}
	hence $(g_n)_{n\in\IN}$ is a Cauchy sequence in the $v_s$-topology as $v_s(\xi_y)\neq \infty$. Thus $g=\lim_{n\to\infty}g_n$ exists in $B_I$ and satisfies $f=\xi_yg$. This proves \itememph{1}.
	
	For \itememph{2}, let $I=[a,b]$ and let $(f_n)_{n\in\IN}$ be an $v_s$-Cauchy sequence for all $s\in I$ converging to $f$. Since $f\neq 0$ and $\Newt_I(f)=\emptyset$, we deduce that already $\Newt_I(f_n)=\emptyset$ for all $n\gge 0$ (this follows from \cref{rem:uniformOnCompact} for example). So it suffices to consider the case $f\in B^b$ (indeed, if the $f_n$ are units for $n\gge 0$, then $(f_n^{-1})_{n\gge 0}$ is a Cauchy sequence---here we critically use $f\neq 0$ again---and it converges to an inverse of $f$). Now we can write
	\begin{equation*}
		f=\sum_{n\gge -\infty}^\infty [x_n]\pi^n=\sum_{n\leq N}[x_n]\pi^n+\sum_{n>N}[x_n]\pi^n\eqqcolon f_-+f_+\,.
	\end{equation*}
	Here $N$ is chosen in such a way that each slope of $\Newt(f)$ on $(-\infty,N]$ is $<-b$ and each slope on $[N,\infty)$ is $>-a$. This works, since by assumption $\Newt(f)$ has no slopes in $I$.
	\begin{center}
		\begin{tikzpicture}[line width=rule_thickness, line cap=round, line join =round, x=1cm,y=1cm]
		\draw[-to] (-4.5,0) -- (4.5,0);
		\draw[-to] (0,-0.5) -- (0,3.5);
		\draw[thick] (-3.6875,3.375) -- (-3,2) -- (-2,1) node[pos=0.5, above right] {$\lambda_1$} -- (-1,0.5) node[pos=0.4, above right] {$\lambda_2$} -- (0,0.275) -- (2,0.125) -- (4.375,0.110375);
		\draw[dotted] (-4.375,3.375) -- (-3,2);
		\draw[dotted] (-2,1) -- (-1,0);
		\draw[dotted] (-1,0.5) -- (0.75,-0.375);
		\draw[dotted] (-2,1) -- (-4.375,2.1875);
		\fill (-2,1) circle (0.5ex);
		\fill (-3,2) circle (0.5ex);
		\fill (-1,0.5) circle (0.5ex);
		\draw (-1,0.75ex) -- (-1,-0.75ex) node[below] {$N-1$};
		\draw (-2,0.75ex) -- (-2,-0.75ex) node[below] {$N$};
		\draw (-3,0.75ex) -- (-3,-0.75ex) node[below] {$N+1$};
		\end{tikzpicture}
	\end{center}
	Let $\lambda_1$ and $\lambda_2$ be the slopes in the picture, so that $-\lambda_1>b>a>-\lambda_2$. Looking at the dotted lines we derive inequalities
	\begin{align*}
		v(x_n)&\geq (n-N)\lambda_1+v(x_N)\quad\text{for all }n\leq N\,,\\
		v(x_n)&\geq (n-N)\lambda_2+v(x_N)\quad\text{for all }n\geq N\,.
	\end{align*}
	Let $f=f_-+f_+$ be the above sum decomposition and write 
	\begin{equation*}
		f_-=[x_N]\pi^N\left(1+\sum_{n<N}[x_nx_N^{-1}]\pi^{n-N}\right)\,.
	\end{equation*}
	Writing the second factor as $1+g$, we claim that $g$ is topologically nilpotent in $B_I$. Indeed, let $r\in I$. We compute
	\begin{equation*}
		v_r(g)=\inff_{n<N}\big\{v(x_n)-v(x_N)+r(n-N)\big\}\geq \inff_{n<N}\big\{(\lambda_1+r)(n-N)\big\}=-\lambda_1-r>0\,,
	\end{equation*}
	proving that $g$ is topologically nilpotent, as claimed. Thus $(1+g)\in B_I^\times$. The element $[x_N]\pi^N$ is already invertible in $B^b$, hence $f_-=[x_N]\pi^N(1+g)\in B_I^\times$. To show that $f$ is a unit too, write $f=f_-(1+f_-^{-1}f_+)$. Similar as above we show $v_r(f_+)>v_r([x_N]\pi^N)$ for all $r\in I$, hence $f_-^{-1}f_+$ is topologically nilpotent in $B_I$, so $f$ is indeed a unit.
	
	We omit the proof of \itememph{3}, since it is very similar to the proof of \cref{thm:NewtonSlope} (approximate $f$ by a Cauchy sequence $(f_n)_{n\in\IN}$ in $B^b$, show that$-\lambda$ occurs as a slope in $\Newt_I(f_n)$ for all $n\gge 0$, find a Cauchy sequence $(y_n)_{n\gge 0}$ of zeros $y_n\in |Y_{-\lambda}|$ of $f_n$, and use that $|Y_{-\lambda}|$ is complete by Proposition~\cref{prop:YrComplete}).
\end{proof}
\subsection{Divisors on \texorpdfstring{$|Y|$}{|Y|}}
\begin{defi}
	Let $I\subseteq (0,\infty)$ be any intervall. The \defemph{monoid of effective divisors on $|Y_I|$} is the partially ordered monoid $\Div^+(|Y_I|)$ of formal sums
	\begin{equation*}
		\sum_{y\in|Y_I|}n_yy\,,\quad n_y\in\IN\,,
	\end{equation*}
	such that for each compact intervall $J\subseteq I$ the set $\left\{y\in|Y_J|\st n_y\neq 0\right\}$ is finite (so in particular, if $I$ is not compact, the above sums need not be finite).
\end{defi}
\begin{exm}
	if $I$ is compact, we have $\Div^+(|Y_I|)=\IN^{|Y_I|}$. In general, for arbitrary intervalls $I$ we have $\Div^+(|Y_I|)\cong \limit_{J}\Div^+(|Y_J|)$, where the limit is taken over all compact subintervalls $J\subseteq I$.
\end{exm}
\begin{defi}\label{def:div}
	For all $y$ we denote by $\ord_y\colon B_{\dR,y}^+\morphism \IN\cup\{\infty\}$ the valuation of $B_{\dR,y}^+$. For $f\in B_I\setminus\{0\}$, let
	\begin{equation*}
		\div(f)=\sum_{y\in|Y_I|}\ord_y(f)y\in \Div^+(|Y_I|)
	\end{equation*}
	be the \defemph{principal divisor associated to $f$}. Since $B_J$ is a PID for all compact $J\subseteq I$ by \cref{thm:BIPID}, the map $\div\colon B_I\setminus\{0\}\morphism \Div^+(|Y_I|)$ is well-defined, multiplicative, and vanishes on units.
\end{defi}
\begin{prop}\label{prop:divInjective}
	If $I\subseteq (0,\infty)$ is an intervall, then the map
	\begin{equation*}
		\div\colon \big(B_I\setminus\{0\}\big)/B_I^\times\morphism \Div^+(|Y_I|)
	\end{equation*}
	is injective, and bijective if $I$ is compact. Moreover, $\div(f)\geq \div(g)$ iff $f\in gB_I$.
\end{prop}
\begin{proof}
	The assertion is clear if $I$ is compact, since in this case $B_I$ is a PID by \cref{thm:BIPID}, whose primes are precisely (up to units) the $\xi_y$ for $y\in |Y_I|$. In general, write $B_I\cong\limit_JB_J$ and $\Div^+(|Y_I|)\cong \limit_J\Div^+(|Y_J|)$ and use that limits preserve injective maps. The second assertion can be seen in a similar way.
\end{proof}
\begin{lem}\label{lem:PEigenspaces}
	Recall that $P_d=B^{\phi=\pi^d}$. Then
	\begin{equation*}
		P_d=\begin{cases*}
			E & if $d=0$\\
			0 & if $d<0$\\
			\text{complicated} & if $d>0$
		\end{cases*}\,.
	\end{equation*}
\end{lem}
\begin{proof}
	Similar as for $B^b$ (see \cref{lem:BbEigenspaces}), using $\IA_\inf=\left\{f\in B\st\Newt_{(0,\infty)}(f)\subseteq \IR_{\geq 0}^2\right\}$. This equality is left as an exercise (a hard one, though).
\end{proof}
We have a canonical Frobenius action of $\Div^+(|Y|)$ defined as follows: for $y\in|Y|$ let $\phi^*(y)\in |Y|$ be the point associated to the prime ideal $\phi^{-1}(\pp_y)$. Then we put
\begin{equation*}
	\phi^*\Bigg(\sum_{y\in|Y|}n_yy\Bigg)=\sum_{y\in|Y|}n_y\phi^*(y)\,.
\end{equation*}
Since $d(\phi^*(y),0)=q^{-1}d(y,0)$, it is easily established that the right-hand side is an element of $\Div^+(|Y|)$ again, so we get indeed an action $\phi\curvearrowright \Div^+(|Y|)$.
\begin{defi}
	We define $\Div^+(|Y|/\phi^\IZ)\coloneqq \Div^+(|Y|)^{\phi^\IZ}$ to be the monoid of \defemph{effective divisors on the Fargues--Fontaine curve}. 
\end{defi}
\begin{rem}\label{rem:Div+}
	Let $a>0$ be arbitrary and $I=[a,qa)$. Then $\Div^+(|Y|/\phi^\IZ)$ is in canonical bijection with $\Div^+_\mathrm{fin}(|Y_I|)$, where the subscript $_\mathrm{fin}$ denotes the subset of those divisors which are actually finite sums. Indeed, since the Frobenius action is a \enquote{contraction with factor $q^{-1}$} in the sense that $d(\phi^*(y),0)=q^{-1}d(y,0)$, exactly one of the $\{(\phi^n)^*(y)\}_{n\in\IZ}$ will be contained in $|Y_I|$. Now the claimed bijection comes from the fact that every divisor $D\in \Div^+(|Y|/\phi^\IZ)$ can be decomposed into a finite sum of divisors of the form $\sum_{n\in\IZ}(\phi^n)^*(y)$ (do induction in the finite number of $y\in Y_I$ occurring with non-zero coefficient in $D$), and this decomposition is unique.
\end{rem}
\begin{thm}\label{thm:divIso}
	The principal divisors map $\div$ from \cref{def:div} induces an isomorphism
	\begin{equation*}
		\div\colon\bigcup_{d\geq 0}\big(P_d\setminus\{0\}\big)/E^\times\isomorphism \Div^+\big(|Y|/\phi^\IZ\big)\,.
	\end{equation*}
	In particular, this implies \cref{thm:PGradedFactorial}.
\end{thm}
\begin{proof}
	To derive \cref{thm:PGradedFactorial}, use that every effective divisor $D\in \Div^+(|Y|/\phi^\IZ)$ decomposes uniquely into a finite sum of divisors of the form $\sum_{n\in\IZ}(\phi^n)^*(y)$ as in \cref{rem:Div+}. If you think about it, the isomorphism $\div$ translates this into the assertion that the monoid on the left-hand side is free on $(P_d\setminus\{0\})/E^\times$.
	
	To prove the theorem, we first check well-definedness. For $x\in P_d\setminus\{0\}$ we have $\phi^*(\div(x))=\div(\phi^{-1}(x))=\div(\pi^{-d}x)=\div(x)$, since $\pi^{-d}$ is a unit in $B$. Hence $\div$ has indeed image in $\Div^+(|Y|)^{\phi^\IZ}$.
	
	For injectivity, let $x\in P_d\setminus\{0\}$ and $x'\in P_{d'}\setminus\{0\}$ such that $\div(x)=\div(y)$. Without restriction $d'\geq d$. From the second part of \cref{prop:divInjective} we get $x=ux'$ for some $u\in B^\times$. Then $u\in B^{\phi=\pi^{d-d'}}$. But then \cref{lem:PEigenspaces} allows only $d=d'$. In this case $B^{\phi=1}=E$, so $u\in E^\times$, proving that $x$ and $x'$  represent the same element. This shows injectivity.

	To prove surjectivity, it suffices to show that $\sum_{n\in\IZ}(\phi^n)^*(y)$ is in the image of $P_1\setminus\{0\}$. We may assume $\xi_y=\pi-[a]$. Put
	\begin{equation*}
		x=\prod_{n\geq 0}\left(1-\frac{[a]^{q^n}}{\pi}\right)=\prod_{n\leq 0}\frac{\phi^n(\xi_y)}\pi\,.
	\end{equation*}
	This $x$ is well-defined as $[a]^{q^n}$ converges to $0$ for $n\to\infty$, see \cref{lem:convergenceInB}\itememph{1}. Moreover, $\phi(x)=\prod_{n\geq 1}(\phi^n(\xi_y)/\pi)=(\xi_y/\pi)^{-1}x$ and $\div(x)=\sum_{n\leq 0}(\phi^n)^*(y)$. Applying \cref{lem:EigenspacesDim1} below to $\xi_y$ provides an element $z\neq 0$ such that $\phi(z)=\xi_yz$. Then
	\begin{equation*}
		\div(z)=\div\big(\xi_y\phi^{-1}(z)\big)=y+\phi^*\big(\div(z)\big)=y+\phi^*(y)+(\phi^2)^*(y)+\dotsb\,.
	\end{equation*}
	Hence $\div(x\phi^{-1}(z))=\sum_{n\in\IZ}(\phi^n)^*(y)$. Moreover, $\phi(x\phi^{-1}(z))=(\xi_y/\pi)^{-1}xz=\pi x\phi^{-1}(z)$. Hence $t\coloneqq x\pi^{-1}(z)$ is an element of $P_1\setminus\{0\}$ mapping to $\sum_{n\in\IZ}(\phi^n)^*(y)$.
\end{proof}
\begin{lem}\label{lem:EigenspacesDim1}
	Let $\beta\in B^b\cap W_{\Oo_E}(F)^\times$ (for example, $\xi_y$ lies in this intersection). Then we have
	\begin{equation*}
		\dim_E(B^b)^{\phi=\beta}=1\,.
	\end{equation*}
\end{lem}
\begin{proof}
	Proving \enquote{$\leq 1$} is easy: if $f,f'\in (B^b)^{\phi=\beta}$ are two non-zero eigenvectors, then
	\begin{equation*}
		f/f'\in\left(W_{\Oo_E}(F)\localize{\pi}\right)^{\phi=1}=W_{\Oo_E}(\IF_q)\localize{\pi}=E\,,
	\end{equation*}
	which has dimension $1$ over $E$.
	
	It remains to prove that $(B^b)^{\phi=\beta}$ is non-zero. Without restriction let $\beta\in\IA_\inf\setminus\pi\IA_\inf$ (a general $\beta\in B^b\cap W_{\Oo_E}(F)^\times$ can be written as $[z^{-1}]\beta'$ for $\beta'\in \IA_\inf\setminus \pi\IA_\inf$ and $z\in \Oo_F$, and it's easy to construct an eigenvector with eigenvalue $[z^{-1}]$). To obtain a non-zero eigenvector of $\beta$, we construct a converging sequence $(x_n)_{n\in\IN}$ in $\IA_\inf$ with the properties
	\begin{numerate}
		\item $x_1\notin\pi\IA_\inf$,
		\item $x_n\equiv x_1\mod \pi$ for all $n\geq 1$, and
		\item $\phi(x_n)\equiv \beta x_n\mod\pi^n$ for all $n\geq 1$.
	\end{numerate}
	We do this by induction on $n$. For $n=1$, take $x_1=[a]$, where $a\in \Oo_F\setminus\{0\}$ is a non-zero solution of $a^q=\ov{\beta }a$, where $\ov{\beta}\in \Oo_F$ is the reduction of $\beta$ modulo $\pi$. Such $a$ exists as $F$ is algebraically closed. Now let $n\geq1$ and assume $x_n$ has already been constructed. We use the ansatz $x_{n+1}=x_n+[u]\pi^n$. Then \itememph{2} is automatically satisfied. For \itememph{3} write $\phi(x_n)\equiv \beta x_n+[z]\pi^n\mod \pi^{n+1}$ and compute
	\begin{align*}
		\phi(x_n+[u]\pi^n)&\equiv \beta(x_n+[u]\pi^n)-\beta[u]\pi^n+[u^q]\pi^n+[z]\pi^n\\
		&\equiv \beta(x_n+[u]\pi^n)-[\ov{\beta}u-u^q-z]\pi^n\mod \pi^{n+1}\,.
	\end{align*}
	Thus it suffices to choose $u$ such that $\ov{\beta}u-u^q-z=0$, which is always possible as $F$ is algebraically closed.
\end{proof}
\subsection{Proof of the Main Result}
\lecture[The fundamental exact sequence. The Fargues--Fontaine curve is indeed a curve. Cohomology of twisting sheaves on the Fargues--Fontaine curve. Relation with $\IA_\cris$.]{2019-12-18}The aim for today is to show \cref{thm:FFCisACurve}, asserting that $X=\Proj P$ is indeed a \enquote{curve}, i.e., a Dedekind scheme. In some sense, $X$ is similar to $\IP_E^1$. In fact, if $E$ is replaced by $\IC$ or $\IR$, then the analogs of $X$ should be $\IP_\IC^1$ and $\snake{\IP}_\IR^1=V_+(x^2+y^2+z^2)\subseteq \IP_\IR^2$.

We have seen in the proof of \cref{thm:PGradedFactorial} that for every $y\in |Y|$ there is an element $t\in B^{\phi=\pi}$ such that $\div(t)=\sum_{n\in\IZ}(\phi^n)^*(y)$. We denote this element by $\Pi(\xi_y)$.
\begin{thm}[\enquote{Fundamental exact sequence of $p$-adic Hodge theory}]\label{thm:FundamentalExactSequence}
	Let $y\in |Y|$ and $t\coloneqq \Pi(\xi_y)\in B^{\phi=\pi}$. Then for all $d\geq 0$ the following sequence is exact:
	\begin{equation*}
		0\morphism E\cdot t^d \morphism B^{\phi=\pi^d}\morphism B_{\dR,y}^+/\xi_y^dB_{\dR,y}^+\morphism 0\,.
	\end{equation*}
\end{thm}
\begin{proof}
	Injectivity on the left is clear. By construction of $\div(t)$, we see that $\ord_y(t)=1$, hence the image of $E\cdot t^d$ is contained in the kernel of $B^{\phi=\pi^d}\morphism B_{\dR,y}^+/\xi_y^dB_{\dR,y}^+$. Conversely, if $x\in B^{\phi=\pi}\cap \xi_y^d B_{\dR,y}^+$, then $\div(x)\geq dy$. But $\div(x)$ is $\phi$-invariant, hence we even get $\div(x)\geq d\div(t)=\div(t^d)$, so $x\in E\cdot t^d$. This shows exactness at $\smash{B^{\phi=\pi^d}}$. 
	
	So it remains to show surjectivity of the third arrow. We claim that it suffices to deal with the case $d=1$. Indeed, suppose $B^{\phi=\pi}\epimorphism C_y$ is surjective. For all $c\in C_y$ let $t_c\in B^{\phi=\pi}$ be a preimage; in particular, $t_1$ maps to $1$. Now suppose $x\in B_{\dR,y}^+/\xi_y^dB_{\dR,y}$ is given. If $c_0$ is the image of $x$ in $C_y$, then $t_{c_0}\cdot t_1^{d-1}\in B^{\phi=\pi^d}$ is an element whose image approximates $x$ up to a multiple of $\xi_y$, say, 
	\begin{equation*}
		x-t_{c_0}\cdot t_1^{d-1}\equiv c_1\xi_y\mod \xi_y^2B_{\dR,y}^+
	\end{equation*}
	for some $c_1\in C_y$. By construction we have $\ord_y(t)=1$, hence $t\equiv u\xi_y\mod \xi_y^2B_{\dR,y}^+$ for some $u\in C_y\setminus \{0\}$. Now $t_{u^{-1}c_1}\cdot t\cdot t_1^{d-2}$ is an element of $B^{\phi=\pi^d}$ and satisfies
	\begin{equation*}
		x-t_{c_0}\cdot t_1^{d-1}-t_{u^{-1}c_1}\cdot t\cdot t_1^{d-2}\equiv c_2\xi_y^2\mod \xi_y^3B_{\dR,y}^+
	\end{equation*}
	for some $c_2\in C_y$. Continuing in this fashion, we obtain the desired surjectivity.
	
	Thus we may assume $d=1$. For simplicity, we finish the proof of surjectivity only for the case $E=\IQ_p$ (the general case needs Lubin--Tate theory). In this case the assertion follows from \cref{lem:Qp} below.
\end{proof}
\begin{lem}\label{lem:Qp}
	Suppose $E=\IQ_p$. Let $\epsilon=(1,\zeta_p,\zeta_{p^2},\dotsc)\in \Oo_{C_y}^\flat\cong \Oo_F$ be a compatible system of non-trivial $(p^n)\ordinalth$ roots of unity. Let $t=\log{[\epsilon]}\in B^{\phi=p}$. Then there exists a commutative diagram
	\begin{equation*}
		\begin{tikzcd}
			1 \rar &\epsilon^{\IQ_p}\dar[iso]\rar & 1+\mm_F \dar[iso, "\log{[-]}"{swap}]\rar & C_y \rar \eqar[d] &0\\
			1 \rar & \IQ_p\cdot t \rar& B^{\phi=p}\rar["\theta_y"] & C_y\rar & 0 
		\end{tikzcd}
	\end{equation*}
\end{lem}
\begin{proof}
	In the above diagram, $\log{[-]}$ denotes the power series defined as in \cref{rem:log}\itememph{2} by $\log (1-x)=\sum_{i=1}^\infty(-1)^{i-1}x^i/i$. An element $u\in1+\mm_F$ satisfies $v_r(1-u)>0$ for all $r\in (0,\infty)$, so its easy to check that the partial sums of this power series form a Cauchy sequence in the $v_r$-topology on $B^b$. Thus the series converges. Moreover, we check $\phi\log(u)=\log(\phi(u))=\log(u^p)=p\log (u)$, so $\log{[-]}\colon 1+\mm_F\morphism B^{\phi=p}$ is well-defined. 
	
	In view of \cref{thm:FundamentalExactSequence} have to show surjectivity of $\theta_y\colon B^{\phi=p}\morphism C_y$. Consider the commutative diagram
	\begin{equation*}
		\begin{tikzcd}
			1+\mm_F\dar[epi,"(-)^\sharp"'] \rar["\log{[-]}"]& B^{\phi=p}\dar["\theta_y"]\\
			1+\mm_{C_y} \rar[epi,"\log"]& C_y
		\end{tikzcd}\,.
	\end{equation*}
	The left vertical arrow is surjective since $C_y$ is algebraically closed (so $(-)^\sharp\colon \Oo_F\epimorphism\Oo_C$ is surjective, and it's easy to check that $1+\mm_F$ is the preimage of $1+\mm_{C_y}$). The bottom horizontal arrow is surjective as its image is $p$-divisible (because $C_y$ admits $p\ordinalth$ roots) and open (because for all $c\in C_y$ in the image, the power series defining $\exp$ converges on $c+p^n\Oo_{C_y}$ for sufficiently large $n$, so $\exp$ defines a local inverse). This shows surjectivity of $\theta_y\colon B^{\phi=p}\morphism C_y$, which is all we need for \cref{thm:FundamentalExactSequence}.
	
	Nevertheless, to finish the proof of \cref{lem:Qp}, we also need to show exactness of the top row. But the top row is the inverse limit of
	\begin{equation*}
		1\morphism \mu_{p^\infty}(C_y)\morphism 1+\mm_{C_y}\morphism[\log]C_y\morphism 0
	\end{equation*}
	along multiplication/exponentiation by $p$. Here we use $\limit_{x\mapsto x^p}\mu_{p^\infty}(C_y)\cong \epsilon^{\IQ_p}$, the left-hand side being isomorphic to $\IQ_p/\IZ_p$ and the right-hand side to $\IQ_p$.
\end{proof}
\begin{cor}\label{cor:P/tPpoint}
	Let $t=\Pi(\xi_y)$ as in \cref{thm:FundamentalExactSequence}. Then we have an isomorphism of graded rings
	\begin{equation*}
		P/tP\cong S\coloneqq\left\{f\in C_y[T]\st f(0)\in E\right\}\,.
	\end{equation*}
	In particular, $\Proj P/tP=\{0\}$ is a single point. We denote by $\infty_t$ its image in $\Proj P=X$.
\end{cor}
\begin{proof}
	As usual, let $\theta_y\colon B\morphism C_y$ denote the canonical map (or rather the continuous extension of the canonical map, constructed as in Claim~\itememph{1} in the proof of \cref{thm:BIPID}). Then we obtain a morphism of graded rings $P\morphism S$ by sending
	\begin{equation*}
		\sum_{d\geq 0}x_d\longmapsto \sum_{d\geq 0}\theta_y(x_d)T^d
	\end{equation*}
	(the left-hand side denotes a decomposition of an element of $P=\bigoplus_{d\geq 0}P_d$ into homogeneous components). As $\theta_y(t)=0$, this descends to a graded ring morphism $P/tP\morphism S$. By \cref{lem:PEigenspaces} this is an isomorphism in degree $0$, and surjective by \cref{thm:FundamentalExactSequence}.
	
	To see injectivity, suppose $x\in P_d$ satisfies $\theta_y(x)=0$. Then $x$ is divisible by $\xi_y$ in $B_{\dR,y}^+$. Using $\ord_y(t)=1$ and the surjectivity part of the fundamental sequence, we see that we can write $x\equiv t't\mod \xi_y^dB_{\dR,y}^+$ for some $t'\in P_{d-1}$. By the fundamental sequence again, we obtain $x-t't\in Et^d$. Hence $x\in tP$, proving injectivity.
	
	It remains to show $\Proj P/tP=\{0\}$. Suppose $\pp$ is a homogeneous prime ideal of $P/tP$ and $cT^d\in \pp$ for some $c\in C_y\setminus\{0\}$, $d\geq 1$. Then $T^{d+1}=c^{-1}T\cdot cT^d$ is an element of $\pp$ since the first factor is an element of $S$ and the second is in $\pp$. Thus $T\in \pp$, so $\pp\notin \Proj S$.
\end{proof}
We know $P$ is generated by $P_1$. Hence for all $n\in \IZ$ there are canonical line bundles $\Oo_X(n)$ on $X$. These are obtained as the quasi-coherent sheaves associated to the graded modules $P[n]$ defined by $P[n]_d=P_{d+n}$.
\begin{lem}\label{lem:HiOXn}
	For all $n\in \IZ$ we have an isomorphism $H^0(X,\Oo_X(n))\cong B^{\phi=\pi^n}$.
\end{lem}
\begin{proof}
	We have a canonical morphism $B^{\phi=\pi^d}=P_d\morphism H^0(X,\Oo_X(n))$. Since $P$ is graded factorial, it is easy to check that this is an isomorphism.
\end{proof}
Now we can restate and prove our main result, \cref{thm:FFCisACurve}. This finally justifies calling the Fargues--Fontaine curve a \defemph{curve}.
\begin{thm}[Fargues--Fontaine]\label{thm:FFCisACurveII}
	For any non-zero $t\in P_1=B^{\phi=\pi}$, the ring $B_t\coloneqq P\localize{t}_0=B\localize{t}^{\phi=1}$ is a PID, and on underlying sets
	\begin{equation*}
		X=\Proj P=D_+(t)\sqcup V_+(t)=\Spec B_t\sqcup \{\infty_t\}\,.
	\end{equation*}
	In particular, $X$ is noetherian and regular of Krull dimension $1$.
\end{thm}
\begin{proof}
	As in the proof of \cref{thm:BIPID}, it suffices that $B_t$ is factorial and that each (non-invertible) irreducible element generates a maximal ideal. If $x\in B_t$, then for some $d\geq 0$ we have $x=t'/t^d$ with $t'\in P_d$. By \cref{thm:PGradedFactorial}, we can factor $t'=t_1\dotsm t_d$ with $t_i\in P_1$. By the previous \cref{cor:P/tPpoint}, the vanishing set of each $t_i/t$ is either empty or a single closed point. Hence $t_i/t$ is a unit or generates a maximal ideal.
	
	Now pick $t,t'\in P_1\setminus \{0\}$ non-$E$-collinear (these exist by \cref{thm:divIso} for example). Then $X=\Spec B_t\cup \Spec B_{t'}$ and the theorem follows.
\end{proof}
\begin{lem}\label{lem:BdRx}
	Let $|X|$ denote the set of closed points of $X$. Then---as for $\IP_E^1$---there exists bijections
	\begin{equation*}
		|X|\cong |Y|/\phi^\IZ \cong (P_1\setminus\{0\})/E^\times\,.
	\end{equation*}
	Moreover, if $y\in |Y|$ corresponds to $x\in |X|$, then $B_{\dR,x}^+\coloneqq \roof{\Oo}_{X,x}\cong B_{\dR,y}^+$.
\end{lem}
\begin{proof*}
	By \cref{thm:divIso}, we get a bijection $|Y|/\phi^\IZ\cong (P_1\setminus\{0\})/E^\times$, as the left-hand side are precisely the \enquote{indecomposable} divisors in $\Div^+(|Y|/\phi^\IZ)$. By \cref{thm:FFCisACurveII} and \cref{cor:P/tPpoint}, we see that the closed points of $X$ are precisely the points of the form $\infty_t$ for $t\in P_1\setminus\{0\}$, and moreover $t$ is unique up to $E^\times$. This shows the asserted bijection.
	
	Choose $t\in P_1$ corresponding to $y$ and let $t'\in P_1$ be such that $X=\Spec B_t\cup \Spec B_{t'}$. Then $\ord_y(t)=1$ and $\ord_y(t')=0$, so the canonical map $B\morphism B_{\dR,y}^+$ induces maps $B_{t'}/(t/t')^dB_{t'}\morphism B_{\dR,y}^+/\xi_y^dB_{\dR,y}^+$ for all $d\geq 1$. Taking limits (and using that $(t/t')$ is a maximal ideal in $B_{t'}$) gives a map 
	\begin{equation*}
		\roof{\Oo}_{X,x}\morphism B_{\dR,y}^+\,.
	\end{equation*}
	We claim that this is an isomorphism. Indeed, it is a morphism of DVRs mapping the uniformizer $t/t'$ to some uniformizer of $B_{\dR,y}^+$, so we only need to check that the induced morphism on residue fields is an isomorphism. But a non-zero map of fields is always injective, so surjectivity suffices. By the fundamental sequence (\cref{thm:FundamentalExactSequence}), $P_1\epimorphism C_y$ surjects onto the residue field of $B_{\dR,y}^+$. Since $t'$ maps to a unit in $B_{\dR,y}^+$, we see that $t'^{-1}P_1\epimorphism C_y$ is still surjective, and $t'^{-1}P_1\subseteq B_{t'}$.
\end{proof*}
\begin{defi}\label{def:deg}
	As usual, let $\Div(X)$ denote the group of \defemph{divisors} of $X$, i.e., the free abelian group on the set of closed points $|X|$.
	\begin{numerate}
		\item We define the \defemph{degree map} $\deg\colon \Div(X)\morphism \IZ$ by $\deg\left(\sum_{x\in |X|}n_xx\right)=\sum_{x\in |X|}n_x$.
		\item If $f\in K(X)^\times$ is a non-zero element of the function field (i.e., the stalk at the generic point) of $X$, we put $\div(f)=\sum_{x\in |X|}\ord_x(f)$, where $\ord_x$ denotes the valuation of $B_{\dR,x}^+$.
	\end{numerate}
\end{defi}
\begin{rem}
	In the lecture it was pointed out that \cref{def:deg}\itememph{1} is actually a rather odd choice of degree map. To see where this comes from, recall that the \enquote{real} analogue of the Fargues--Fontaine curve should be $\snake{\IP}_{\IR}^1$. Now for a divisor on $\snake{\IP}_{\IR}^1$ consisting of a single point $x$, there are two ways to define its degree:
	\begin{numerate}
		\item we could put $\deg x=[\kappa(x):\IR]$,
		\item or just $\deg x=1$.
	\end{numerate}
	Option~\itememph{1} is the one we would expect to be the canonical choice, since it comes from $\snake{\IP}_{\IR}^1$ considered as a curve over $\IR$. But in \cref{def:deg} we actually go with option~\itememph{2}.
\end{rem}
\begin{prop}
	For $f\in K(X)^\times$ we have $\deg(\div(f))=0$ (so heuristically speaking \enquote{$X$ is proper}). Moreover, the induced map
	\begin{equation*}
		\deg\colon \Pic(X)\isomorphism \IZ
	\end{equation*}
	is an isomorphism, with inverse given by $n\mapsto \Oo_X(n)$.
\end{prop}
\begin{proof}
	Without restriction assume $f=t'/t$, with $t',t\in P_1$. Indeed, since $X$ is locally a PID (\cref{thm:FFCisACurveII}) and $P$ is graded factorial (\cref{thm:PGradedFactorial}), every element in the function field can be decomposed into a product of elements of the form $t/t'$. In this case we have $\div(f)=\infty_{t'}-\infty_t$, which is clearly of degree $0$.
	
	To see the second assertion, use the short exact sequence
	\begin{equation*}
		0\morphism \IZ\{\Oo_X(1)\}\morphism \Pic(X)\morphism \Pic(\Spec B_t)\morphism 0
	\end{equation*}
	(this is rather easy to derive) and the fact that $\Pic(\Spec B_t)=0$ as $B_t$ is factorial.
\end{proof}
\begin{prop}
	The cohomology of the twisting sheaves $\Oo_X(n)$ is given by
	\begin{equation*}
		H^i\big(X,\Oo_X(n)\big)=\begin{cases*}
		B^{\phi=\pi^n} & if $i=0$\\
		0 & if $i\geq 2$\\
		0 & if $i=1$, $n\geq 0$\\
		B_{\dR,x}^+/(\Fil^{-n}B_{\dR,x}^++E) & if $i=1$, $n<0$
		\end{cases*}\,,
	\end{equation*}
	where $x$ may be any closed point of $X$ and $\Fil^dB_{\dR,x}^+=t^dB_{\dR,x}^+$ for $t$ corresponding to $x$ under the bijection from \cref{lem:BdRx}.
\end{prop}
\begin{proof*}
	The case $i=0$ was done in \cref{lem:HiOXn}. The case $i\geq 2$ follows from Grothendieck's theorem on cohomological dimension and the fact that $X$ is one-dimensional, or alternatively via \v Cech cohomology, using that $X$ can be covered by two affine opens.
	
	For $i=1$, $n\geq 0$, we claim that it suffices to show $H^1(X,\Oo_X)=0$. Indeed, choose any $t\in P_1\setminus\{0\}$ and let $B_{\dR}^+=B_{\dR,x}^+$ for the corresponding point $x=\infty_t$. Then we have an exact sequence
	\begin{equation}\label{eq:BdRExactSeq1}
		0\morphism \Oo_X\morphism[t^n]\Oo_X(n)\morphism t^{-n}B_{\dR}^+/B_{\dR}^+\morphism 0\,.
	\end{equation}
	The term on the right-hand side is abuse of notation for the corresponding skyscraper sheaf supported on $\infty_t$. Since a sheaf supported only at a closed point as vanishing higher cohomology, we find that $H^1(X,\Oo_X)\epimorphism H^1(X,\Oo_X(n))$ is surjective, so $H^1(X,\Oo_X)=0$ is indeed sufficient to deduce $H^1(X,\Oo_X(n))=0$ as well.
	
	To see $H^1(X,\Oo_X)=0$, let $j\colon \Spec B_t\monomorphism X$ denote the corresponding open embedding. Now look at the exact sequence
	\begin{equation}\label{eq:BdRExactSeq2}
		0\morphism \Oo_X\morphism j_*\Oo_{\Spec B_t}\morphism B_{\dR}/B^+_\dR\morphism 0\,,
	\end{equation} 
	where $B_\dR\coloneqq \Frac(B^+_\dR)$ denotes the fraction field. Exactness of this sequence can be seen by writing $j_*\Oo_{\Spec B_t}\cong \colimit_{d\geq 0}\Oo_X(d\cdot \infty_t)$ and $B_\dR/B_\dR^+\cong \colimit_{d\geq 0}t^{-d}B_\dR^+/B_\dR^+$. Since $X=\Proj P$ is separated, the inclusion $j\colon \Spec B_t\monomorphism X$ is affine. Hence $H^1(X,j_*\Oo_{\Spec B_t})\cong H^1(\Spec B_t,\Oo_{\Spec B_t})=0$. Therefore, taking the long exact cohomology sequence associated to \cref{eq:BdRExactSeq2} gives
	\begin{equation*}
		0\morphism E\morphism B_t\morphism B_\dR/B_\dR^+\morphism H^1(X,\Oo_X)\morphism 0
	\end{equation*}
	(using $H^0(X,\Oo_X)\cong P_0\cong E$ by \cref{lem:HiOXn} and \cref{lem:PEigenspaces}). Now the fundamental exact sequence implies that $t^{-d}P_d\epimorphism t^{-d}B_\dR^+/B_\dR^+$ is surjective. Since $B_t=\bigoplus_{d\geq 0}t^{-d}P_d$ and $B_\dR/B_\dR^+\cong \colimit_{d\geq 0}t^{-d}B_\dR^+/B_\dR^+$ and surjectivity behaves well under colimits, wee see that $B_t\epimorphism B_\dR/B_\dR^+$ must be surjective as well. Thus $H^1(X,\Oo_X)=0$, as required.
	
	Now let $n<0$. In this case we use the short exact sequence
	\begin{equation}\label{eq:BdRExactSeq3}
		0\morphism \Oo_X(n)\morphism[t^{-n}]\Oo_X\morphism B_\dR^+/t^{-n}B_\dR^+\morphism 0\,,
	\end{equation}
	which can be derived analogous to \cref{eq:BdRExactSeq1}. Using $H^1(X,\Oo_X)=0$ and $H^0(X,\Oo_X)\cong E$ and $H^0(X,\Oo_X(n))\cong P_n=0$, we find that the induced sequence on cohomology looks like
	\begin{equation*}
		0\morphism E\morphism B_\dR^+/t^{-n}B_\dR^+\morphism H^1\big(X,\Oo_X(n)\big)\morphism 0\,.
	\end{equation*}
	This immediately implies $H^1(X,\Oo_X(n))=B_\dR^+/(\Fil^{-n}B_\dR^++E)$, as required.
\end{proof*}
\subsection{The Fargues--Fontaine Curve and \texorpdfstring{$\IA_\cris$}{Acris}}
Assume $E=\IQ_p$. In this case we can express $X$ in terms of the crystalline period ring $B_\cris^+=\IA_\cris\localize{p}$. Let's recall the construction of $\IA_\cris$ from \cref{subsec:Acris} first. Fix a non-archimedean algebraically closed extension $C/\IQ_p$. We have seen in the proof of Example~\cref{exm:OCperfectoid} that the kernel of $\theta\colon\IA_\inf\morphism \Oo_C$ is generated by $\xi=p-[p^\flat]$, where $p^\flat=(p,p^{1/p},\dotsc)\in \Oo_C^\flat\cong \Oo_F$. Then
\begin{equation*}
	\IA_\cris=\IA_\inf\left[\frac{[p^\flat]^n}{n!}\st n\in\IN\right]_p^\complete
\end{equation*}
(in our original definition of $\IA_\cris$ we adjoined divided powers $\xi$ instead; however, $p$ already has divided powers in $\IA_\inf$, so we may equivalently adoin divided powers of $[p^\flat]$).
\begin{defi}\label{def:Bb+}
	We define the following variations of the ring $B$.
	\begin{numerate}
		\item Let $B^{b,+}\coloneqq \IA_\inf\localize{p}$.
		\item For an interval $I\subseteq (0,\infty)$, let $B_I^+$ denote the completion of $B^{b,+}$ with respect to the valuations $(v_r)_{r\in I}$. This coincides with the closure of $B^{b,+}$ in $B_I$.
		\item For $I=\{r\}$, we put $B_r^+\coloneqq B_{\{r\}}^+$ for convenience.
		\item Let $B^+=B_{(0,\infty)}^+$ be the ring of \enquote{functions on $|Y|$ that extend to the boundary}.
	\end{numerate}
\end{defi}
\begin{rem}\label{rem:Bs+}
	Note that if $s\leq r$, then $v_s(x)\geq \frac{s}{r}v_r(x)$ for $x\in B^{b,+}$. This would be false for $B^b$, but in $B^{b,+}$ it works because $B^{b,+}$ consist of $p$-power series whose Teichmüller coefficients have non-negative valuation. Thus every $v_s$-Cauchy sequence is a $v_r$-Cauchy sequence too, and we get a canonical inclusion $B_s^+\subseteq B_r^+$. In particular, we obtain $B_r^+=B_{(0,r]}^+$.
\end{rem}
\begin{lem}\label{lem:Br+Ainfap}
	Let $a\in\mm_F\setminus\{0\}$ and $r=v_F(a)$. Then
	\begin{equation*}
		B_r^+=\IA_\inf\Big[\textstyle\frac{[a]}p\Big]_p^\complete\localize{p}
	\end{equation*}
\end{lem}
\begin{proof*}
	Let $A$ denote the right-hand side. We must show that $A$ is $v_r$-complete (or more precisely, complete with respect to the obvious continuous extension of $v_r$ to $A$) and that every $v_r$-continuous map $B^{b,+}\morphism A'$ into a complete topological ring extends uniquely to a map $A\morphism A'$.
	
	The latter is quite easy to see: elements $\alpha\in A$ can be (non-uniquely) written as $p$-Laurent series $\alpha=\sum_{n\gge -\infty}^\infty a_np^n$ for $a_n\in \IA_\inf \left[[a]/p\right]$. Now if $B^{b,+}\morphism A'$ is given, then the images of $a_np^n$ are determined, so it suffices to see that $(a_np^n)_{n\gge -\infty}$ is a $v_r$-null sequence (since then the partial sums converge in $A'$, hence we can take their limit as the image of $\alpha$). But $v_r([a]/p)=0$, hence $v_r(b)\geq 0$ for all $b\in \IA_\inf\left[[a]/p\right]$. Thus $v_r(a_np^n)\geq rn$ and we get indeed a $v_r$-null sequence.
	
	To see that every $v_r$-Cauchy sequence in $A$ converges, it's enough to check that every series whose terms form a $v_r$-null sequence is convergent. This will be an immediate consequence of the following claim:
	\begin{alphanumerate}
		\item[\itememph{*}] If $\alpha\in A$ is an element such that $v_r(\alpha)\geq rn$ for some $n\geq 0$, then $\alpha\in p^n\IA_\inf\left[[a]/p\right]_p^\complete$.
	\end{alphanumerate}
	To prove \itememph{*}, write $\alpha$ as a $p$-Laurent series as above. Also, without restriction, $r(n+1)>v_r(\alpha)$. All terms $a_mp^m$ with $m\geq n+1$ may be ignored, so we may assume that $\alpha=bp^{-N}$ for some $b\in \IA_\inf\left[[a]/p\right]$ and some $N\geq 0$. Increasing $N$ if necessary we may even assume $b\in \IA_\inf$. Write $b=\sum_{i=0}^\infty[b_i]p^i$. As $v_r(bp^{-N})\geq rn$, we obtain $v_F(b_i)\geq r(N+n-i)$. As $v_F(a)=r$, we may write $b_i=a^{N+n-i}c_i$ for some $c_i\in \Oo_F$. Then
	\begin{equation*}
		\alpha=bp^{-N}=p^n\sum_{i=0}^{N+n}[c_i]\left(\frac{[a]}{p}\right)^{N+n-i}+p^{n+1}\sum_{i=N+n+1}^\infty[b_i]p^{i-(N+n+1)}\,.
	\end{equation*}
	Both sums are elements of $\IA_\inf[[a]/p]$. This shows that $\alpha$ is indeed divisible by $p^n$, and thus \itememph{*} is proved.
\end{proof*}


The Frobenius $\phi$ on $B^{b,+}$ induces an isomorphism $\phi\colon B_r^+\isomorphism B_{pr}^+\subseteq B_r^+$. Moreover, if $v_C\colon C\morphism \IR\cup\{\infty\}$ denotes the valuation of $C$, then the following lemma holds.
\begin{lem}\label{lem:B+}
	Let $r=v_C(p)$. Then $B_{pr}^+\subseteq B_\cris^+\subseteq B_r^+$. Moreover, we have
	\begin{equation*}
		B^+=\bigcap_{n=1}^\infty \phi^nB_\cris^+=\bigcap_{n=1}^\infty \phi^nB_r^+\,.
	\end{equation*}
	In particular, $B^+$ is the largest subring of $B_\cris^+$ on which $\phi$ is bijective (or, equivalently, surjective, since it's easy to check that $\phi$ is injective on $B_\cris^+$).
\end{lem}
\begin{proof}
	Note that $r=v_C(p)=v_F(p^\flat)$. Hence $B_{pr}^+$ and $B_r^+$ can be described via \cref{lem:Br+Ainfap}. Concretely, we obtain a chain of inclusions
	\begin{equation*}
		\IA_\inf\left[\frac{[p^\flat]^p}{p}\right]\subseteq \IA_\inf\left[\frac{[p^\flat]^n}{n!}\st n\in\IN\right]\subseteq \IA_\inf\left[\frac{[p^\flat]}{p}\right]\,.
	\end{equation*}
	After $p$-completion and localization at $p$ (both operations preserve inclusions) this becomes $B_{pr}^+\subseteq B_\cris^+\subseteq B_r^+$, as required. This already shows that it doesn't matter whether we take the intersection over $\phi^nB_\cris^+$ or $\phi^nB_r^+$.
	
	Moreover, $\phi^n\colon B_r^+\morphism B_r^+$ has image $B_{p^nr}^+$. Using the observation from \cref{rem:Bs+}, we thus obtain
	\begin{equation*}
		\bigcap_{n=1}^\infty\phi^nB_r^+=\limit_{n\geq 1}B_{p^nr}=B^+\,,
	\end{equation*}
	where the limit in the middle is taken along the canonical inclusions $B_{p^{n+1}r}^+\subseteq B_{p^nr}^+$. This finishes the proof.
\end{proof}
\begin{prop}\label{prop:FFandBcris}
	We have canonical isomorphisms
	\begin{equation*}
		P=\bigoplus_{d\geq 0}B^{\phi=p^d}\cong \bigoplus_{d\geq 0}(B^+)^{\phi=p^d}\cong \bigoplus_{d\geq 0} (B_\cris^+)^{\phi=p^d}\,.
	\end{equation*}
\end{prop}
\begin{proof}[Sketch of a proof]
	One first checks that if $x\in B^{\phi=p^d}$, then $\Newt_{(0,\infty)}(x)\geq 0$. Indeed, since $\phi(x)=p^dx$, scaling $\Newt_{(0,\infty)}$ along the $y$-axis with factor $p$ is the same as a translation by $d$ along the $x$-axis. Now if $\Newt_{(0,\infty)}(x)$ is not always strictly positive, then it has to cross the $x$-axis somewhere. But then it must be identically zero by the above symmetry observation.
	
	Moreover, one can show that
	\begin{equation*}
		B^+=\left\{x\in B\st\Newt_{(0,\infty)}(x)\geq 0\right\}\,.
	\end{equation*}
	Thus $B^{\phi=p^d}=(B^+)^{\phi=p^d}$. Moreover, $B_\cris^+=\IA_\cris\localize{p}$ is $p$-divisible, hence $\phi$ is bijective on the subring $\bigoplus_{d\geq 0}(B_\cris^+)^{\smash{\phi=p^d}}$. But since $B^+$ is the largest subring with this property by \cref{lem:B+}, hence it contains all $(B_\cris^+)^{\phi=p^d}$. This shows $(B^+)^{\phi=p^d}=(B_\cris^+)^{\phi=p^d}$ and we are done.
\end{proof}
\begin{rem}
	Let $\epsilon=(1,\zeta_p,\zeta_{p^2},\dotsc)\in \Oo_C^\flat\cong \Oo_F$ and $t=\log{[\epsilon]}$ as in \cref{lem:Qp}. Put $B_\cris=B_\cris^+\localize{t}$ and let $B_e=(B_\cris)^{\phi=1}$. Then on underlying topological spaces we can write
	\begin{equation*}
		X=\text{\enquote{$\Spec B_e\cup_{\Spec B_\dR}\Spec B_\dR^+$}}\,.
	\end{equation*}
	That is, the Fargues--Fontaine curve is obtained by \enquote{gluing} the open subset $D_+(t)$ together with the spectrum of the DVR $B_\dR^+=B_{\dR,\infty_t}^+$ (which has only two points) along their generic points.
\end{rem}
\begin{center}
	\Large\bfseries Merry $\IA_\cris$mas!
\end{center}


\appendix

\backmatter\KOMAoption{chapterprefix}{false}
\printbibliography
\end{document}